### 2021-03-09 results/draft.tex
push from iMac

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{plext}
\usepackage{cite}
\usepackage{setspace}
\usepackage{float}
\usepackage{lineno}
\usepackage{color}
\usepackage[dvipdfmx]{graphicx}
\usepackage{array, booktabs}
\usepackage[top=25truemm,bottom=25truemm,left=30truemm,right=30truemm]{geometry}
\usepackage{threeparttable}
\usepackage{ulem}
%\usepackage{amsmath}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Table}
\begin{document}\setcounter{page}{1}
\renewcommand\citeleft{(}
\renewcommand\citeright{)}

\flushleft{\textbf{Title: Inetgrated spatial model estimates the fish distribution using environmental DNA and catch data}}\\
%\flushleft{\textbf{Running title: }}\\
\flushleft{Yuki Kanamori$^{1\ast}$, Hiroshi Okamura$^{2}$, Shota Nishijima$^{2}$, Yuki Hongo$^{2}$, Yasuyuki Uto$^{3}$, Hisatoku Mita$^{4}$, Mitsuhiyo Ishii$^{4}$, Kiyoharu Akimoto$^{5}$, and Akane Kusano$^{6}$}\\
\ \\
$^{1}$ Fisheries Resources Institute, Japan Fisheries Research and Education Agency, 25-259 Shimomekurakubo, Samemachi, Hachinohe, Aomori 031-0841, Japan\\
$^{2}$ Fisheries Resources Institute, Japan Fisheries Research and Education Agency, 2-12-4 Fukuura, Kanazawa, Yokohama, Kanagawa 236-8648, Japan\\
$^{3}$ \\
$^{4}$ \\
$^{5}$ \\
$^{6}$ \\
\ \\

$^{\ast}$ Corresponding author\\
Email: kana.yuki@fra.affrc.go.jp

\newpage
\flushleft{\textbf{Abstract}\\}

\flushleft{\textbf{Keywords}}\\

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology. Environmental DNA (eDNA)

\ \ \ \ \ \ \ \ \ \
Accurate species identification of fish eggs and larvae is essential for elucidating the ecology of the early life--history of fish, including the location and timing of fish spawning, hatching, and migration (Ko et al., 2013). Such information can improve the inference and forecasting of fish population size. Morphological characteristics used for species identification have traditionally been the size and oil globules of eggs, and the body shape, pigmentation, and meristic count of larvae (e.g., Matarese and Sandknop, 1984; Ko et al., 2013). However, species identification based on these morphological characteristics leads to species misidentification because these morphological characteristics are likely to overlap among species in early life--history (e.g., Victor et al., 2009; Ko et al., 2013). For example, when we use size of eggs as a morphological measure, we often classify eggs by whether their diameters are greater than or less than a predetermined value. However, because distributions of diameters are likely to overlap among species, some eggs may be erroneously classified as different species. In addition, morphological characteristics can change during developments, so that individuals of the same species at different development stages can be misidentified as a different species (Ko et al., 2013).

\ \ \ \ \ \ \ \ \ \
Spotted mackerel \textit{Scomber australasicus} and chub mackerel \textit{Scomber japonicus} are small pelagic fish that are widely distributed in the western North Pacific (ca. $\textrm{120}-\textrm{150}^{\circ}$E, Fig. 1; Watanabe and Yatsu, 2006). These species spawn in waters near the Kuroshio Current from winter to summer (e.g., Watanabe, 1970; Watanabe et al., 1999; Watanabe and Yatsu, 2006), after which the adults and their offspring are transported to their feeding ground by the Kuroshio Current (e.g., Watanabe and Nishida, 2002). Because Nishida (2001) suggested that egg diameter differs between the two species, species identification based on egg diameter has been conducted routinely since 2005; eggs smaller than 1.1 mm in diameter were classified as chub mackerel and vice versa. These eggs, which were identified according to this basis, have been used as the indices of the spawning stock biomass of spotted mackerel and chub mackerel for stock assessment. However, the recent egg density of spotted mackerel was considerably high although stock biomass and spawning stock biomass has been low (Yukami et al., 2019). This considerable increase in the egg density of spotted mackerel is likely the result of overestimation because the difference in egg diameter has become ambiguous according to the increase in the egg density of chub mackerel and overlapping the distributions of egg diameters in the two species (Yukami et al., 2019). That is, the boundary between the left tail of the distribution of egg diameters of spotted mackerel and the right tail of the distribution of egg diameters of chub mackerel is clear when egg density of chub mackerel is low. In contrast, this boundary becomes unclear when egg density of chub mackerel increases because the whole of the distribution of egg diameters of chub mackerel becomes large and includes the distribution of egg diameters of spotted mackerel (i.e., the distributions of egg diameters of two species are overlapped). Owing to the possibility of overestimation, it is problematic to use a yearly trend simply estimated from the egg density data as a spawning stock biomass index for stock assessment, which could lead to sources of bias in stock assessment.

\ \ \ \ \ \ \ \ \ \
There are two straightforward approaches to resolving this issue. The first approach is DNA analysis. However, Egg samples are fixed with formalin to preserve their morphological characteristics and this results in DNA fragmentation and protein cross-linking, which makes DNA extraction difficult or impossible (e.g., Goelz et al., 1985; Impraim et al., 1987). The second approach is to use a mixture distribution of the eggs of chub mackerel and spotted mackerel which contains the temporal changes in egg diameters of two species. However, this is difficult on a practical level owing to complex and interconnected factors, such as spawning times within a given year, age, water temperature, and body condition affect egg diameter, and these may be difficult to obtain by field surveys alone (e.g., spawning times). As another solution, we modelled the species identification error by linking the catchability of egg density of spotted mackerel to the egg density of chub mackerel, because the recent increase of chub mackerel abundance may result in identification error for spotted mackerel egg. That is, an unexpected increase in the egg density of spotted mackerel is virtually replaced by the increase in catchability of the spotted mackerel eggs.

\ \ \ \ \ \ \ \ \ \
In this paper, we demonstrate a method for reducing identification error by using the state-of-the-art spatio--temporal standardization method (Thorson 2019). Our {new application substantially reduced the bias that would have been caused by the species misidentification of spawning eggs between chub mackerel and spotted mackerel and led to considerable improvement in the stock assessment of spotted mackerel in the western North Pacific. To quantify the effect of species misidentification, we estimated the indices of egg density for spotted mackerel both with and without incorporation of the effect of the egg density of chub mackerel on the catchability of spotted mackerel, using 15 years data of spawning eggs. We then examined how retrospective biases of three measurements of stock abundance (total number of individuals, total stock biomass, and spawning stock biomass; SSB) changed when we used the estimated indices for a stock assessment model. We tested the hypothesis that the retrospective bias should be lower in the spotted mackerel stock assessment with the egg--abundance index standardized by the spatio--temporal model incorporating chub mackerel egg density as a catchability covariate.

\ \\

\section{Materials and Methods}
\subsection{Data sets}
\flushleft{\textbf{2.1.1 Survey and data}}\\
The egg density data with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution in the areas from $\textrm{122}^\circ$E to $\textrm{150}^\circ$E and $\textrm{24}^\circ$N to $\textrm{43}^\circ$N was used. The egg density data set was derived from monthly egg surveys off the Pacific coast of Japan from January to June, 2005--2019 (Takasuka et al., 2008a, 2019). The aim of the surveys was to monitor the egg abundance of major small pelagic fish species, including chub mackerel and spotted mackerel, so that the spatial area and survey month of the data largely covered the major spawning grounds and spawning season. While some sampling locations were fixed, others varied for various reasons (e.g., environmental conditions). Accordingly, the survey design changed slightly each year (Kanamori et al., 2019). Although the sampling efforts were approximately consistent year-round, the efforts tended to be more intensive during early spring; effort was highest in February and decreased gradually thereafter (Takasuka et al., 2008b).

\ \ \ \ \ \ \ \ \ \
The egg surveys were conducted by 18 prefectural experimental stations or fisheries research institutes and two national research institutes of the Japan Fisheries Research and Education Agency, following the consistent sampling designs, as a part of the stock assessment project. In the surveys, plankton nets were towed vertically from a depth of ~150 m to the surface (if the depth was <150 m, nets were lowered to just above the bottom). This range of depths covers the vertical distributions of eggs of small pelagic fish. During the period from 2005 to 2019, the surveys used a plankton net with a mouth ring diameter of 0.45 m and a mesh size of 0.335 (partially 0.330 mm in 2015) (Takasuka et al., 2017). The samples were fixed with 5\% formalin immediately after collection. In the laboratory, the samples were identified and sorted into eggs and larvae of different small pelagic species, based on the morphological characteristics (e.g., egg shape and size, number of oil globules, segmented yolk, perivitelline space ranging, yolk diameter, oil globule diameter). For the mackerel eggs, the egg diameters were measured to the nearest 0.025 mm by a micrometer for a maximum number of 100 individuals per sample (station or tow). Eggs with diameters $>$1.1 mm were identified as spotted mackerel, whereas those with diameters $leq$1.0 mm were identified as chub mackerel, according to Nishida et al. (2001). For any sample of $>$100 individuals, the proportion of the two species among 100 randomly selected individuals was assumed to be the same for the whole sample. Additionally, the number of eggs per unit area in the water column (number $\mathrm{m^{-2}}$) for each sampling tow was calculated by flow-meter revolutions, flow-meter revolutions per meter tow in the calibration, wire length (m), opening mouth area of the net  ($\mathrm{m^{-2}}$), and wire angle. Then, the arithmetic average of the number of eggs was obtained with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution.
\textcolor{red}{The mean proportion of the total number of eggs of spotted mackerel against the total number of eggs of \textit{Scomber} was less than 20 \% from 2005 to 2019. Therefore, the effect of the misidentification error that we considered was from chub mackerel on spotted mackerel (i.e., we assumed that the effect of the misidentification error from spotted  mackerel on chub mackerel was small.)} More detailed descriptions of the surveys and data set are provided in previous studies of the reproductive biology of small pelagic fish species (e.g., Takasuka et al. 2008a,b, 2017, 2019).

\subsection{Data analyses}
\flushleft{\textbf{2.2.1 Indices of egg density}}\\
In this study, we used the three indices of egg density of spotted mackerel; nominal, chub--, and chub+. The nominal index was the arithmetic mean of egg density for each year. The chub-- index was the estimated egg density by considering sampling effects (i.e., spatio--temporal changes in survey design). The chub+ index was the estimated egg density by considering sampling effects and the effect of egg density of chub mackerel on the catchability of egg density of spotted mackerel. The process for estimating chub-- and the chub+ is described in the following section.

\flushleft{\textbf{2.2.2 Estimation of the indices of egg density}}\\
To estimate the chub-- and the chub+ indices of egg density by considering sampling effects (i.e., spatio--temporal changes in survey design) as well as the effect of the egg density of chub mackerel on the catchability of egg density of spotted mackerel, we used the multivariate vector autoregressive spatio-temporal (VAST) model (Thorson and Barnett, 2017), which accounts for spatio-temporal changes in survey design, survey effort, and observation rates and can accurately estimate relative local densities at high resolution by standardizing sampling designs (Thorson and Barnett, 2017; Thorson, 2019). The model includes two potential components because it is designed to support delta-models: (i) the encounter probability $p_{i}$ for each sample $i$ and (ii) the expected egg density $d_{i}$ for each sample $i$ when spawning occurs (i.e., egg density is not zero). The encounter probability $p_{i}$ and the expected egg density $d_{i}$ are, respectively, approximated using a logit-linked linear predictor and a log-linked linear predictor as follows (Thorson and Barnett, 2017):
%\[
\begin{equation}
\begin{array}{ll}
\mathrm{logit}\ p_{i} = \beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i}) + \lambda_{p}Q(i)\\
%\]
%\[
\log d_{i} = \beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i}) + \lambda_{d}Q(i)
%\]
\end{array}
\end{equation}
where $\beta(t_{i})$ is the intercept for year $t$, and $\omega(s_{i})$ and $\varepsilon(s_{i}, t_{i})$ are the spatial and spatio--temporal random effects for year $t$ and location $s$, respectively. $\eta(v_{i})$ is the overdispersion random effect of factor $v_{i}$, which is the interaction of year and month.
$\lambda$ is the effect of the chatchability covariate $Q(i)$:
\[
%Q(i) = \mathrm{log} (\mathrm{chub\,mackerel\,egg\,density}(s_{i})+0.1).
Q(i) = \mathrm{log} (d_{chub}(s_{i})+0.1).
\]
That is, this term considers the effect of species misidentification between chub mackerel and spotted mackerel; as mentioned earlier, we suspected overestimation of egg density of spotted mackerel because the difference in egg diameter has become ambiguous according to increase in egg density of chub mackerel and the distributions of egg diameters between species have overlapped (Yukami et al., 2019). The constant 0.1 was added because $\mathrm{log} 0$ (i.e., no chub mackerel eggs) is undefined, and the same result was obtained when using $1$ in place of $0.1$.

\ \ \ \ \ \ \ \ \ \
The probability density function of $\omega(\cdot)$ is a multivariate normal distribution $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function. The probability density function of $\varepsilon(s_{i}, t_{i})$ is
\[\
\varepsilon(\cdot, t_{i}) \sim \left\{
\begin{array}{ll}
\mathrm{MVN}(0, \mathbf{R}), &if \;t = 1\\
\mathrm{MVN}(\rho_{\varepsilon} \varepsilon(\cdot, t-1_{i}), \mathbf{R}), &if \;t > 1 \\
\end{array} \right.
. \]
Here, we set $\rho_{\varepsilon} = 0$ under the assumption that the year was independent. Therefore, the probability density function of $\eta(v_{i})$ is $\eta(v_{i}) \sim \mathrm{N}(0, 1)$.

\ \ \ \ \ \ \ \ \ \
For computational reasons, the spatio-temporal variation $\varepsilon_{p}(s_{i}, t_{i})$ was approximated as being piecewise constant at a fine spatial scale. We used a k-means algorithm to identify 200 locations (termed ``knots'') to minimize the total distance between the location of sampling data (Thorson et al., 2015) using R-INLA software (Lindgren, 2012). The number of knots was increased to the greatest extent possible, and similar results were obtained for low knots (= 100; Akaike information criterion [AIC] = 6773.01) and high knots (= 200; AIC = 6676.25).

\ \ \ \ \ \ \ \ \ \
Parameters in the VAST model were estimated using the VAST package (Thorson et al., 2015,2016a) in R 3.6.1 (R Development Core Team, 2019). Bias-correction for random effects (Thorson and Kristensen, 2016) was applied when estimating the derived parameters. We evaluated the model diagnostics plots and confirmed that there were no serious problems with the model. The relative egg density in year $t$ at location $s$, $\hat{d}(s, t)$ and the index of egg density in year $t$, $\hat{D}(t)$, were estimated using the predicted values for random effects as follows (Thorson et al., 2017):
\newpage
\[
\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i})]
\]
\[
\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i})],
\]
\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
\]

%\[
%\begin{split}
%\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i}) + \lambda_{p}Q(i)]\\
 %\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i}) + \lambda_{d}Q(i)],
% \end{split}
%\]
%\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
%\]
where $a (s)$ is the area of location $s$. It is noteworthy that  the effect of the catchability covariate $\lambda Q(i)$ in the above equation (1) is removed in the calculation of densities. This means that the abundance index can be derived from the model by removing the bias from the contamination of spotted mackerel eggs with chub mackerel eggs.

\flushleft{\textbf{2.2.3 Estimation of stock abundance}}\\
To examine the validity of the three indices (i.e., nominal index, chub- index, and chub+ index), we estimated the three measurements of stock abundance (total number of individuals, total stock biomass, and SSB) from 1995 to 2018 using a tuned virtual population analysis (VPA). This model is an age-based cohort analysis for estimating the historical abundance and fishing mortality rates from catch-at-age data and has been applied to spotted mackerel in Japan (Yukami et al., 2019). In addition to the three indices of egg density, we used catch-at-age, weight-at-age (not constant over time), maturity-at-age (constant over time) for four age categories (1 to 3, and 4+), the natural mortality coefficient, and a recruitment index following stock assessment in Japan (Yukami et al., 2019). The fishing mortality coefficients other than the terminal age in the terminal year were estimated under the assumption that the selectivity in the latest year was equal to the average selectivity of the prior 5 years (Ichinokawa and Okamura, 2014; Mori and Hiyama, 2014). We confirmed that this assumption did not change our results when using the average selectivity of the prior 3 years as the selectivity in the latest year. The fishing mortality coefficient at each age in the terminal year was estimated by a maximum likelihood method as follows:
\[\sum_{k} \sum_{y} \left[ \frac{\{\mathrm{log}(I_{k,y})-\mathrm{log}(q_{k}X_{k,y})\}^2} {2\sigma^{2}} - \mathrm{log}(\frac{1} {\sqrt{2\pi\sigma^{2}}}) \right]
,\]
where $I_{k,y}$ is the value of index $k$ in year $y$, $q_{k}$ is a proportionality constant, $X_{k,y}$ is the abundance estimate in VPA for index $k$ (i.e., recruitment, and the three indices of egg density), $\sigma^2$ is the variance in fitting the abundance estimate to the index, and $y_{k}$ is the first year of index $k$.

\flushleft{\textbf{2.2.4 Retrospective analysis}}\\
Stock abundance in the terminal year estimated by VPA is notoriously inaccurate and imprecise compared with historical abundance estimates (Okamura et al. 2017). One of the most serious problems is that the stock abundance estimate in the terminal year has temporally systematic bias, i.e., retrospective bias (Hurtado-Ferro et al. 2015). Retrospective analysis is therefore a useful method for detecting such a systematic bias in stock abundance estimate in the terminal year. Dropping the most recent year's data sequentially and then comparing the estimates from a full-year data model and removed data model reveals presence or absence of systematic bias (Mohn 1999). Herein, we conduct a retrospective analysis to evaluate the relative goodness of estimation of stock abundance for} three indices of egg density.

\ \ \ \ \ \ \ \ \ \
To examine improvements in estimations of the three measurements of stock abundance when using the estimated indices of egg density from the VAST model and considering the effect of the chub mackerel, we performed a retrospective analysis by sequentially removing the five most recent years of data from the full data set. Retrospective analysis is usually used in stock assessment models such as VPA to examine the reliability and predictability of stock assessments (e.g., Mohn, 1999; Hashimoto et al., 2018). We calculated Mohn's rho to estimate the biases of the indices of egg density as follows (Mohn, 1999):
\[\rho = \frac{1}{c} \sum_{i}^{c} \left(\frac{B_{y-i}^R - B_{y-i}} {B_{y-i}} \right)
,\]
where $B_{y-i}$ is the value of the year $y-i$ estimate using the full data and $B_{y-i}^R$ is the estimate using the data up to year $y-i$. $c$ is the maximum number of removed years (i.e., $c = 5$). A positive $\rho$ means that the estimate in the terminal year tends to be positively biased on average, and vice versa. Moreover, a $\rho$ close to $0$ means no serious retrospective bias and greatly improved estimation of the stock abundance.

\ \\
\section{Results}
\flushleft{\textbf{3.1 Temporal trend in the indices of egg density}}\\
When comparing the standardized indices (i.e., chub- and chub+ indices) to the nominal index, the standardized indices reduced temporal fluctuation (Fig. 2). Whereas the nominal index increased substantially in 2018, the standardized indices were reduced to a considerable degree. Moreover, the standardized indices for some years, such as 2008, 2009, and 2012, were increased.

\ \ \ \ \ \ \ \ \ \
The model with the effect of chub mackerel egg density on the catchability of spotted mackerel was more parsimonius than the model without the effect of chub mackerel based on AIC (chub+, AIC = 8250.12; chub--, AIC = 8978.81). The coefficient of the effect of chub mackerel on the catchability of spotted mackerel, $\lambda$, indicates a positive effect ($\lambda$ = 0.17). The estimated index with the effect of chub mackerel effect reached a peak in 2008 and decreased gradually thereafter. The value of this index in 2019 was the lowest since 2005 (Fig. 2).

\flushleft{\textbf{3.2 Spatial distribution of the relative egg density}}\\
The relative egg density with the effect of chub mackerel was high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig. 3). In addition, the relative egg density was slightly high off the coast of the Tohoku region. These patterns were consistent during the study period. The relative egg density did not clearly increase or decrease in any area during the study period.

\flushleft{\textbf{3.3 Retrospective analysis}}\\
Recent estimated values of stock abundance (i.e., total numbers of individuals, total biomass, and SSB) differed depending on the indices used, whereas the directions of retrospective bias were sometimes consistent depending on the indices used (Fig. 4). In all the three measurements of stock abundance, the recent estimated values were higher when using the nominal and estimated index without the effect of chub mackerel than using the estimated index with the effect of chub mackerel. The directions of retrospective bias were always positive, independent of the indices used.

\ \ \ \ \ \ \ \ \ \
For all the three measurements of stock abundance (i.e., total numbers of individuals, total biomass, and SSB), retrospective biases clearly improved when using the estimated index with the effect of chub mackerel (Table 1). Values of Mohn's rho, which represents the magnitude and direction of retrospective bias, were similar when using the nominal index and the estimated index without the effect of chub mackerel (Table 1). In contrast, Mohn's rho decreased when using the estimated index with the effect of chub mackerel. The directions of the retrospective bias did not change depending on the indices used because the values of Mohn's rho were always positive.

\ \\
\section{Discussion}
We modelled the species identification error by linking the catchability of spotted mackerel eggs to the egg density of chub mackerel. We found that the model incorporating the effect of the egg density of chub mackerel was better, based on AIC (Fig. 2). In addition, the model showed that the egg density of chub mackerel had a positive effect on the catchability of spotted mackerel. These results suggest the necessity of incorporating the effect of the egg density of chub mackerel when standardizing the egg density of spotted mackerel.

\ \ \ \ \ \ \ \ \ \
Whereas the nominal index increased substantially in 2018, the standardized indices of chub- and chub+ were similarly reduced (Fig. 2). The reduction in both standardized indices, irrespective of whether the effect of the egg density of chub mackerel was incorporated, may be explained by spatio--temporal changes in survey design, survey effort, and observation rate by the VAST model. Indeed, the surveys in 2018 were conducted. by chance, at the site with a high egg density of spotted mackerel (Yukami et al., 2019), which was spatially smoothed by considering the spatial correlation using the VAST model. Hence, we think that the nominal index in 2018 included both species identification bias and spatio--temporal bias from the survey.

\ \ \ \ \ \ \ \ \ \
The retrospective biases in all the three measurements of stock abundance were clearly improved when using the estimated index that incorporates the effect of chub mackerel; the magnitude of the retrospective biases decreased by about half compared with those for the other indices (Fig. 4 and Table 1). These results suggest that our new application is effective for reducing the bias in species misidentification and greatly improves stock estimation, especially for pelagic eggs, which have relatively minor differences in shape and size for species identification.
\textcolor{red}{The samples are usually fixed with formalin to preserve their morphological characteristics, which makes DNA extraction difficult or impossible due to DNA fragmentation and protein cross-linking (e.g., Goelz et al., 1985; Impraim et al., 1987).} Accordingly, samples collected prior to the development of DNA techniques cannot used for DNA analysis. In contrast, our new method requires only the geographic locations and ``prior-" information, such as the species name (which can be based on morphological characteristics), to use various data types, such as survey data for eggs and larvae collected in the ICES area. Thus, our method should be of great benefit in fisheries science.

\ \ \ \ \ \ \ \ \ \
Our results can play an important role in the actual management of spotted mackerel. The stock status and management of this species have received substantial attention in Japan because this species is one of the nine TAC (total allowable catch) species, whose catches are strictly managed according to output control. In fact, a new harvest control rule based on maximum sustainable yield (MSY) was implemented in 2020 (Yukami et al. 2020). The stock abundance of spotted mackerel has been decreasing in recent years, and positive retrospective bias caused overestimates of abundance in the terminal year in a previous stock assessment using an unstandardized index of spawning eggs (Yukami et al. 2019). This indicates that the allowable biological catch (ABC) was also overestimated, and this may have led to overfishing.
The stock assessments with the nominal and chub- indices would estimate, respectively, 140 and 105 thousand tons as ABC in 2020, whilst that with the chub+ index would derive 38 thousand tons as ABC in 2020. The present study found that the retrospective bias was considerably reduced in the stock assessment with the chub+ index and this approach would therefore contribute to the derivation of an adequate ABC. Although the current status is overfishing and overfished (Yukami et al. 2020), it is expected that the Pacific stock of spotted mackerel will show a recovery to a level that produces the MSY by using our assessment method and the new Harvest Control Rules.

\ \ \ \ \ \ \ \ \ \
Although detailed information on spawning grounds is necessary for understanding fluctuations in recruitment as well as for providing a basis for stock management, prior data for spotted mackerel has not been reliable. For example, some studies have reported that the area around the Izu Islands may not be a suitable spawning ground for spotted mackerel because few eggs have been observed (Yukami et al. 2019). In contrast, it is possible that the spotted mackerel spawns around the Izu Islands because the estimated hatch day and the spatial distribution of spotted mackerel at the Kuroshio--Oyashio transition area were similar to those of chub mackerel, which spawns around mainly the Izu Islands (Takahashi et al., 2010). The present study showed that the relative egg density, which was estimated using the better model, was equally high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig. 3), providing direct evidence that the area around the Izu Islands are also a major spawning ground of spotted mackerel. It is possible that spotted mackerel spawn in the area around the Izu Islands because they are not sensitive to rising water temperatures and they are generally distributed farther south than chub mackerel (Mitani et al., 2002). Indeed, although both spotted mackerel and chub mackerel spawn at the same time around the Izu Islands (Tanoue et al., 1960; Hanai and Meguro, 1997), the reproductive phenology of chub mackerel has changed due to rising sea surface temperatures associated with climate change; since 2000, chub mackerel migrate to their feeding ground earlier and spawn father northward (Kanamori et al., 2019).

\ \ \ \ \ \ \ \ \ \
Understanding migration patterns is necessary for conducting stock assessments (Crossin et al., 2017). It has been assumed that the spawning grounds of spotted mackerel change with age; individuals migrate from around the Izu Islands to the Kuroshio--Oyashio transition area to feed before spawning at 2 years of age (Nishida et al., 2000; Kawabata et al. 2008). Adults that have spawned gradually migrate westward, using the spawning grounds off the coast of Kyushu and Shikoku (Hanai, 1999; Nashida et al., 2006). Although the number of recruits were particularly high in 2004 and 2009 (Yukami et al., 2019), we did not find evidence for an increase in the relative egg density around the Izu Islands in 2006 and in 2011 or the other spawning grounds after 2007 and 2012 (Fig. 3). One explanation for this is that the migration range of spotted mackerel is narrower than we assumed. Previous studies have reported that spotted mackerel remains around the Izu Islands and off the coast of Shikoku (Hanai, 1999; Nashida et al., 2006). Another explanation is that part of a strong year may remain in another area due to the expansion of the spatial distribution resulting from an increase number in recruitments. For example, Kawabata et al. (2008) reported that the 2004 year class migrated for feeding and overwintering until at least 3 years old over the Emperor Seamounts (around $\textrm{165}-\textrm{170}^{\circ}$E and $\textrm{30}-\textrm{55}^{\circ}$N). Testing these hypotheses will be the subject of future research and should improve our understanding of the migratory patterns of the spotted mackerel, which in turn should improve stock assessment and management.
\ \\

\ \\
\flushleft{\textbf{\Large{Conclusion}}}\\
This study showed that indices of egg density of spotted mackerel, which were standardized using a spatio--temporal model, reduced temporal fluctuation. In particular, the standardized indices in 2018 were reduced to a considerable degree compared with the nominal index. The model incorporating the effect of chub mackerel egg density on the catchability of spotted mackerel (i.e., the model incorporating species misidentification bias) was the better model according to the AIC. In addition, the retrospective bias decreased by about half when using the egg density index from the better model. These results suggest that incorporating species misidentification bias is an essential process for improving stock assessment.

\ \\
%\setstretch{1}
\flushleft{\textbf{\Large{Acknowledgments}}}\\
This research was financiallysupportted by the grants from the Japan Society for the Promotion of Science (JSPS) (19K15905, 20392904).
\ \\

%\flushleft{\textbf{\Large{Authorship}}}\\
%YK conceived of the research idea. AT and MW conducted field sampling. YK, SN, and HO designed statistical analyses. YK and SN wrote programs and performed the analyses. YK wrote the manuscript with input from all co-authors' comments.
\ \\

%\setstretch{1}
\flushleft{\textbf{\Large{Literature cited}}}\\
\hangindent=30pt
\noindent
Crossin, G.T., Cooke, S.J., Goldbogen, J.A., Phillips, R.A. 2014. Tracking fitness in marine vertebrates: current knowledge and opportunities for future research. Mar. Ecol. Prog. Ser. 496:1-17.

\hangindent=30pt
\noindent
Elphick, C.S. 2008. How you count counts: the importance of methods research in applied ecology. J. Appl. Ecol. 45:1313-1320.

\hangindent=30pt
\noindent
Garcia-Vazquez, E., Machado-Schiaffino, G., Campo ,D., Juanes, F. 2012. Species misidentification in mixed hake fisheries may lead to overexploitation and population bottlenecks. Fish. Res. 114:52-55.

\hangindent=30pt
\noindent
Goelz, S.E., Hamilton, S.R., Vogelstein, B. 1985. Purification of DNA from formaldehyde fixed and paraffin embedded human tissue. Biochem. Biophys. Res. Commun. 130:118–126.

\hangindent=30pt
\noindent
Hashimoto, M., Nishijima, S., Yukami, R., Watanabe, C., Kamimura, Y., Furuichi, S., Ichinokawa, M., Okamura, H. 2019. Spatiotemporal dynamics of the Pacific chub mackerel revealed by standardized abundance indices. Fish. Res. 219:105315.

\hangindent=30pt
\noindent
Hashimoto, M., Okamura, H., Ichinokawa, M., Hiramatsu, K., Yamakawa, T. 2018. Impacts of the nonlinear relationship between abundance and its index in a tuned virtual population analysis. Fish. Sci. 84:335-347.

\hangindent=30pt
\noindent
Hurtado-Ferro, F., Szuwalski, C.S., Valero. J.L., Andderson. S.C., Cunningham, C.J., Johnson, K.F., Licandeo, R.L., McGilliard, C.R., Monnahan, C.C., Muradian, M.L., Ono, K., Vert-Pre, K.A., Whitten, A.R., Punt, A.E. 2015. Looking in the review mirror: bias and retrospective patterns in integrated, age-structured stock assessment models. ICES J. Mar. Sci. 72:99-110.

\hangindent=30pt
\noindent
Ichinokawa, M., Okamura, H. 2014. Review of stock evaluation methods using VPA for fishery stocks in Japan: implementation with R. Bull. Jpn. Soc. Fish. Oceanogr. 78:104-113 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Impraim, C.C., Saiki. R.K., Erlich, H.A., Teplitz, R.L. 1987. Analysis of DNA extracted from formalin-fixed, paraffin-embedded tissues by enzymatic amplification and hybridization with sequence-specific oligonucleotides. Biochem. Biophys. Res. Commun. 142:710–716.

\hangindent=30pt
\noindent
Kanamori, Y., Takasuka, A., Nishijima, S., Okamura, H. 2019. Climate change shifts the spawning ground northward and extends the spawning period of chub mackerel in the western North Pacific. Mar. Ecol. Prog. Ser. 624:155-166.

\hangindent=30pt
\noindent
Ko, H.L., Wang, Y.T., Chiu, T.S., Lee, M.A., Leu, M.Y., Chang, K.Z. et al. 2013. Evaluating the accuracy of morphological identification of larval fishes by applying DNA barcoding. PLoS ONE 8:e53451.

\hangindent=30pt
\noindent
Lindgren, F. 2012. Continuous domain spatial models in R-INLA. ISBA Bull. 19:14-20.

\hangindent=30pt
\noindent
MacKenzie, D.I., Nichols, J.D., Lanchman, G.B., Droege, S., Royle, J.A., Langtimm, C.A. 2002. Estimating site occupancy rates when detection probabilities are less than one. Ecology 83:2248-2255.

\hangindent=30pt
\noindent
Marko, P.B., Lee, S.C., Rice, A.M., Gramling, J.M., Fitzhenry, T.M., McAlister, J.S., Harper, G.R., Moran, A.L. 2004. Mislabelling of a depleted reef fish. Nature 430:309-310.

\hangindent=30pt
\noindent
Matarese, A.C., Spies, I.B., Busby, M.S., Orr, J.W. 2011. Early larvae of \textit{Zesticelus profundorum} (family Cottidae) identified using DNA barcording. Ichthyol. Res. 58: 170-174.

\hangindent=30pt
\noindent
Mohn, R. 1999. The retrospective problem in sequential population analysis: an investigation using cod fishery and simulated data. ICES J. Mar. Sci. 56:473-488.

\hangindent=30pt
\noindent
Mori, K., Hiyama, Y. 2014. Stock assessment and management for walleye pollock in Japan. Fish. Sci. 80:161-172.

\hangindent=30pt
\noindent
Nishida, H., Wada, T., Oozeki, Y., Sezaki, K., Saito, M. 2001. Possibility of identifying chub mackerel and spotted mackerel by measuring diameter of mackerel eggs. Nippon Suisan Gakkaishi, 67: 102-104.

\hangindent=30pt
\noindent
Okamura, H., Yamashita, Y., Ichinokawa, M. 2017. Ridge virtual population analysis to reduce the instability of fishing mortalities in the terminal year. ICES J. Mar. Sci. 74:2427-2436.

\hangindent=30pt
\noindent
R Development Core Team, 2019. R: a language and envi- ronment for statistical computing. R Foundation for Sta- tistical Computing, Vienna.

\hangindent=30pt
\noindent
Takahashi, M., Takagi, K,, Kawabata, A., Watanabe, C., Nishida, H., Yamashita, N., Mori, K., Suyama, S., Nakagami, M., Ueno, Y., Saito, M. 2010. Estimated hatching season of the Pacific stock of chub mackerel \textit{Scomber japonicus} and spotted mackerel \textit{S. australasicus} in 2007. Fisheries biology and oceanography in the Kuroshio 11:49-54 (in Japanese).

\hangindent=30pt
\noindent
Takasuka, A., Kubota, Hm., Oozeki, Y. 2008a. Spawning overlap of anchovy and sardine in the western North Pacific. Mar. Ecol. Prog. Ser. 366:231-244.

\hangindent=30pt
\noindent
Takasuka, A., Oozeki, Y., Kubota, H. 2008b. Multi-species regime shifts reflected in spawning temperature optima of small pelagic fish in the western North Pacific. Mar. Ecol. Prog. Ser. 360:211-217.

\hangindent=30pt
\noindent
Takasuka, A., Tadokoro, K., Okazaki, Y., Ichikawa, T., Sugisaki, H., Kuroda, H., Oozeki, Y. 2017. In situ filtering rate vari- ability in egg and larval surveys off the Pacific coast of Japan: Do plankton nets clog or over-filter in the sea? Deep-Sea Res. I 120:132−137.

\hangindent=30pt
\noindent
Takasuka, A., Yoneda, M., Oozeki, Y. 2019. Density depend- ence in total egg production per spawner for marine fish. Fish. Fish. 20:125−137.

\hangindent=30pt
\noindent
Thorson, J.T. 2019.  Guidance for decisions using the Vector Autoregressive Spatio-Temporal (VAST) package in stock, ecosystem, habitat and climate assessments. Fish. Res. 210:143-161.

\hangindent=30pt
\noindent
Thorson, J.T., Barnett, L.A.K. 2017. Comparing estimates of abundance trends and distribution shifts using single- and multispecies models of fishes and biogenic habitat. ICES J. Mar. Sci. 74:1311−1321.

\hangindent=30pt
\noindent
Thorson, J.T., Kristensen, K. 2016. Implementing a generic method for bias correction in statistical models using ran- dom effects, with spatial and population dynamics exam- ples. Fish. Res. 175: 66–74.

\hangindent=30pt
\noindent
Thorson, J.T., Shelton, A.O., Ward, E.J., Skaug, H.J. 2015. Geostatistical delta-generalized linear mixed models improve precision for estimated abundance indices for West Coast groundfishes. ICES J. Mar. Sci. 72:1297−1310.

\hangindent=30pt
\noindent
Victor, B.C., Hanner, R., Shivji, M., Hyde, J., Caldow, C. 2009. Identification of the larval and juvenile stages of the cubera snapper, \textit{Lutignus cyanopterus}, using DNA barcoding. Zootaxa 2215:24-36.

\hangindent=30pt
\noindent
Watanabe, C., Hanai, T., Meguro, K., Ogino, R., Kubota, Y., Kimura, R. 1999. Spawning biomass estimates of chub mackerel \textit{Scomber japonicus} of Pacific subpopulation off central Japan by a daily egg production method. Nippon Suisan Gakkaishi 65: 695-702 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Watanabe, C., Nishida, H. 2002. Development of assessment techniques for pelagic fish stocks: applications of daily egg production method and pelagic trawl in the northwestern Pacific Ocean. Fish. Sci. 68:97-100.

\hangindent=30pt
\noindent
Watanabe, C., Yatsu, A. 2006. Long-tem changes in maturity at age of chub mackerel (\textit{Scomber japonicus}) in relation to population declines in the waters off northeastern Japan. Fish. Res. 78:323-332.

\hangindent=30pt
\noindent
Watanabe, T., 1970. Morphology and ecology of early stages of life in Japanese common mackerel, \textit{Scomber japonicus} HOUTTUYN, with special reference to fluctuation of population. Bull. Tokai Reg. Fish. Res. Lab. 62:1-283 (in Japanese with English abstract).

\hangindent=30pt
\noindent
Williams, B.K., Nichols, J.D., Conroy, M.J. 2002. Analysis and management of animal population. Academic Press, New York.

\hangindent=30pt
\noindent
Yukami, R., Isu, S., Watanabe, C., Kamimura, Y., Furuichi, S. 2019. Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2018). In: Marine fisheries stock assessment and evaluation for Japanese waters (2018/ 2019). Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa, p 248−278 (in Japanese).

\hangindent=30pt
\noindent
Yukami, R., Isu. S., Kamimura, Y., Furuichi, S., Watanabe, R., Kanamori, Y. 2020. Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2019). In: Marine fisheries stock assessment and evaluation for Japanese waters (2019/ 2020). Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa (in Japanese).

\newpage
\flushleft{\textbf{\Large{Captions}}}\\
\flushleft{\textbf{Fig. 1}} Study area. Spotted mackerel \textit{Scomber australasicus} in the western North Pacific spawns around Kyushu, Shikoku, and the Izu Islands in Japan. Adults and their offspring are then transported to their feeding ground by the Kuroshio Current.
\ \\
\flushleft{\textbf{Fig. 2}} Temporal trends in indices of egg density. The gray line represents the scaled nominal index, the blue line represents the estimated index without the effect of chub mackerel, and the red line represents the estimated index with the effect of chub mackerel. Vertical bars are 95\% confidence intervals of the estimated indices.
\ \\
\flushleft{\textbf{Fig. 3}} Temporal changes in the spatial distribution of relative egg density, \textcolor{red}{as} estimated using the model with the effect of chub mackerel.
\ \\
\flushleft{\textbf{Fig. 4}} Retrospective patterns of total numbers of individuals, total biomass, and spawning stock biomass (SSB). Color differences denote differences in sequentially removing data for the five most recent years (blue, light blue, green, orange, and red indicate removal of data for years 1 to 5 years, respectively) from the full data set (gray).
\ \\

\end{linenumbers}
\end{document}

### 2021-03-09 results/draft.tex
added

@@
 \section{Introduction}
-Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology. Environmental DNA (eDNA)
+Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
+Field survey using environmental DNA (eDNA) is recently widely used for detecting invesive or rare species and hotspot of biodiversity because eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method such as visual.
+%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
+The presence/absence of eDNA, however, includes many types of
 

### 2021-03-09 results/draft.tex
wrote the first paragraph

--- 2021-03-09 results/draft.tex
@@
 \section{Introduction}
-Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology. Environmental DNA (eDNA)
+Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
+Field surveys using environmental DNA (eDNA) are widely used for detecting invesive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
+2014; Thomsen \& Willerslev 2015 #Dorazioに引用されていたやつ．あとで再確認).
+%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
+The presence/absence of eDNA, however, includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
+For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
+Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.
 

### 2021-03-09 results/draft.tex
wrote the paragraph of joint model

@@
 \ \ \ \ \ \ \ \ \ \
-Accurate species identification of fish eggs and larvae is essential for elucidating the ecology of the early life--history of fish, including the location and timing of fish spawning, hatching, and migration (Ko et al., 2013).
-Such information can improve the inference and forecasting of fish population size.
-Morphological characteristics used for species identification have traditionally been the size and oil globules of eggs, and the body shape, pigmentation, and meristic count of larvae (e.g., Matarese and Sandknop, 1984; Ko et al., 2013).
-However, species identification based on these morphological characteristics leads to species misidentification because these morphological characteristics are likely to overlap among species in early life--history (e.g., Victor et al., 2009; Ko et al., 2013).
-For example, when we use size of eggs as a morphological measure, we often classify eggs by whether their diameters are greater than or less than a predetermined value.
-However, because distributions of diameters are likely to overlap among species, some eggs may be erroneously classified as different species.
-In addition, morphological characteristics can change during developments, so that individuals of the same species at different development stages can be misidentified as a different species (Ko et al., 2013).
+One step towards overcoming these uncertinties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies
 
 \ \ \ \ \ \ \ \ \ \
-Spotted mackerel \textit{Scomber australasicus} and chub mackerel \textit{Scomber japonicus} are small pelagic fish that are widely distributed in the western North Pacific (ca.
-$\textrm{120}-\textrm{150}^{\circ}$E, Fig.
-1; Watanabe and Yatsu, 2006).
-These species spawn in waters near the Kuroshio Current from winter to summer (e.g., Watanabe, 1970; Watanabe et al., 1999; Watanabe and Yatsu, 2006), after which the adults and their offspring are transported to their feeding ground by the Kuroshio Current (e.g., Watanabe and Nishida, 2002).
-Because Nishida (2001) suggested that egg diameter differs between the two species, species identification based on egg diameter has been conducted routinely since 2005; eggs smaller than 1.1 mm in diameter were classified as chub mackerel and vice versa.
-These eggs, which were identified according to this basis, have been used as the indices of the spawning stock biomass of spotted mackerel and chub mackerel for stock assessment.
-However, the recent egg density of spotted mackerel was considerably high although stock biomass and spawning stock biomass has been low (Yukami et al., 2019).
-This considerable increase in the egg density of spotted mackerel is likely the result of overestimation because the difference in egg diameter has become ambiguous according to the increase in the egg density of chub mackerel and overlapping the distributions of egg diameters in the two species (Yukami et al., 2019).
-That is, the boundary between the left tail of the distribution of egg diameters of spotted mackerel and the right tail of the distribution of egg diameters of chub mackerel is clear when egg density of chub mackerel is low.
-In contrast, this boundary becomes unclear when egg density of chub mackerel increases because the whole of the distribution of egg diameters of chub mackerel becomes large and includes the distribution of egg diameters of spotted mackerel (i.e., the distributions of egg diameters of two species are overlapped).
-Owing to the possibility of overestimation, it is problematic to use a yearly trend simply estimated from the egg density data as a spawning stock biomass index for stock assessment, which could lead to sources of bias in stock assessment.
+Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
+The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data wihch is widely collected and abundant, and combine in a single model (Isaac et al.
+2020; Miller et al.
+2019).
+
+The models combine the different type of data with strengths and weaknesses in a single model ().
+For example, scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
+Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when we use single data (Pacifici et al. 2017; Miller et al. 2019).
 

### 2021-03-09 results/draft.tex
small changes

@@
 %Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
-The presence/absence of eDNA, however, includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
+However, the presence/absence of eDNA includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
 For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.

### 2021-03-09 results/draft.tex
wrote the paragraph of Tokyo Bay

@@
 \ \ \ \ \ \ \ \ \ \
-There are two straightforward approaches to resolving this issue.
-The first approach is DNA analysis.
-However, Egg samples are fixed with formalin to preserve their morphological characteristics and this results in DNA fragmentation and protein cross-linking, which makes DNA extraction difficult or impossible (e.g., Goelz et al., 1985; Impraim et al., 1987).
-The second approach is to use a mixture distribution of the eggs of chub mackerel and spotted mackerel which contains the temporal changes in egg diameters of two species.
-However, this is difficult on a practical level owing to complex and interconnected factors, such as spawning times within a given year, age, water temperature, and body condition affect egg diameter, and these may be difficult to obtain by field surveys alone (e.g., spawning times).
-As another solution, we modelled the species identification error by linking the catchability of egg density of spotted mackerel to the egg density of chub mackerel, because the recent increase of chub mackerel abundance may result in identification error for spotted mackerel egg.
-That is, an unexpected increase in the egg density of spotted mackerel is virtually replaced by the increase in catchability of the spotted mackerel eggs.
+Tokyo Bay is a large enclosed coastal sea in Japan.
+In Tokyo Bay, there are many useful species for fisheries that are colled "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago).
+Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution).
+Catch statistics (total catch in each fish, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay, which is widely collected and abundant.
+In addition, scientific survey of eDNA has been conducted monthly in same points since 2018 for monitoring biodiveristy (Hongo et al., submitted).
 

### 2021-03-10 results/draft.tex
small changes
tidy up

@@
 Field surveys using environmental DNA (eDNA) are widely used for detecting invesive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
-2014; Thomsen \& Willerslev 2015 #Dorazioに引用されていたやつ．あとで再確認).
+2014; Thomsen \& Willerslev 2015 %Dorazioに引用されていたやつ．あとで再確認).
 %Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
@@
 Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
-The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data wihch is widely collected and abundant, and combine in a single model (Isaac et al.
+The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al.
 2020; Miller et al.
@@
 Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution).
-Catch statistics (total catch in each fish, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay, which is widely collected and abundant.
-In addition, scientific survey of eDNA has been conducted monthly in same points since 2018 for monitoring biodiveristy (Hongo et al., submitted).
+Catch statistics (total catch in each species, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay.
+The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay, Japan.
+On the other hand, weakness of this data is like a opportunistic data because the data is likely to be biased towards areas to high density of focal species due to commercially fishes, consequently less zero data.
+In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes (Hongo et al., submitted).
+The strengths are that the data is systematically collected because of scientific survey data and includes zero data, while the weaknesses are that the data is less abundant and includes uncertinties in presence/absence as description in above.
 
 \ \ \ \ \ \ \ \ \ \ 
-In this paper, we demonstrate a method for reducing identification error by using the state-of-the-art spatio--temporal standardization method (Thorson 2019).
-Our {new application substantially reduced the bias that would have been caused by the species misidentification of spawning eggs between chub mackerel and spotted mackerel and led to considerable improvement in the stock assessment of spotted mackerel in the western North Pacific.
-To quantify the effect of species misidentification, we estimated the indices of egg density for spotted mackerel both with and without incorporation of the effect of the egg density of chub mackerel on the catchability of spotted mackerel, using 15 years data of spawning eggs.
-We then examined how retrospective biases of three measurements of stock abundance (total number of individuals, total stock biomass, and spawning stock biomass; SSB) changed when we used the estimated indices for a stock assessment model.
-We tested the hypothesis that the retrospective bias should be lower in the spotted mackerel stock assessment with the egg--abundance index standardized by the spatio--temporal model incorporating chub mackerel egg density as a catchability covariate.
+%In this paper, we make an integrated spatial distribution model by combining both catch statistics, which is opportunistic data but abundant and represents the direct evidence where fish was, and eDNA data, which is the monitoring data in the same points but not abundant and includes uncertinties due to environmental factors.
+
+%In this paper, we make the model considering with uncertinties caused by environmental factors, such as temperature and advection, to predict spatial distribution of species using an integrated spatial distribution model.
+
+In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertinties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model.
+We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan.
+The predicted spatial distribution of four fish form our model reduced
 
@@
 
-\ \ \ \ \ \ \ \ \ \
-The probability density function of $\omega(\cdot)$ is a multivariate normal distribution $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function.
-The probability density function of $\varepsilon(s_{i}, t_{i})$ is
-\[\
-\varepsilon(\cdot, t_{i}) \sim \left\{
-\begin{array}{ll}
-\mathrm{MVN}(0, \mathbf{R}), &if \;t = 1\\
-\mathrm{MVN}(\rho_{\varepsilon} \varepsilon(\cdot, t-1_{i}), \mathbf{R}), &if \;t > 1 \\
-\end{array} \right.
-. \]
-Here, we set $\rho_{\varepsilon} = 0$ under the assumption that the year was independent. Therefore, the probability density function of $\eta(v_{i})$ is $\eta(v_{i}) \sim \mathrm{N}(0, 1)$.
-
-\ \ \ \ \ \ \ \ \ \
-For computational reasons, the spatio-temporal variation $\varepsilon_{p}(s_{i}, t_{i})$ was approximated as being piecewise constant at a fine spatial scale.
-We used a k-means algorithm to identify 200 locations (termed ``knots'') to minimize the total distance between the location of sampling data (Thorson et al., 2015) using R-INLA software (Lindgren, 2012).
-The number of knots was increased to the greatest extent possible, and similar results were obtained for low knots (= 100; Akaike information criterion [AIC] = 6773.01) and high knots (= 200; AIC = 6676.25).
-
-\ \ \ \ \ \ \ \ \ \
-Parameters in the VAST model were estimated using the VAST package (Thorson et al., 2015,2016a) in R 3.6.1 (R Development Core Team, 2019).
-Bias-correction for random effects (Thorson and Kristensen, 2016) was applied when estimating the derived parameters.
-We evaluated the model diagnostics plots and confirmed that there were no serious problems with the model.
-The relative egg density in year $t$ at location $s$, $\hat{d}(s, t)$ and the index of egg density in year $t$, $\hat{D}(t)$, were estimated using the predicted values for random effects as follows (Thorson et al., 2017):
-\newpage
-\[
-\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i})]
-\]
-\[
-\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i})],
-\]
-\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
-\]
-
-%\[
-%\begin{split}
-%\hat{d}(s, t) = \mathrm{logit}^{-1}[\beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i}) + \lambda_{p}Q(i)]\\
- %\times \exp[\beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i}) + \lambda_{d}Q(i)],
-% \end{split}
-%\]
-%\[\hat{D}(t) = \sum_{s} a(s) \times \hat{d}(s, t)
-%\]
-where $a (s)$ is the area of location $s$.
-It is noteworthy that  the effect of the catchability covariate $\lambda Q(i)$ in the above equation (1) is removed in the calculation of densities.
-This means that the abundance index can be derived from the model by removing the bias from the contamination of spotted mackerel eggs with chub mackerel eggs.
-
-\flushleft{\textbf{2.2.3 Estimation of stock abundance}}\\
-To examine the validity of the three indices (i.e., nominal index, chub- index, and chub+ index), we estimated the three measurements of stock abundance (total number of individuals, total stock biomass, and SSB) from 1995 to 2018 using a tuned virtual population analysis (VPA).
-This model is an age-based cohort analysis for estimating the historical abundance and fishing mortality rates from catch-at-age data and has been applied to spotted mackerel in Japan (Yukami et al., 2019).
-In addition to the three indices of egg density, we used catch-at-age, weight-at-age (not constant over time), maturity-at-age (constant over time) for four age categories (1 to 3, and 4+), the natural mortality coefficient, and a recruitment index following stock assessment in Japan (Yukami et al., 2019).
-The fishing mortality coefficients other than the terminal age in the terminal year were estimated under the assumption that the selectivity in the latest year was equal to the average selectivity of the prior 5 years (Ichinokawa and Okamura, 2014; Mori and Hiyama, 2014).
-We confirmed that this assumption did not change our results when using the average selectivity of the prior 3 years as the selectivity in the latest year.
-The fishing mortality coefficient at each age in the terminal year was estimated by a maximum likelihood method as follows:
-\[\sum_{k} \sum_{y} \left[ \frac{\{\mathrm{log}(I_{k,y})-\mathrm{log}(q_{k}X_{k,y})\}^2} {2\sigma^{2}} - \mathrm{log}(\frac{1} {\sqrt{2\pi\sigma^{2}}}) \right]
-,\]
-where $I_{k,y}$ is the value of index $k$ in year $y$, $q_{k}$ is a proportionality constant, $X_{k,y}$ is the abundance estimate in VPA for index $k$ (i.e., recruitment, and the three indices of egg density), $\sigma^2$ is the variance in fitting the abundance estimate to the index, and $y_{k}$ is the first year of index $k$.
-
-\flushleft{\textbf{2.2.4 Retrospective analysis}}\\
-Stock abundance in the terminal year estimated by VPA is notoriously inaccurate and imprecise compared with historical abundance estimates (Okamura et al.
-2017).
-One of the most serious problems is that the stock abundance estimate in the terminal year has temporally systematic bias, i.e., retrospective bias (Hurtado-Ferro et al.
-2015).
-Retrospective analysis is therefore a useful method for detecting such a systematic bias in stock abundance estimate in the terminal year.
-Dropping the most recent year's data sequentially and then comparing the estimates from a full-year data model and removed data model reveals presence or absence of systematic bias (Mohn 1999).
-Herein, we conduct a retrospective analysis to evaluate the relative goodness of estimation of stock abundance for} three indices of egg density.
-
-\ \ \ \ \ \ \ \ \ \
-To examine improvements in estimations of the three measurements of stock abundance when using the estimated indices of egg density from the VAST model and considering the effect of the chub mackerel, we performed a retrospective analysis by sequentially removing the five most recent years of data from the full data set.
-Retrospective analysis is usually used in stock assessment models such as VPA to examine the reliability and predictability of stock assessments (e.g., Mohn, 1999; Hashimoto et al., 2018).
-We calculated Mohn's rho to estimate the biases of the indices of egg density as follows (Mohn, 1999):
-\[\rho = \frac{1}{c} \sum_{i}^{c} \left(\frac{B_{y-i}^R - B_{y-i}} {B_{y-i}} \right)
-,\]
-where $B_{y-i}$ is the value of the year $y-i$ estimate using the full data and $B_{y-i}^R$ is the estimate using the data up to year $y-i$.
-$c$ is the maximum number of removed years (i.e., $c = 5$).
-A positive $\rho$ means that the estimate in the terminal year tends to be positively biased on average, and vice versa.
-Moreover, a $\rho$ close to $0$ means no serious retrospective bias and greatly improved estimation of the stock abundance.
-
-\ \\
-\section{Results}
-\flushleft{\textbf{3.1 Temporal trend in the indices of egg density}}\\
-When comparing the standardized indices (i.e., chub- and chub+ indices) to the nominal index, the standardized indices reduced temporal fluctuation (Fig.
-2).
-Whereas the nominal index increased substantially in 2018, the standardized indices were reduced to a considerable degree.
-Moreover, the standardized indices for some years, such as 2008, 2009, and 2012, were increased.
-
-\ \ \ \ \ \ \ \ \ \
-The model with the effect of chub mackerel egg density on the catchability of spotted mackerel was more parsimonius than the model without the effect of chub mackerel based on AIC (chub+, AIC = 8250.12; chub--, AIC = 8978.81).
-The coefficient of the effect of chub mackerel on the catchability of spotted mackerel, $\lambda$, indicates a positive effect ($\lambda$ = 0.17).
-The estimated index with the effect of chub mackerel effect reached a peak in 2008 and decreased gradually thereafter.
-The value of this index in 2019 was the lowest since 2005 (Fig.
-2).
-
-\flushleft{\textbf{3.2 Spatial distribution of the relative egg density}}\\
-The relative egg density with the effect of chub mackerel was high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig.
-3).
-In addition, the relative egg density was slightly high off the coast of the Tohoku region.
-These patterns were consistent during the study period.
-The relative egg density did not clearly increase or decrease in any area during the study period.
-
-\flushleft{\textbf{3.3 Retrospective analysis}}\\
-Recent estimated values of stock abundance (i.e., total numbers of individuals, total biomass, and SSB) differed depending on the indices used, whereas the directions of retrospective bias were sometimes consistent depending on the indices used (Fig.
-4).
-In all the three measurements of stock abundance, the recent estimated values were higher when using the nominal and estimated index without the effect of chub mackerel than using the estimated index with the effect of chub mackerel.
-The directions of retrospective bias were always positive, independent of the indices used.
-
-\ \ \ \ \ \ \ \ \ \
-For all the three measurements of stock abundance (i.e., total numbers of individuals, total biomass, and SSB), retrospective biases clearly improved when using the estimated index with the effect of chub mackerel (Table 1).
-Values of Mohn's rho, which represents the magnitude and direction of retrospective bias, were similar when using the nominal index and the estimated index without the effect of chub mackerel (Table 1).
-In contrast, Mohn's rho decreased when using the estimated index with the effect of chub mackerel.
-The directions of the retrospective bias did not change depending on the indices used because the values of Mohn's rho were always positive.
-
-\ \\
-\section{Discussion}
-We modelled the species identification error by linking the catchability of spotted mackerel eggs to the egg density of chub mackerel.
-We found that the model incorporating the effect of the egg density of chub mackerel was better, based on AIC (Fig.
-2).
-In addition, the model showed that the egg density of chub mackerel had a positive effect on the catchability of spotted mackerel.
-These results suggest the necessity of incorporating the effect of the egg density of chub mackerel when standardizing the egg density of spotted mackerel.
-
-\ \ \ \ \ \ \ \ \ \
-Whereas the nominal index increased substantially in 2018, the standardized indices of chub- and chub+ were similarly reduced (Fig.
-2).
-The reduction in both standardized indices, irrespective of whether the effect of the egg density of chub mackerel was incorporated, may be explained by spatio--temporal changes in survey design, survey effort, and observation rate by the VAST model.
-Indeed, the surveys in 2018 were conducted.
-by chance, at the site with a high egg density of spotted mackerel (Yukami et al., 2019), which was spatially smoothed by considering the spatial correlation using the VAST model.
-Hence, we think that the nominal index in 2018 included both species identification bias and spatio--temporal bias from the survey.
-
-\ \ \ \ \ \ \ \ \ \
-The retrospective biases in all the three measurements of stock abundance were clearly improved when using the estimated index that incorporates the effect of chub mackerel; the magnitude of the retrospective biases decreased by about half compared with those for the other indices (Fig.
-4 and Table 1).
-These results suggest that our new application is effective for reducing the bias in species misidentification and greatly improves stock estimation, especially for pelagic eggs, which have relatively minor differences in shape and size for species identification.
-\textcolor{red}{The samples are usually fixed with formalin to preserve their morphological characteristics, which makes DNA extraction difficult or impossible due to DNA fragmentation and protein cross-linking (e.g., Goelz et al., 1985; Impraim et al., 1987).} Accordingly, samples collected prior to the development of DNA techniques cannot used for DNA analysis.
-In contrast, our new method requires only the geographic locations and ``prior-" information, such as the species name (which can be based on morphological characteristics), to use various data types, such as survey data for eggs and larvae collected in the ICES area.
-Thus, our method should be of great benefit in fisheries science.
-
-\ \ \ \ \ \ \ \ \ \
-Our results can play an important role in the actual management of spotted mackerel.
-The stock status and management of this species have received substantial attention in Japan because this species is one of the nine TAC (total allowable catch) species, whose catches are strictly managed according to output control.
-In fact, a new harvest control rule based on maximum sustainable yield (MSY) was implemented in 2020 (Yukami et al.
-2020).
-The stock abundance of spotted mackerel has been decreasing in recent years, and positive retrospective bias caused overestimates of abundance in the terminal year in a previous stock assessment using an unstandardized index of spawning eggs (Yukami et al.
-2019).
-This indicates that the allowable biological catch (ABC) was also overestimated, and this may have led to overfishing.
-The stock assessments with the nominal and chub- indices would estimate, respectively, 140 and 105 thousand tons as ABC in 2020, whilst that with the chub+ index would derive 38 thousand tons as ABC in 2020.
-The present study found that the retrospective bias was considerably reduced in the stock assessment with the chub+ index and this approach would therefore contribute to the derivation of an adequate ABC.
-Although the current status is overfishing and overfished (Yukami et al.
-2020), it is expected that the Pacific stock of spotted mackerel will show a recovery to a level that produces the MSY by using our assessment method and the new Harvest Control Rules.
-
-\ \ \ \ \ \ \ \ \ \
-Although detailed information on spawning grounds is necessary for understanding fluctuations in recruitment as well as for providing a basis for stock management, prior data for spotted mackerel has not been reliable.
-For example, some studies have reported that the area around the Izu Islands may not be a suitable spawning ground for spotted mackerel because few eggs have been observed (Yukami et al.
-2019).
-In contrast, it is possible that the spotted mackerel spawns around the Izu Islands because the estimated hatch day and the spatial distribution of spotted mackerel at the Kuroshio--Oyashio transition area were similar to those of chub mackerel, which spawns around mainly the Izu Islands (Takahashi et al., 2010).
-The present study showed that the relative egg density, which was estimated using the better model, was equally high off the coast of Kyushu, Shikoku, and the Izu Islands (Fig.
-3), providing direct evidence that the area around the Izu Islands are also a major spawning ground of spotted mackerel.
-It is possible that spotted mackerel spawn in the area around the Izu Islands because they are not sensitive to rising water temperatures and they are generally distributed farther south than chub mackerel (Mitani et al., 2002).
-Indeed, although both spotted mackerel and chub mackerel spawn at the same time around the Izu Islands (Tanoue et al., 1960; Hanai and Meguro, 1997), the reproductive phenology of chub mackerel has changed due to rising sea surface temperatures associated with climate change; since 2000, chub mackerel migrate to their feeding ground earlier and spawn father northward (Kanamori et al., 2019).
-
-\ \ \ \ \ \ \ \ \ \
-Understanding migration patterns is necessary for conducting stock assessments (Crossin et al., 2017).
-It has been assumed that the spawning grounds of spotted mackerel change with age; individuals migrate from around the Izu Islands to the Kuroshio--Oyashio transition area to feed before spawning at 2 years of age (Nishida et al., 2000; Kawabata et al.
-2008).
-Adults that have spawned gradually migrate westward, using the spawning grounds off the coast of Kyushu and Shikoku (Hanai, 1999; Nashida et al., 2006).
-Although the number of recruits were particularly high in 2004 and 2009 (Yukami et al., 2019), we did not find evidence for an increase in the relative egg density around the Izu Islands in 2006 and in 2011 or the other spawning grounds after 2007 and 2012 (Fig.
-3).
-One explanation for this is that the migration range of spotted mackerel is narrower than we assumed.
-Previous studies have reported that spotted mackerel remains around the Izu Islands and off the coast of Shikoku (Hanai, 1999; Nashida et al., 2006).
-Another explanation is that part of a strong year may remain in another area due to the expansion of the spatial distribution resulting from an increase number in recruitments.
-For example, Kawabata et al.
-(2008) reported that the 2004 year class migrated for feeding and overwintering until at least 3 years old over the Emperor Seamounts (around $\textrm{165}-\textrm{170}^{\circ}$E and $\textrm{30}-\textrm{55}^{\circ}$N).
-Testing these hypotheses will be the subject of future research and should improve our understanding of the migratory patterns of the spotted mackerel, which in turn should improve stock assessment and management.
-\ \\
-
-\ \\
-\flushleft{\textbf{\Large{Conclusion}}}\\
-This study showed that indices of egg density of spotted mackerel, which were standardized using a spatio--temporal model, reduced temporal fluctuation.
-In particular, the standardized indices in 2018 were reduced to a considerable degree compared with the nominal index.
-The model incorporating the effect of chub mackerel egg density on the catchability of spotted mackerel (i.e., the model incorporating species misidentification bias) was the better model according to the AIC.
-In addition, the retrospective bias decreased by about half when using the egg density index from the better model.
-These results suggest that incorporating species misidentification bias is an essential process for improving stock assessment.
-
-\ \\
-%\setstretch{1}
-\flushleft{\textbf{\Large{Acknowledgments}}}\\
-This research was financiallysupportted by the grants from the Japan Society for the Promotion of Science (JSPS) (19K15905, 20392904).
-\ \\
-
-%\flushleft{\textbf{\Large{Authorship}}}\\
-%YK conceived of the research idea.
-AT and MW conducted field sampling.
-YK, SN, and HO designed statistical analyses.
-YK and SN wrote programs and performed the analyses.
-YK wrote the manuscript with input from all co-authors' comments.
-\ \\
-
-%\setstretch{1}
-\flushleft{\textbf{\Large{Literature cited}}}\\
-\hangindent=30pt
-\noindent
-Crossin, G.T., Cooke, S.J., Goldbogen, J.A., Phillips, R.A. 2014. Tracking fitness in marine vertebrates: current knowledge and opportunities for future research. Mar. Ecol. Prog. Ser. 496:1-17.
-
-\hangindent=30pt
-\noindent
-Elphick, C.S. 2008. How you count counts: the importance of methods research in applied ecology. J. Appl. Ecol. 45:1313-1320.
-
-\hangindent=30pt
-\noindent
-Garcia-Vazquez, E., Machado-Schiaffino, G., Campo ,D., Juanes, F. 2012. Species misidentification in mixed hake fisheries may lead to overexploitation and population bottlenecks. Fish. Res. 114:52-55.
-
-\hangindent=30pt
-\noindent
-Goelz, S.E., Hamilton, S.R., Vogelstein, B. 1985. Purification of DNA from formaldehyde fixed and paraffin embedded human tissue. Biochem. Biophys. Res. Commun. 130:118–126.
-
-\hangindent=30pt
-\noindent
-Hashimoto, M., Nishijima, S., Yukami, R., Watanabe, C., Kamimura, Y., Furuichi, S., Ichinokawa, M., Okamura, H.
-2019.
-Spatiotemporal dynamics of the Pacific chub mackerel revealed by standardized abundance indices.
-Fish.
-Res.
-219:105315.
-
-\hangindent=30pt
-\noindent
-Hashimoto, M., Okamura, H., Ichinokawa, M., Hiramatsu, K., Yamakawa, T.
-2018.
-Impacts of the nonlinear relationship between abundance and its index in a tuned virtual population analysis.
-Fish.
-Sci.
-84:335-347.
-
-\hangindent=30pt
-\noindent
-Hurtado-Ferro, F., Szuwalski, C.S., Valero.
-J.L., Andderson.
-S.C., Cunningham, C.J., Johnson, K.F., Licandeo, R.L., McGilliard, C.R., Monnahan, C.C., Muradian, M.L., Ono, K., Vert-Pre, K.A., Whitten, A.R., Punt, A.E.
-2015.
-Looking in the review mirror: bias and retrospective patterns in integrated, age-structured stock assessment models.
-ICES J.
-Mar.
-Sci.
-72:99-110.
-
-\hangindent=30pt
-\noindent
-Ichinokawa, M., Okamura, H.
-2014.
-Review of stock evaluation methods using VPA for fishery stocks in Japan: implementation with R.
-Bull.
-Jpn.
-Soc.
-Fish.
-Oceanogr.
-78:104-113 (in Japanese with English abstract).
-
-\hangindent=30pt
-\noindent
-Impraim, C.C., Saiki.
-R.K., Erlich, H.A., Teplitz, R.L.
-1987.
-Analysis of DNA extracted from formalin-fixed, paraffin-embedded tissues by enzymatic amplification and hybridization with sequence-specific oligonucleotides.
-Biochem.
-Biophys.
-Res.
-Commun.
-142:710–716.
-
-\hangindent=30pt
-\noindent
-Kanamori, Y., Takasuka, A., Nishijima, S., Okamura, H.
-2019.
-Climate change shifts the spawning ground northward and extends the spawning period of chub mackerel in the western North Pacific.
-Mar.
-Ecol.
-Prog.
-Ser.
-624:155-166.
-
-\hangindent=30pt
-\noindent
-Ko, H.L., Wang, Y.T., Chiu, T.S., Lee, M.A., Leu, M.Y., Chang, K.Z. et al. 2013. Evaluating the accuracy of morphological identification of larval fishes by applying DNA barcoding. PLoS ONE 8:e53451.
-
-\hangindent=30pt
-\noindent
-Lindgren, F. 2012. Continuous domain spatial models in R-INLA. ISBA Bull. 19:14-20.
-
-\hangindent=30pt
-\noindent
-MacKenzie, D.I., Nichols, J.D., Lanchman, G.B., Droege, S., Royle, J.A., Langtimm, C.A. 2002. Estimating site occupancy rates when detection probabilities are less than one. Ecology 83:2248-2255.
-
-\hangindent=30pt
-\noindent
-Marko, P.B., Lee, S.C., Rice, A.M., Gramling, J.M., Fitzhenry, T.M., McAlister, J.S., Harper, G.R., Moran, A.L. 2004. Mislabelling of a depleted reef fish. Nature 430:309-310.
-
-\hangindent=30pt
-\noindent
-Matarese, A.C., Spies, I.B., Busby, M.S., Orr, J.W. 2011. Early larvae of \textit{Zesticelus profundorum} (family Cottidae) identified using DNA barcording. Ichthyol. Res. 58: 170-174.
-
-\hangindent=30pt
-\noindent
-Mohn, R. 1999. The retrospective problem in sequential population analysis: an investigation using cod fishery and simulated data. ICES J. Mar. Sci. 56:473-488.
-
-\hangindent=30pt
-\noindent
-Mori, K., Hiyama, Y. 2014. Stock assessment and management for walleye pollock in Japan. Fish. Sci. 80:161-172.
-
-\hangindent=30pt
-\noindent
-Nishida, H., Wada, T., Oozeki, Y., Sezaki, K., Saito, M.
-2001.
-Possibility of identifying chub mackerel and spotted mackerel by measuring diameter of mackerel eggs.
-Nippon Suisan Gakkaishi, 67: 102-104.
-
-\hangindent=30pt
-\noindent
-Okamura, H., Yamashita, Y., Ichinokawa, M. 2017. Ridge virtual population analysis to reduce the instability of fishing mortalities in the terminal year. ICES J. Mar. Sci. 74:2427-2436.
-
-\hangindent=30pt
-\noindent
-R Development Core Team, 2019. R: a language and envi- ronment for statistical computing. R Foundation for Sta- tistical Computing, Vienna.
-
-\hangindent=30pt
-\noindent
-Takahashi, M., Takagi, K,, Kawabata, A., Watanabe, C., Nishida, H., Yamashita, N., Mori, K., Suyama, S., Nakagami, M., Ueno, Y., Saito, M.
-2010.
-Estimated hatching season of the Pacific stock of chub mackerel \textit{Scomber japonicus} and spotted mackerel \textit{S.
-australasicus} in 2007.
-Fisheries biology and oceanography in the Kuroshio 11:49-54 (in Japanese).
-
-\hangindent=30pt
-\noindent
-Takasuka, A., Kubota, Hm., Oozeki, Y. 2008a. Spawning overlap of anchovy and sardine in the western North Pacific. Mar. Ecol. Prog. Ser. 366:231-244.
-
-\hangindent=30pt
-\noindent
-Takasuka, A., Oozeki, Y., Kubota, H. 2008b. Multi-species regime shifts reflected in spawning temperature optima of small pelagic fish in the western North Pacific. Mar. Ecol. Prog. Ser. 360:211-217.
-
-\hangindent=30pt
-\noindent
-Takasuka, A., Tadokoro, K., Okazaki, Y., Ichikawa, T., Sugisaki, H., Kuroda, H., Oozeki, Y.
-2017.
-In situ filtering rate vari- ability in egg and larval surveys off the Pacific coast of Japan: Do plankton nets clog or over-filter in the sea?
-Deep-Sea Res.
-I 120:132−137.
-
-\hangindent=30pt
-\noindent
-Takasuka, A., Yoneda, M., Oozeki, Y. 2019. Density depend- ence in total egg production per spawner for marine fish. Fish. Fish. 20:125−137.
-
-\hangindent=30pt
-\noindent
-Thorson, J.T. 2019.  Guidance for decisions using the Vector Autoregressive Spatio-Temporal (VAST) package in stock, ecosystem, habitat and climate assessments. Fish. Res. 210:143-161.
-
-\hangindent=30pt
-\noindent
-Thorson, J.T., Barnett, L.A.K.
-2017.
-Comparing estimates of abundance trends and distribution shifts using single- and multispecies models of fishes and biogenic habitat.
-ICES J.
-Mar.
-Sci.
-74:1311−1321.
-
-\hangindent=30pt
-\noindent
-Thorson, J.T., Kristensen, K.
-2016.
-Implementing a generic method for bias correction in statistical models using ran- dom effects, with spatial and population dynamics exam- ples.
-Fish.
-Res.
-175: 66–74.
-
-\hangindent=30pt
-\noindent
-Thorson, J.T., Shelton, A.O., Ward, E.J., Skaug, H.J.
-2015.
-Geostatistical delta-generalized linear mixed models improve precision for estimated abundance indices for West Coast groundfishes.
-ICES J.
-Mar.
-Sci.
-72:1297−1310.
-
-\hangindent=30pt
-\noindent
-Victor, B.C., Hanner, R., Shivji, M., Hyde, J., Caldow, C.
-2009.
-Identification of the larval and juvenile stages of the cubera snapper, \textit{Lutignus cyanopterus}, using DNA barcoding.
-Zootaxa 2215:24-36.
-
-\hangindent=30pt
-\noindent
-Watanabe, C., Hanai, T., Meguro, K., Ogino, R., Kubota, Y., Kimura, R.
-1999.
-Spawning biomass estimates of chub mackerel \textit{Scomber japonicus} of Pacific subpopulation off central Japan by a daily egg production method.
-Nippon Suisan Gakkaishi 65: 695-702 (in Japanese with English abstract).
-
-\hangindent=30pt
-\noindent
-Watanabe, C., Nishida, H.
-2002.
-Development of assessment techniques for pelagic fish stocks: applications of daily egg production method and pelagic trawl in the northwestern Pacific Ocean.
-Fish.
-Sci.
-68:97-100.
-
-\hangindent=30pt
-\noindent
-Watanabe, C., Yatsu, A.
-2006.
-Long-tem changes in maturity at age of chub mackerel (\textit{Scomber japonicus}) in relation to population declines in the waters off northeastern Japan.
-Fish.
-Res.
-78:323-332.
-
-\hangindent=30pt
-\noindent
-Watanabe, T., 1970.
-Morphology and ecology of early stages of life in Japanese common mackerel, \textit{Scomber japonicus} HOUTTUYN, with special reference to fluctuation of population.
-Bull.
-Tokai Reg.
-Fish.
-Res.
-Lab.
-62:1-283 (in Japanese with English abstract).
-
-\hangindent=30pt
-\noindent
-Williams, B.K., Nichols, J.D., Conroy, M.J. 2002. Analysis and management of animal population. Academic Press, New York.
-
-\hangindent=30pt
-\noindent
-Yukami, R., Isu, S., Watanabe, C., Kamimura, Y., Furuichi, S.
-2019.
-Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2018).
-In: Marine fisheries stock assessment and evaluation for Japanese waters (2018/ 2019).
-Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa, p 248−278 (in Japanese).
-
-\hangindent=30pt
-\noindent
-Yukami, R., Isu.
-S., Kamimura, Y., Furuichi, S., Watanabe, R., Kanamori, Y.
-2020.
-Stock assessment and evaluation for the Pacific stock of spotted mackerel (fiscal year 2019).
-In: Marine fisheries stock assessment and evaluation for Japanese waters (2019/ 2020).
-Fisheries Agency and Fisheries Research Agency of Japan, Yokohama, Kanagawa (in Japanese).
-
-\newpage
-\flushleft{\textbf{\Large{Captions}}}\\
-\flushleft{\textbf{Fig.
-1}} Study area.
-Spotted mackerel \textit{Scomber australasicus} in the western North Pacific spawns around Kyushu, Shikoku, and the Izu Islands in Japan.
-Adults and their offspring are then transported to their feeding ground by the Kuroshio Current.
-\ \\
-\flushleft{\textbf{Fig.
-2}} Temporal trends in indices of egg density.
-The gray line represents the scaled nominal index, the blue line represents the estimated index without the effect of chub mackerel, and the red line represents the estimated index with the effect of chub mackerel.
-Vertical bars are 95\% confidence intervals of the estimated indices.
-\ \\
-\flushleft{\textbf{Fig. 3}} Temporal changes in the spatial distribution of relative egg density, \textcolor{red}{as} estimated using the model with the effect of chub mackerel.
-\ \\
-\flushleft{\textbf{Fig.
-4}} Retrospective patterns of total numbers of individuals, total biomass, and spawning stock biomass (SSB).
-Color differences denote differences in sequentially removing data for the five most recent years (blue, light blue, green, orange, and red indicate removal of data for years 1 to 5 years, respectively) from the full data set (gray).
-\ \\
-
 \end{linenumbers}

### 2021-03-10 results/draft.tex
added the eDNA survey

@@
 Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
-Field surveys using environmental DNA (eDNA) are widely used for detecting invesive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
+Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
 2014; Thomsen \& Willerslev 2015 %Dorazioに引用されていたやつ．あとで再確認).
 %Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
-However, the presence/absence of eDNA includes many types of uncertinties due to relating to environmental factors such as temperature and advection ().
+However, the presence/absence of eDNA includes many types of uncertainties due to relating to environmental factors such as temperature and advection ().
 For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
@@
 \ \ \ \ \ \ \ \ \ \ 
-One step towards overcoming these uncertinties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies
+One step towards overcoming these uncertainties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies
 
@@
 Tokyo Bay is a large enclosed coastal sea in Japan.
-In Tokyo Bay, there are many useful species for fisheries that are colled "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago).
+In Tokyo Bay, there are many commercially important species for fisheries that are called "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago).
 Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution).
 Catch statistics (total catch in each species, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay.
-The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay, Japan.
+The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay.
 On the other hand, weakness of this data is like a opportunistic data because the data is likely to be biased towards areas to high density of focal species due to commercially fishes, consequently less zero data.
-In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes (Hongo et al., submitted).
-The strengths are that the data is systematically collected because of scientific survey data and includes zero data, while the weaknesses are that the data is less abundant and includes uncertinties in presence/absence as description in above.
+In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes in Tokyo Bay (Hongo et al., submitted).
+The strengths are that the data is systematically collected by scientific survey data and includes zero data, while the weaknesses are that the data is less abundant due to spatial restriction of the survey and includes uncertainties in presence/absence as description in above.
 
 \ \ \ \ \ \ \ \ \ \ 
+In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model.
+We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan.
+The predicted spatial distribution of four fish form our model reduced
+
 %In this paper, we make an integrated spatial distribution model by combining both catch statistics, which is opportunistic data but abundant and represents the direct evidence where fish was, and eDNA data, which is the monitoring data in the same points but not abundant and includes uncertinties due to environmental factors.
@@
 
-In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertinties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model.
-We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan.
-The predicted spatial distribution of four fish form our model reduced
-
 \ \\
@@
 \section{Materials and Methods}
-\subsection{Data sets}
-\flushleft{\textbf{2.1.1 Survey and data}}\\
-The egg density data with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution in the areas from $\textrm{122}^\circ$E to $\textrm{150}^\circ$E and $\textrm{24}^\circ$N to $\textrm{43}^\circ$N was used.
+%2.1: a general model to estimate species distribution from eDNA
+%2.2: an application to a eDNA and catch data in Tokyo Bay
+%2.2.1: 野外調査
+%2.2.2: 漁獲量データ
+%2.2.3: model in Tokyo Bay
+
+\subsection{A general model to estimate species distribution from eDNA}
+%\flushleft{\textbf{2.1.1 Survey and data}}\\
+%The egg density data with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution in the areas from $\textrm{122}^\circ$E to $\textrm{150}^\circ$E and $\textrm{24}^\circ$N to $\textrm{43}^\circ$N was used.
 The egg density data set was derived from monthly egg surveys off the Pacific coast of Japan from January to June, 2005--2019 (Takasuka et al., 2008a, 2019).
@@
 
-\ \ \ \ \ \ \ \ \ \ 
-The egg surveys were conducted by 18 prefectural experimental stations or fisheries research institutes and two national research institutes of the Japan Fisheries Research and Education Agency, following the consistent sampling designs, as a part of the stock assessment project.
+%\ \ \ \ \ \ \ \ \ \ 
+%The egg surveys were conducted by 18 prefectural experimental stations or fisheries research institutes and two national research institutes of the Japan Fisheries Research and Education Agency, following the consistent sampling designs, as a part of the stock assessment project.
 In the surveys, plankton nets were towed vertically from a depth of ~150 m to the surface (if the depth was <150 m, nets were lowered to just above the bottom).
@@
 Then, the arithmetic average of the number of eggs was obtained with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution.
-\textcolor{red}{The mean proportion of the total number of eggs of spotted mackerel against the total number of eggs of \textit{Scomber} was less than 20 \% from 2005 to 2019.
+%\textcolor{red}{The mean proportion of the total number of eggs of spotted mackerel against the total number of eggs of \textit{Scomber} was less than 20 \% from 2005 to 2019.
 Therefore, the effect of the misidentification error that we considered was from chub mackerel on spotted mackerel (i.e., we assumed that the effect of the misidentification error from spotted  mackerel on chub mackerel was small.)} More detailed descriptions of the surveys and data set are provided in previous studies of the reproductive biology of small pelagic fish species (e.g., Takasuka et al.
@@
 
-\subsection{Data analyses}
-\flushleft{\textbf{2.2.1 Indices of egg density}}\\
-In this study, we used the three indices of egg density of spotted mackerel; nominal, chub--, and chub+.
-The nominal index was the arithmetic mean of egg density for each year.
-The chub-- index was the estimated egg density by considering sampling effects (i.e., spatio--temporal changes in survey design).
-The chub+ index was the estimated egg density by considering sampling effects and the effect of egg density of chub mackerel on the catchability of egg density of spotted mackerel.
-The process for estimating chub-- and the chub+ is described in the following section.
+\subsection{An application to a eDNA and catch data in Tokyo Bay}
+\flushleft{\textbf{2.2.1 Field survey}}\\
+Field surveys were conducted at 14 sites in Tokyo Bay from April to December in 2018 using R/V Fusanami or R/V Fusami-maru of Chiba Prefecture and R/V Enoshima-maru of Kanagawa Prefecture (Fig.
+1).
+In each station, sea water for eDNA analysis and environmental data were simultaneously collected.
+For eDNA analysis, two litter of bottom sea water was collected using a Niskin water sampler and were separated for two 1L samples.
+Each samples filtered glass fiber membrane GF/F (0.7 $\mu m$ pore size; Cytiva, Sheffield, UK) onboard and then the filters were frozen on a block of dry ice.
+These frozen filters were transported and stored at $-30^\circ$ in the laboratory until use.
+Equipments for eDNA sampling were changed new one or washed in each sites to exclude contamination.
+During sampling the bottom sea water, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー？).
 
-\flushleft{\textbf{2.2.2 Estimation of the indices of egg density}}\\
+\flushleft{\textbf{2.2.2 Catch statistics}}\\
 To estimate the chub-- and the chub+ indices of egg density by considering sampling effects (i.e., spatio--temporal changes in survey design) as well as the effect of the egg density of chub mackerel on the catchability of egg density of spotted mackerel, we used the multivariate vector autoregressive spatio-temporal (VAST) model (Thorson and Barnett, 2017), which accounts for spatio-temporal changes in survey design, survey effort, and observation rates and can accurately estimate relative local densities at high resolution by standardizing sampling designs (Thorson and Barnett, 2017; Thorson, 2019).
@@
 
+\flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
+
 \end{linenumbers}

### 2021-03-10 results/draft.tex
added acknowledgement and authorship

@@
 \subsection{An application to a eDNA and catch data in Tokyo Bay}
-\flushleft{\textbf{2.2.1 Field survey}}\\
+\flushleft{\textbf{2.2.1 eDNA data}}\\
+\flushleft{\textbf{2.2.1.1 Field survey}}\\
 Field surveys were conducted at 14 sites in Tokyo Bay from April to December in 2018 using R/V Fusanami or R/V Fusami-maru of Chiba Prefecture and R/V Enoshima-maru of Kanagawa Prefecture (Fig.
 1).
-In each station, sea water for eDNA analysis and environmental data were simultaneously collected.
-For eDNA analysis, two litter of bottom sea water was collected using a Niskin water sampler and were separated for two 1L samples.
+In each station, seawater for eDNA analysis and environmental data were simultaneously collected.
+For eDNA analysis, two litter of bottom seawater was collected using a Niskin water sampler and were separated for two 1L samples.
 Each samples filtered glass fiber membrane GF/F (0.7 $\mu m$ pore size; Cytiva, Sheffield, UK) onboard and then the filters were frozen on a block of dry ice.
-These frozen filters were transported and stored at $-30^\circ$ in the laboratory until use.
-Equipments for eDNA sampling were changed new one or washed in each sites to exclude contamination.
-During sampling the bottom sea water, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー？).
+These frozen filters were transported and stored at $-30^\circ$ in the laboratory until eDNA extraction.
+To lower the levels of cross-contamination, equipments for eDNA sampling were changed new one or washed in each site.
+During sampling the bottom seawater, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー？).
+
+\flushleft{\textbf{2.2.1.1 Laboratory experiments}}\\
+In laboratory, eDNA extraction, eDNA amplification, and eDNA sequence were conducted.
+Total eDNA was extracted from the frozen filters using a DNeasy Blood and Tissue Kit (Qiagen, Hilden, Germany) following Yamamoto et al.
+2019.
+Mitochondorial 12S rRNA gene was amplified using MiFish universal primers referring to Miya et al.
+20
 
@@
 
+\ \\
+%\setstretch{1}
+\flushleft{\textbf{\Large{Acknowledgments}}}\\
+This research was financially supported by Grant-in-Aid for Fisheries Agency of Japan.
+%This research was financially supported by the grants from the Japan Society for the Promotion of Science (JSPS) (19K15905, 20392904).
+\ \\
+
+\flushleft{\textbf{\Large{Authorship}}}\\
+YK conceived of the research idea.
+YH, YU, HM, MI, KA, and AK conducted field sampling.
+YH performed the laboratory experiments.
+YK, HO, and SN designed statistical analyses.
+YK wrote programs and performed the analyses.
+YK wrote the manuscript with input from all co-authors' comments.
+\ \\
+
 \end{linenumbers}

### 2021-03-10 results/draft.tex
wrote eDNA experiments in Lab.
wrote catch data

@@
 \ \ \ \ \ \ \ \ \ \ 
-Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
+Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
 The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al.
@@
 \ \ \ \ \ \ \ \ \ \ 
-In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model.
+In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
 We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan.
@@
 To lower the levels of cross-contamination, equipments for eDNA sampling were changed new one or washed in each site.
-During sampling the bottom seawater, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー？).
+During sampling the bottom seawater, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー).
 
@@
 Mitochondorial 12S rRNA gene was amplified using MiFish universal primers referring to Miya et al.
-20
+2015 with slight modification.
+The details was shown in Hongo et al.
+(受理されてないようだったら書くしかない).
+eDNA sequence were ....
 
 \flushleft{\textbf{2.2.2 Catch statistics}}\\
-To estimate the chub-- and the chub+ indices of egg density by considering sampling effects (i.e., spatio--temporal changes in survey design) as well as the effect of the egg density of chub mackerel on the catchability of egg density of spotted mackerel, we used the multivariate vector autoregressive spatio-temporal (VAST) model (Thorson and Barnett, 2017), which accounts for spatio-temporal changes in survey design, survey effort, and observation rates and can accurately estimate relative local densities at high resolution by standardizing sampling designs (Thorson and Barnett, 2017; Thorson, 2019).
-The model includes two potential components because it is designed to support delta-models: (i) the encounter probability $p_{i}$ for each sample $i$ and (ii) the expected egg density $d_{i}$ for each sample $i$ when spawning occurs (i.e., egg density is not zero).
-The encounter probability $p_{i}$ and the expected egg density $d_{i}$ are, respectively, approximated using a logit-linked linear predictor and a log-linked linear predictor as follows (Thorson and Barnett, 2017):
+A part of catch statistics of small-scale bottom trawl fisheries recorded by several representative boats of Chiba Prefecture were provided by Chiba Prefecture.
+This data included date, geographic location, efforts (number of tows), gear, and catch weight (kg) in each fish.
+Almost of all gear was beam trawl although dredge net also used.
+The species which also detected by eDNA was \textit{Conger myriaster} (マアナゴ), \textit{Kareius bicoloratus} (イシガレイ), \textit{Lateolabrax japonicus} (スズキ), and \textit{Konosirus punctatus} (コノシロ).
+Thus, we estimated the spatial distribution of these four species using the eDNA-IDM.
+\textcolor{red}{マコガレイ，カマス類，クロダイ，イシモチ類も解析できる？？}
+
+\flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
+
+\flushleft{\textbf{equation examples}}\\
 %\[
@@
 
-\flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
-
 \ \\

### 2021-03-10 results/draft.tex
changed in Field survey

@@
 \subsection{A general model to estimate species distribution from eDNA}
+To estimate
+
+\[
+\mathrm{logit}(p_{1}(s_{i})) = \alpha_{1} + \beta(s_{i}) + \theta(s_{i}) + u_{1}(s_{i})
+\]
+\[
+\mathrm{logit}(p_{2}(s_{i})) = \alpha_{2} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{2}(s_{i})
+\]
 %\flushleft{\textbf{2.1.1 Survey and data}}\\
@@
 \flushleft{\textbf{2.2.1.1 Field survey}}\\
-Field surveys were conducted at 14 sites in Tokyo Bay from April to December in 2018 using R/V Fusanami or R/V Fusami-maru of Chiba Prefecture and R/V Enoshima-maru of Kanagawa Prefecture (Fig.
-1).
-In each station, seawater for eDNA analysis and environmental data were simultaneously collected.
-For eDNA analysis, two litter of bottom seawater was collected using a Niskin water sampler and were separated for two 1L samples.
+Field surveys were conducted by prefectural experimental station in Chiba, following the consistent sampling design at 14 sites in Tokyo Bay from April to December in 2018 (Fig. 1). 
+%Field surveys were conducted at 14 sites in Tokyo Bay from April to December in 2018 using R/V Fusanami or R/V Fusami-maru of Chiba Prefecture and R/V Enoshima-maru of Kanagawa Prefecture (Fig. 1). 
+In each sites, seawater and environmental data were simultaneously collected.
+For eDNA analysis, two litter of bottom seawater was collected using a Niskin water sampler, and then it was separated for two 1L samples for replicate.
 Each samples filtered glass fiber membrane GF/F (0.7 $\mu m$ pore size; Cytiva, Sheffield, UK) onboard and then the filters were frozen on a block of dry ice.
-These frozen filters were transported and stored at $-30^\circ$ in the laboratory until eDNA extraction.
-To lower the levels of cross-contamination, equipments for eDNA sampling were changed new one or washed in each site.
-During sampling the bottom seawater, water temperature, salinity, pH, and dissolved oxygen (DO) were measured by CTD (メーカー).
+These frozen filters were stored at $-30^\circ$ in the laboratory until eDNA extraction.
+To lower the levels of cross-contamination, equipments for eDNA sampling were changed new one or washed in each sites.
+During sampling the bottom seawater, seawater temperature, salinity, pH, and dissolved oxygen (DO) at the same depth of seawater sampling for eDNA were measured by CTD (メーカー).
+%The egg surveys were conducted by 18 prefectural experimental stations or fisheries research institutes and two national research institutes of the Japan Fisheries Research and Education Agency, following the consistent sampling designs, as a part of the stock assessment project.
 
@@
 \flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
+To estimate the spatial distribution of four focal species from eDNA and catch data by considering uncertainties caused by environmental factors, we fitted the model (equation 1) to the presence/absence data of eDNA and of catch data collected in Tokyo Bay as follows:
 

### 2021-03-11 results/draft.tex
added a conceptual diagram

@@
 \subsection{A general model to estimate species distribution from eDNA}
-To estimate
+To estimate the spatial distribution from eDNA considering with spatial biases due to degradation from environmental factors (e.g., temperature and advection),
 
@@
 
+\newpage
+\begin{figure}[h]
+  \centering
+  \includegraphics[width = 18cm]{idea.png}
+  \caption{Conceptual diagram of this study.}
+\end{figure}
+
 \end{linenumbers}

### 2021-03-11 results/draft.tex
added the explanation of joint likelihood method

--- 2021-03-10 results/draft.tex
@@
 \subsection{A general model to estimate species distribution from eDNA}
-To estimate
+Integrated spatial distribution model that account for explicitly spatial autocorrelation in occurrence were built by Pacifici et al.
+(2017), which shows three approaches to predict the spatial distribution of species: the joint likelihood (shared), correlation, and covariate methods.
+The joint likelihood method uses multiple data types to simultaneously estimate a shared set of parameters with constraining that the likelihoods of shared set of parameters to be equal across.
+The correlation method connects multiple data types indirectly through a shared covariance matrix that captures similar patterns present in each data sources.
+The covariate method incorporates information from a added dataset via a fixed effect.
+
+\ \ \ \ \ \ \ \ \ \ 
+Although each methods estimate the spatial distribution of species using multiple data sets, we need to select method depending on the data features for analysis because there are strengths and weaknesses (Pacifici et al.
+2017; Miller et al.
+2018).
+The joint likelihood method may be problematic when the added data (second data?) is of poorly quality compared to correlation and covariate methods because each data can directly inform the latent occurrence state and the weight given to estimate the parameters is naturally determined by their relative size and quality.
+Thus, it is not the best method when our second data is low quality while it is the best method when all data are deemed reliable.
+%The joint likelihood method simultaneously fits a likelihood to both data sources
+%The joint likelihood approach uses multiple data types to simultaneously estimate a shared set of parameters.
+%the shared set of parameters within each of the individual likelihoods is constrained to be equal across likelihoods.
+
+\ \ \ \ \ \ \ \ \ \ 
+In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
 
@@
 \flushleft{\textbf{2.2.1 eDNA data}}\\
-\flushleft{\textbf{2.2.1.1 Field survey}}\\
+\flushleft{\textbf{Field surveys}}\\
 Field surveys were conducted by prefectural experimental station in Chiba, following the consistent sampling design at 14 sites in Tokyo Bay from April to December in 2018 (Fig. 1). 
@@
 
-\flushleft{\textbf{2.2.1.1 Laboratory experiments}}\\
+\flushleft{\textbf{Laboratory experiments}}\\
 In laboratory, eDNA extraction, eDNA amplification, and eDNA sequence were conducted.

### 2021-03-11 results/draft.tex
added the explanation about correlation method

@@
 2018).
-The joint likelihood method may be problematic when the added data (second data?) is of poorly quality compared to correlation and covariate methods because each data can directly inform the latent occurrence state and the weight given to estimate the parameters is naturally determined by their relative size and quality.
-Thus, it is not the best method when our second data is low quality while it is the best method when all data are deemed reliable.
+The joint likelihood method may be problematic when the second data is of poorly quality compared to correlation and covariate methods because each data can directly inform the latent occurrence state (probabilities?) and the weight given to estimate the parameters is naturally determined by their relative size and quality.
+Thus, it is not the best method when our second data is low quality while it is the best method when our second data is high quality (vise versa).
 %The joint likelihood method simultaneously fits a likelihood to both data sources
@@
 %the shared set of parameters within each of the individual likelihoods is constrained to be equal across likelihoods.
+The correlation method is added robustness to the joint likelihood because the second data indirectly inform the occurrence state.
+Thus, it is the best method when our second data is low quality while it is inferior to the joint likelihood method when both data are deemed reliable.
+%The correlation method is added robustness to the joint likelihood for the influence of unreliable data because the second data indirectly inform the occurrence state.
+% while this method is inferior to the joint likelihood when both data are deemed reliable.
 

### 2021-03-11 results/draft.tex
added the explanation about covariate model

@@
 % while this method is inferior to the joint likelihood when both data are deemed reliable.  
+The covariate method does not make full use of the information in the second data because the second data as a constructed covariate in the mean occurrence state.
+In addition, this method can reduce the computational cost because there are fewer parameters to estimate and the number of data locations can be reduced.
+Thus, it is the best method when the second data is low quality and/or there is computational limitation while it may not the best method when the information of the second data is needed.
 

### 2021-03-11 results/draft.tex
added the general equation

@@
 
+%\ \ \ \ \ \ \ \ \ \ 
+%As described above, 
+%When predicting the spatial distribution of species from eDNA, eDNA data is often collected systematic method (e.g., collected at the same sites and efforts)
+
+%When predicting the spatial distribution of species from eDNA using integrated species distribution model, the information that a species exists as second data is needed because of spatial uncertainties of eDNA due to complex factors.
 \ \ \ \ \ \ \ \ \ \ 
-In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
+When predicting the spatial distribution of species from eDNA using integrated species distribution model, the information that a species exists is needed as second data to consider spatial uncertainties of eDNA due to complex factors (Fig.
+1).
+Hence, the second data is preferred to high quality as possible.
+%However, spatially widely collected data and/or 
+%しかし，空間的に広く，また調査データのように系統的に取得されているデータを2番目のデータとして使用できるケースは限られているかもしれない．なぜなら，eDNAは直接的なモニタリングに比べて簡易的であるためより広い範囲で取得されており，またコンタミを防ぐためにも厳密な調査手法によって取得されている可能性が高いからである．
+%したがって，2番目のデータがhigh qualityであることは期待できないかもしれない．
 
-\[
-\mathrm{logit}(p_{1}(s_{i})) = \alpha_{1} + \beta(s_{i}) + \theta(s_{i}) + u_{1}(s_{i})
-\]
-\[
-\mathrm{logit}(p_{2}(s_{i})) = \alpha_{2} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{2}(s_{i})
-\]
+しかし，eDNAは直接的なモニタリングに比べて簡易的であるためより広い範囲で取得されている可能性が高く，eDNAのデータと同様の空間範囲で調査データのように質の高いデータを取得することは難しいかもしれない．その一方で，eDNAの空間的な不確実性を考慮するためには，種がいた証拠である2番目のデータの情報をeDNAのデータにしっかりと伝える必要がある．これらを考えると，integrated spetial distribution modelを用いたeDNAからの空間分布の推定には，以下のようなcorrelation methodが適切である:
+
+\begin{equation}
+\begin{array}{ll}
+p_{e}(s_{i}) = \alpha_{e} + \sum_{k}f_{e, k}(x_{e, k}(s_{i})) + w \theta(s_{i}) + u_{e}(s_{i})\\
+p_{a}(s_{i}) = \alpha_{a} + \sum_{k}f_{a, k}(x_{a, k}(s_{i})) + \theta(s_{i}) + u_{a}(s_{i})\\
+%\]
+%\[
+%\]
+\end{array}
+\end{equation}
+where $\alpha$ and $x_{k}(s_{i})$ are the intercept and the covariates at sites $i$ for occurrence probabilities at sites $i$ of the added data ($p_{a}$) and eDNA data ($p_{e}$), respectively.
+$u(s_{i})$ is spatial error that is specific for each data following multivariate normal distributions $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function.
+$\theta$ which is shared between two equations is the common spatial pattern between the two data, which cannot explain by each terms of the equations.
+That is, $\theta$ can be interpreted as "true" spatial distribution of species.
+
+%\[
+%\mathrm{logit}(p_{1}(s_{i})) = \alpha_{1} + \beta(s_{i}) + \theta(s_{i}) + u_{1}(s_{i})
+%\]
+%\[
+%\mathrm{logit}(p_{2}(s_{i})) = \alpha_{2} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{2}(s_{i})
+%\]
+
 %\flushleft{\textbf{2.1.1 Survey and data}}\\
@@
 To estimate the spatial distribution of four focal species from eDNA and catch data by considering uncertainties caused by environmental factors, we fitted the model (equation 1) to the presence/absence data of eDNA and of catch data collected in Tokyo Bay as follows:
+%In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
 

### 2021-03-11 results/draft.tex
added the eq. in TkyoBay

@@
 
-%\flushleft{\textbf{2.1.1 Survey and data}}\\
-%The egg density data with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution in the areas from $\textrm{122}^\circ$E to $\textrm{150}^\circ$E and $\textrm{24}^\circ$N to $\textrm{43}^\circ$N was used.
-The egg density data set was derived from monthly egg surveys off the Pacific coast of Japan from January to June, 2005--2019 (Takasuka et al., 2008a, 2019).
-The aim of the surveys was to monitor the egg abundance of major small pelagic fish species, including chub mackerel and spotted mackerel, so that the spatial area and survey month of the data largely covered the major spawning grounds and spawning season.
-While some sampling locations were fixed, others varied for various reasons (e.g., environmental conditions).
-Accordingly, the survey design changed slightly each year (Kanamori et al., 2019).
-Although the sampling efforts were approximately consistent year-round, the efforts tended to be more intensive during early spring; effort was highest in February and decreased gradually thereafter (Takasuka et al., 2008b).
-
-%\ \ \ \ \ \ \ \ \ \ 
-%The egg surveys were conducted by 18 prefectural experimental stations or fisheries research institutes and two national research institutes of the Japan Fisheries Research and Education Agency, following the consistent sampling designs, as a part of the stock assessment project.
-In the surveys, plankton nets were towed vertically from a depth of ~150 m to the surface (if the depth was <150 m, nets were lowered to just above the bottom).
-This range of depths covers the vertical distributions of eggs of small pelagic fish.
-During the period from 2005 to 2019, the surveys used a plankton net with a mouth ring diameter of 0.45 m and a mesh size of 0.335 (partially 0.330 mm in 2015) (Takasuka et al., 2017).
-The samples were fixed with 5\% formalin immediately after collection.
-In the laboratory, the samples were identified and sorted into eggs and larvae of different small pelagic species, based on the morphological characteristics (e.g., egg shape and size, number of oil globules, segmented yolk, perivitelline space ranging, yolk diameter, oil globule diameter).
-For the mackerel eggs, the egg diameters were measured to the nearest 0.025 mm by a micrometer for a maximum number of 100 individuals per sample (station or tow).
-Eggs with diameters $>$1.1 mm were identified as spotted mackerel, whereas those with diameters $leq$1.0 mm were identified as chub mackerel, according to Nishida et al.
-(2001).
-For any sample of $>$100 individuals, the proportion of the two species among 100 randomly selected individuals was assumed to be the same for the whole sample.
-Additionally, the number of eggs per unit area in the water column (number $\mathrm{m^{-2}}$) for each sampling tow was calculated by flow-meter revolutions, flow-meter revolutions per meter tow in the calibration, wire length (m), opening mouth area of the net  ($\mathrm{m^{-2}}$), and wire angle.
-Then, the arithmetic average of the number of eggs was obtained with $\textrm{30}^\prime$ latitude $\times$ $\textrm{30}^\prime$ longitude horizontal square resolution.
-%\textcolor{red}{The mean proportion of the total number of eggs of spotted mackerel against the total number of eggs of \textit{Scomber} was less than 20 \% from 2005 to 2019.
-Therefore, the effect of the misidentification error that we considered was from chub mackerel on spotted mackerel (i.e., we assumed that the effect of the misidentification error from spotted  mackerel on chub mackerel was small.)} More detailed descriptions of the surveys and data set are provided in previous studies of the reproductive biology of small pelagic fish species (e.g., Takasuka et al.
-2008a,b, 2017, 2019).
-
 \subsection{An application to a eDNA and catch data in Tokyo Bay}
@@
 \flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
-To estimate the spatial distribution of four focal species from eDNA and catch data by considering uncertainties caused by environmental factors, we fitted the model (equation 1) to the presence/absence data of eDNA and of catch data collected in Tokyo Bay as follows:
+To estimate the spatial distribution of four focal species using eDNA and catch data by considering with spatial  uncertainties of eDNA, we fitted the model (equation 1) to the presence/absence of eDNA and of catch collected in Tokyo Bay as follows:
 %In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
-
-\flushleft{\textbf{equation examples}}\\
-%\[
-\begin{equation}
-\begin{array}{ll}
-\mathrm{logit}\ p_{i} = \beta_{p}(t_{i}) + \omega_{p}(s_{i}) + \varepsilon_{p}(s_{i}, t_{i}) + \eta_{p}(v_{i}) + \lambda_{p}Q(i)\\
-%\]
-%\[
-\log d_{i} = \beta_{d}(t_{i}) + \omega_{d}(s_{i}) + \varepsilon_{d}(s_{i}, t_{i}) + \eta_{d}(v_{i}) + \lambda_{d}Q(i)
-%\]
-\end{array}
-\end{equation}
-where $\beta(t_{i})$ is the intercept for year $t$, and $\omega(s_{i})$ and $\varepsilon(s_{i}, t_{i})$ are the spatial and spatio--temporal random effects for year $t$ and location $s$, respectively.
-$\eta(v_{i})$ is the overdispersion random effect of factor $v_{i}$, which is the interaction of year and month.
-$\lambda$ is the effect of the chatchability covariate $Q(i)$: 
 \[
-%Q(i) = \mathrm{log} (\mathrm{chub\,mackerel\,egg\,density}(s_{i})+0.1). 
-Q(i) = \mathrm{log} (d_{chub}(s_{i})+0.1). 
+\mathrm{logit} \ \ p_{e}(s_{i}) = \alpha_{e} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{e}(s_{i})
 \]
-That is, this term considers the effect of species misidentification between chub mackerel and spotted mackerel; as mentioned earlier, we suspected overestimation of egg density of spotted mackerel because the difference in egg diameter has become ambiguous according to increase in egg density of chub mackerel and the distributions of egg diameters between species have overlapped (Yukami et al., 2019).
-The constant 0.1 was added because $\mathrm{log} 0$ (i.e., no chub mackerel eggs) is undefined, and the same result was obtained when using $1$ in place of $0.1$.
+\[
+\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \beta_{i} + \theta(s_{i}) + u_{c}(s_{i})
+\]
+where $\alpha$ is the intercept, and $x_{k}(s_{i})$ is the covariates at sites $i$ for occurrence probabilities of eDNA at sites $i$.
+In the study, seawater temperature, salinity, pH, and DO were used as covariates which effect on the occurrence of eDNA (i.e., $k = 4$).
+$u(s_{i})$ is spatial error that is specific for each data following multivariate normal distributions $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function.
+$\theta$ which is shared between eDNA and catch is the common spatial pattern between the two data, which cannot explain by each terms of the equations.
+That is, $\theta$ can be interpreted as the spatial distribution of species we want to know.
 

### 2021-03-11 results/draft.tex
small changes
changed fig1
revised the first paragraph in Introduction

@@
 \section{Introduction}
-Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
-Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
-2014; Thomsen \& Willerslev 2015 %Dorazioに引用されていたやつ．あとで再確認).
-%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
-However, the presence/absence of eDNA includes many types of uncertainties due to relating to environmental factors such as temperature and advection ().
-For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
-Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.
+Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
+Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
+because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
+2014; Thomsen \& Willerslev 2015) %Dorazioに引用されていたやつ．あとで再確認
+However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig.
+1).
+Therefore, it is necessary to consider the spatial uncertainty included in eDNA to estimate the spatial distribution of species.
+
+%However, a issue of eDNA is uncertainty of the occurrence of eDNA caused by various factors such as biology and environment (Fig. 1). 
+%However, the occurrence of eDNA includes many types of uncertainties due to relating to environmental factors such as temperature and advection ().For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.
 
@@
 That is, $\theta$ can be interpreted as the spatial distribution of species we want to know.
+\textcolor{red}{共変量の非線形性について書く}Parameters in this model was estimated by Integrated Nested Laplace Approximation using using the R-INLA package (Lindgren, 2012) in \textcolor{red}{R 3.6.1 (R Development Core Team, 2019).}
+\ \ \ \ \ \ \ \ \ \
 
@@
   \centering
-  \includegraphics[width = 18cm]{idea.png}
+  \includegraphics[width = 18cm]{fig1.png}
   \caption{Conceptual diagram of this study.}

### 2021-03-11 results/draft.tex
revised the objectives

@@
 1).
-Therefore, it is necessary to consider the spatial uncertainty included in eDNA to estimate the spatial distribution of species.
+Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species.
 
@@
 \ \ \ \ \ \ \ \ \ \ 
-In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
+In this paper, 
+%to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
+to infer spatial distribution of species from eDNA, we first make a spatial distribution model wichi considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
 We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
-The predicted spatial distribution of four fish form our model reduced
+%The predicted spatial distribution of four fish form our model reduced
 

### 2021-03-12 results/draft.tex
revised edomae

@@
 Tokyo Bay is a large enclosed coastal sea in Japan.
-In Tokyo Bay, there are many commercially important species for fisheries that are called "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago).
-Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution).
-Catch statistics (total catch in each species, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay.
+There are many commercially important species for fisheries that are called "Edomae" in Tokyo Bay because these species have been used for Sushi since Edo Era (about 400 years ago).
+Catch weight of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution).
+Catch statistics (total catch weight in each species, efforts, and geographic location of fishing) have been collected for stock assessment since \textcolor{red}{1990} by prefectures around Tokyo Bay.
 The strengths of this data are the direct evidence that a focal species occupies a location of fishing and abundant because of widely collected in Tokyo Bay.
@@
 In addition to this catch statistics, scientific survey of eDNA has been conducted monthly since 2018 for biodiversity monitoring because biodiversity also may decreased due to human-induced environmental changes in Tokyo Bay (Hongo et al., submitted).
-The strengths are that the data is systematically collected by scientific survey data and includes zero data, while the weaknesses are that the data is less abundant due to spatial restriction of the survey and includes uncertainties in presence/absence as description in above.
+The strengths are that the data is systematically collected data and includes zero data, while the weaknesses are that the data is less abundant due to spatial restriction of the survey and includes spatial uncertainty in the occurrence of eDNA as description in above.
 

### 2021-03-12 results/draft.tex
added the second paragraph (weakness of previous approaches)

@@
 \ \ \ \ \ \ \ \ \ \ 
-One step towards overcoming these uncertainties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies
+After the suggestion of the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016), the studies which used laboratory experiments and numerical hydrological models have been increased to overcome the uncertainty of eDNA.
+%To overcome the uncertainty of eDNA, the studies which used Laboratory experiments and numerical hydrological models have been increased after suggested the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016).
+%Laboratory experiments and numerical hydrological models have been used to overcome the uncertainty of eDNA, because Barnes \& Turner (2016) suggested the importance of knowledge about origin, state, transport, and fate of eDNA ("ecology of eDNA").
+% Laboratory experiments and numerical hydrological models have been used to overcome the uncertainty of eDNA, especially after suggested the importance of "ecology of eDNA" by Barnes \& Turner (2016).
+For example, the relationship between production rate of eDNA and biological factors (e.g., species and body mass) or environmental factors (e.g., temperature), and between decomposition of eDNA and the sate of eDNA (e.g., length of eDNA) or environmental factors were measured.
+In numerical hydrological models, spatial distribution of eDNA was simulated in aquatic area and obtain the production, transport and decay of eDNA (e.g., Fukaya et al.
+2020).
+%深谷さんの論文に引用あり
+However, the keep for all focal species in laboratory is not realistic and low cost-efficiency when multi species studies such as biodiversity monitoring and fisheries management.
+Moreover, biologists monitoring species are often not familiar with hydrological models and the simulation of eDNA often seems to be hard for them.
 

### 2021-03-12 results/draft.tex
revised the last sentence in the third paragraph in Introduction

@@
 Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
-The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al.
+% As alternative approach to over come the spatial uncertainty of eDNA, statistical modeling approach should be a useful approach.
+%The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al.
 2020; Miller et al.
 2019).
+%The model use the different type of data with strengths and weaknesses, such as scientific survey data (high quality but not abundant) and opportunistic citizen data (low quality but abundant) , and combine in a single model (Isaac et al.
+2020; Miller et al.
+2019).
+The models combine the different type of data with strengths and weaknesses in a single model.
+For example, the model can use both scientific survey data, which is high quality but less abundant due to restriction of cost, and citizen data, which is widely collected and abundant but may be low quality due to not using consistent field methods in a model.
+%scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
+Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
+Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the inference of the spatial distribution form the model should be reduced about spatial uncertainty of eDNA and should be improved.
+%したがって，統合モデルにより『生物がその場所に生息する』という情報をeDNAに加えることで，eDNA
+%したがって，eDNAデータと新たなデータ（『生物がその場所に生息する』という情報を持つ）を使って統合モデルを構築すれば，eDNAデータに対する空間的な不確実性は減少し，eDNAから推定される空間分布の精度は上昇することが期待される．
 
-The models combine the different type of data with strengths and weaknesses in a single model ().
-For example, scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
-Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when we use single data (Pacifici et al. 2017; Miller et al. 2019).
-
-\ \ \ \ \ \ \ \ \ \ 
-Tokyo Bay is a large enclosed coastal sea in Japan.
+%\ \ \ \ \ \ \ \ \ \ 
+%Tokyo Bay is a large enclosed coastal sea in Japan.
 There are many commercially important species for fisheries that are called "Edomae" in Tokyo Bay because these species have been used for Sushi since Edo Era (about 400 years ago).
@@
 \ \ \ \ \ \ \ \ \ \ 
+If we use one or more data that include the information about species existence in addition to eDNA data and infer the spatial distribution with combing these data by using IDMs, the spatial uncertainty of eDNA should recuse and the accuracy of prediction should increase.
+
+統合モデルを使えば，eDNAデータだけで空間分布を推定するよりも推定精度が上がり，
 In this paper, 

### 2021-03-12 results/draft.tex
revised the last sentence in 3 para in Intro

@@
 However, the keep for all focal species in laboratory is not realistic and low cost-efficiency when multi species studies such as biodiversity monitoring and fisheries management.
-Moreover, biologists monitoring species are often not familiar with hydrological models and the simulation of eDNA often seems to be hard for them.
+Moreover, biologists monitoring species are not often familiar with hydrological models and the simulation of eDNA seems to be hard for them.
 
@@
 Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
-Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the inference of the spatial distribution form the model should be reduced about spatial uncertainty of eDNA and should be improved.
+Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as treating environmental factors as covariance in the model, then the spatial uncertainty of eDNA should be reduced and the model inference should be improved.
+%Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the model inference of the spatial distribution should be reduced about spatial uncertainty of eDNA and should be improved.
 %したがって，統合モデルにより『生物がその場所に生息する』という情報をeDNAに加えることで，eDNA
@@
 %to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
-to infer spatial distribution of species from eDNA, we first make a spatial distribution model wichi considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
+to infer spatial distribution of species from eDNA, we first make a spatial distribution model which considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
 We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 

### 2021-03-12 results/draft.tex
small changes

@@
 %深谷さんの論文に引用あり
-However, the keep for all focal species in laboratory is not realistic and low cost-efficiency when multi species studies such as biodiversity monitoring and fisheries management.
+However, keeps for all focal species in laboratory are not realistic and low cost-efficiency when multi species studies such as biodiversity monitoring and fisheries management.
 Moreover, biologists monitoring species are not often familiar with hydrological models and the simulation of eDNA seems to be hard for them.
@@
 Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
-Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as treating environmental factors as covariance in the model, then the spatial uncertainty of eDNA should be reduced and the model inference should be improved.
+Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as treating environmental factors as covariance in the model, then the spatial uncertainty of eDNA should be reduced and the model inference should be improved (Fig.
+1).
 %Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the model inference of the spatial distribution should be reduced about spatial uncertainty of eDNA and should be improved.
@@
 \ \ \ \ \ \ \ \ \ \ 
-If we use one or more data that include the information about species existence in addition to eDNA data and infer the spatial distribution with combing these data by using IDMs, the spatial uncertainty of eDNA should recuse and the accuracy of prediction should increase.
+In this paper, to infer spatial distribution of species from eDNA, we first make a spatial distribution model which considers spatial uncertainty of eDNA by using an integrated spatial distribution model.
+We then apply the model to both eDNA data and catch weight data for four fish in Tokyo Bay, Japan.
+%If we use one or more data that include the information about species existence in addition to eDNA data and infer the spatial distribution with combing these data by using IDMs, the spatial uncertainty of eDNA should recuse and the accuracy of prediction should increase.
 
-統合モデルを使えば，eDNAデータだけで空間分布を推定するよりも推定精度が上がり，
-In this paper, 
 %to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
-to infer spatial distribution of species from eDNA, we first make a spatial distribution model which considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
-We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
+
 %The predicted spatial distribution of four fish form our model reduced

### 2021-03-12 results/draft.tex
small changes

@@
 Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
-Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as treating environmental factors as covariance in the model, then the spatial uncertainty of eDNA should be reduced and the model inference should be improved (Fig.
+Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as environmental factors as covariance in the model, then the inference from the model should represent the reduction of the spatial uncertainty of eDNA and improvement (Fig.
 1).
+%reduction of the spatial uncertainty of eDNA and improvement of the inference of spatial distribution from eDNA should be expected (Fig. 1).
+%the spatial uncertainty of eDNA should be reduced and the model inference should be improved (Fig. 1).
 %Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the model inference of the spatial distribution should be reduced about spatial uncertainty of eDNA and should be improved.

### 2021-03-12 results/draft.tex
revised the objectives

@@
 Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
-Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as environmental factors as covariance in the model, then the inference from the model should represent the reduction of the spatial uncertainty of eDNA and improvement (Fig.
+Hence, if we develop a IDM that uses not only the occurrence data of eDNA but also the second data which contains the information that species exists at a location, as well as environmental factors as covariance in the model, then the inference from the model should represent the reduction of the spatial uncertainty of eDNA and improvement (Fig.
 1).
@@
 \ \ \ \ \ \ \ \ \ \ 
-In this paper, to infer spatial distribution of species from eDNA, we first make a spatial distribution model which considers spatial uncertainty of eDNA by using an integrated spatial distribution model.
-We then apply the model to both eDNA data and catch weight data for four fish in Tokyo Bay, Japan.
-%If we use one or more data that include the information about species existence in addition to eDNA data and infer the spatial distribution with combing these data by using IDMs, the spatial uncertainty of eDNA should recuse and the accuracy of prediction should increase.
+In this paper, to infer spatial distribution of species from the occurrence data of eDNA, we first make a spatial distribution model which considers spatial uncertainty of eDNA by using an integrated spatial distribution model.
+We then applied the model to both eDNA data and catch weight data for four fish in Tokyo Bay, Japan, and predicted the spatial distribution of these fish.
+We finally compared the differences in (i) the predicted spatial distribution of eDNA among fish and (ii) the relationship between the occurrence of eDNA and environmental factors among fish to discuss the effects of the biological factors on the spatial uncertainty of eDNA.
+
+%And finally, we compared the differences in the predicted spatial distribution among fish and discuss the relationship between the pattern of the inference of spatial distribution and biological characteristics of fish.
 
 %to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM).
-
-%The predicted spatial distribution of four fish form our model reduced
 

### 2021-03-12 results/draft.tex
revised the title and added keywords

@@
 
-\flushleft{\textbf{Title: Inetgrated spatial model estimates the fish distribution using environmental DNA and catch data}}\\
+\flushleft{\textbf{Title: Integrated species distribution model improves spatial uncertainty of eDNA of Edomae-fish in Tokyo Bay}}\\
+%Integrated spatial model estimates the fish distribution using environmental DNA and catch data
 %\flushleft{\textbf{Running title: }}\\
@@
 \flushleft{\textbf{Keywords}}\\
+Spatial distribution, Environmental DNA, data fusion, Spatial correlation, Ecology of eDNA
 

### 2021-03-12 results/draft.tex
changed the section in MM

@@
 \subsection{A general model to estimate species distribution from eDNA}
+\flushleft{\textbf{Features of integrated spatial distribution model}}\\
 Integrated spatial distribution model that account for explicitly spatial autocorrelation in occurrence were built by Pacifici et al.
@@
 %When predicting the spatial distribution of species from eDNA using integrated species distribution model, the information that a species exists as second data is needed because of spatial uncertainties of eDNA due to complex factors.
-\ \ \ \ \ \ \ \ \ \ 
+\flushleft{\textbf{The model for eDNA}}\\
 When predicting the spatial distribution of species from eDNA using integrated species distribution model, the information that a species exists is needed as second data to consider spatial uncertainties of eDNA due to complex factors (Fig.

### 2021-03-12 results/draft.tex
small changes

@@
 Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
-Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
+Field surveys using environmental DNA (eDNA) are widely used for monitoring such as endangered species, invasive species, and biodiversity 
+%detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
 because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al.
-2014; Thomsen \& Willerslev 2015) %Dorazioに引用されていたやつ．あとで再確認
+2014; Thomsen \& Willerslev 2015).
+%Dorazioに引用されていたやつ．あとで再確認
 However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig.
 1).
-Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species.
+Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species from eDNA occurrence data.
 
@@
 \ \ \ \ \ \ \ \ \ \ 
-After the suggestion of the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016), the studies which used laboratory experiments and numerical hydrological models have been increased to overcome the uncertainty of eDNA.
+After the suggestion of the importance of understanding about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016), the studies which used laboratory experiments and numerical hydrological models have been increased to overcome the uncertainty of eDNA.
 %To overcome the uncertainty of eDNA, the studies which used Laboratory experiments and numerical hydrological models have been increased after suggested the importance to understand about origin, state, transport, and fate of eDNA ("ecology of eDNA") by Barnes \& Turner (2016).

### 2021-03-12 results/draft.tex
added a ref. into Intro

@@
 Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
-Field surveys using environmental DNA (eDNA) are widely used for monitoring such as endangered species, invasive species, and biodiversity 
+Field surveys using environmental DNA (eDNA) are widely used for monitoring such as endangered species, invasive species (e.g., Dougherty et al. 2016%ザリガニJ appl ecol
+; Larson et al. 2020%レビュー
+), and biodiversity 
 %detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 

### 2021-03-12 R/makedata2019.R
initial commit

@@ -1,0 +1,32 @@
+dir_input = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/"
+dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/"
+
+require(tidyverse)
+require(openxlsx)
+require(gdata)
+
+# 2019 ----------------------------------------------------------
+# eDNA ----------------------------------------------------------
+setwd(dir = dir_input)
+d2019_1 <- read.table("Data/COUNT.mifish1.nrOTU.id97.unoise.txt", header = T)
+d2019_2 <- read.table("Data/COUNT.mifish2.nrOTU.id97.unoise.txt", header = T)
+
+setwd(dir = dir_output)
+sp1 = read.xls("splist2019.xlsx", sheet = 1)
+sp2 = read.xls("splist2019.xlsx", sheet = 2)
+
+d2019_1 = inner_join(sp1, d2019_1, by = "ID")
+d2019_1 = d2019_1 %>% gather(key = tag, value = copy, 5:ncol(d2019_1)) 
+d2019_1 = d2019_1 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), depth = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
+
+d2019_2 = inner_join(sp2, d2019_2, by = "ID")
+d2019_2 = d2019_2 %>% gather(key = tag, value = copy, 5:ncol(d2019_2)) 
+d2019_2 = d2019_2 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), depth = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
+
+summary(d2019_1)
+summary(d2019_2)
+
+df = rbind(d2019_1, d2019_2)
+
+setwd(dir = dir_output)
+write.csv(df, "joint_edna2019.csv")

### 2021-03-12 R/makedata2019.R
load env data

@@ -26,7 +26,114 @@ d2019_2 = d2019_2 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5))
 summary(d2019_1)
 summary(d2019_2)
 
-df = rbind(d2019_1, d2019_2)
+edna = rbind(d2019_1, d2019_2)
+
+lonlat = read.table("2018/sampling_points.txt", header = T)
+lonlat = lonlat %>% dplyr::rename(site = pop)
+mifish = left_join(edna, lonlat, by = "site")
+#%>% mutate(tag = paste(month, day, site, layer, sep = "_"))
+
+
+
+
+# env. data ------------------------------------------------------
+setwd(dir = dir_input)
+# env = read_csv("Data/Env_data_merged_unique.csv")
+# summary(env)
+
+#========== env1 ==========#
+dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env1"
+setwd(dir = dir)
+path = dir
+files = list.files(path)
+
+env1 = NULL
+for(i in 1:length(files)){
+  temp = read.csv(paste0(files[i]))
+  temp = temp[, 1:16]
+  temp = temp %>% mutate(year = 2019, month = as.numeric(str_sub(files[i], 9, 10)), day = str_sub(colnames(temp)[1], -2, -1))
+  colnames(temp)[1] = "pop"
+  env1 = rbind(env1, temp)
+}
+
+
+#========== env_129 ==========#
+dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_129"
+setwd(dir = dir)
+path = dir
+files = list.files(path)
+
+env_129 = NULL
+for(i in 1:length(files)){
+  temp = read.xls(paste0(files[i]), sheet = 6, skip = 43)
+  temp = temp %>% mutate(year = 2019, month = as.numeric(str_sub(日付情報, 6, 7)), day = as.numeric(str_sub(日付情報, 9, 10)), site = 129)
+  env_129 = rbind(env_129, temp)
+}
+
+
+#========== env2 ==========#
+# dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env2"
+# setwd(dir = dir)
+# path = dir
+# files = list.files(path)
+# 
+# ###あとで
+
+
+#========== env_27 ==========#
[…]

### 2021-03-12 R/makedata2019.R
added env data into eDNA for Chiba data

@@ -17,11 +17,11 @@ sp2 = read.xls("splist2019.xlsx", sheet = 2)
 
 d2019_1 = inner_join(sp1, d2019_1, by = "ID")
 d2019_1 = d2019_1 %>% gather(key = tag, value = copy, 5:ncol(d2019_1)) 
-d2019_1 = d2019_1 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), depth = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
+d2019_1 = d2019_1 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), SorB = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
 
 d2019_2 = inner_join(sp2, d2019_2, by = "ID")
 d2019_2 = d2019_2 %>% gather(key = tag, value = copy, 5:ncol(d2019_2)) 
-d2019_2 = d2019_2 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), depth = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
+d2019_2 = d2019_2 %>% mutate(year = 2019, month = as.numeric(str_sub(tag, 4, 5)), day = as.numeric(str_sub(tag, 6, 7)), site = str_sub(tag, 9, -5), SorB = str_sub(tag, -3, -3), rep = str_sub(tag, -1, -1))
 
 summary(d2019_1)
 summary(d2019_2)
@@ -33,6 +33,7 @@ lonlat = lonlat %>% dplyr::rename(site = pop)
 mifish = left_join(edna, lonlat, by = "site")
 #%>% mutate(tag = paste(month, day, site, layer, sep = "_"))
 
+mifish = mifish %>% select(-tag) %>% mutate(tag = paste(year, month, day, site, SorB, sep = "_"))
 
 
 
@@ -130,6 +131,35 @@ for(i in 1:length(files)){
 env_136_1 = read.csv("/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/201901-136.csv", skip = 43, fileEncoding = "CP932")
[…]

### 2021-03-12 R/makedata2019.R
revised about three sites in kanagawa

@@ -4,6 +4,7 @@ dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/"
 require(tidyverse)
 require(openxlsx)
 require(gdata)
+require(abind)
 
 # 2019 ----------------------------------------------------------
 # eDNA ----------------------------------------------------------
@@ -42,6 +43,7 @@ setwd(dir = dir_input)
 # env = read_csv("Data/Env_data_merged_unique.csv")
 # summary(env)
 
+#========== chiba ==========#
 #========== env1 ==========#
 dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env1"
 setwd(dir = dir)
@@ -58,6 +60,9 @@ for(i in 1:length(files)){
 }
 
 
+
+
+#========== kanagawa ==========#
 #========== env_129 ==========#
 dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_129"
 setwd(dir = dir)
@@ -72,64 +77,85 @@ for(i in 1:length(files)){
 }
 
 
-#========== env2 ==========#
-# dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env2"
+
+
+# #========== env_27 ==========#
+# dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_27"
 # setwd(dir = dir)
 # path = dir
 # files = list.files(path)
 # 
-# ###あとで
+# env_27 = NULL
+# for(i in 1:length(files)){
+#   temp = read.table(paste0(files[i]), header = T)
+#   temp = temp %>% mutate(year = 2019, month = as.numeric(str_sub(files[i], 5, 6)), day = NA, site = 27)
+#   env_27 = rbind(env_27, temp)
+# }
+# 
+# env_27_1 = read.csv("/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/201901-27.csv", skip = 43, fileEncoding = "CP932")
+# env_27_1 = env_27_1 %>% mutate(year = 2019, month = 1, day = NA, site = 27)
+# 
+# 
+# #========== env_134 ==========#
+# dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_134"
+# setwd(dir = dir)
+# path = dir
+# files = list.files(path)
+# 
+# env_134 = NULL
+# for(i in 1:length(files)){
[…]

### 2021-03-12 R/makedata2019.R
combined Jan. data

@@ -156,10 +156,51 @@ envk1 = data.frame(t2) %>% mutate(year = 2019, month = as.numeric(str_sub(file, 
 (colnames(envk1))
 envk1 = envk1 %>% select("T090C", "Ph", "Sal00", "Sbeox0Mg.L","SorB", "year", "month", "day", "site")
 colnames(envk1) = c("temp", "pH", "salinity", "DO_mg","SorB", "year", "month", "day", "site")
+summary(envk1) #pHの値が変（負の値）
+
+### Jan.
+env_27_1 = read.csv("/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/201901-27.csv", skip = 43, fileEncoding = "CP932")
+env_27_1 = env_27_1 %>% mutate(year = 2019, month = 1, day = NA, site = 27)
+t = env_27_1
+min = min(t$深度..m.)
+max = max(t$深度..m.)
+s = t %>% filter(深度..m. == min) %>% mutate(SorB = "S")
+b = t %>% filter(深度..m. == max) %>% mutate(SorB = "B")
+env_27_1 = rbind(s, b)
+
+env_134_1 = read.csv("/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/201901-134.csv", skip = 43, fileEncoding = "CP932")
+env_134_1 = env_134_1 %>% mutate(year = 2019, month = 1, day = NA, site = 134)
+t = env_134_1
+min = min(t$深度..m.)
+max = max(t$深度..m.)
+s = t %>% filter(深度..m. == min) %>% mutate(SorB = "S")
+b = t %>% filter(深度..m. == max) %>% mutate(SorB = "B")
+env_134_1 = rbind(s, b)
+
+env_136_1 = read.csv("/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/201901-136.csv", skip = 43, fileEncoding = "CP932")
+env_136_1 = env_136_1 %>% mutate(year = 2019, month = 1, day = NA, site = 136)
+t = env_136_1
+min = min(t$深度..m.)
+max = max(t$深度..m.)
+s = t %>% filter(深度..m. == min) %>% mutate(SorB = "S")
+b = t %>% filter(深度..m. == max) %>% mutate(SorB = "B")
+env_136_1 = rbind(s, b)
+
+jan = rbind(env_27_1, env_134_1, env_136_1)
+
+(colnames(jan))
[…]

### 2021-03-12 R/makedata2019.R
finished env data in kanagawa

@@ -63,18 +63,18 @@ for(i in 1:length(files)){
 
 
 #========== kanagawa ==========#
-#========== env_129 ==========#
-dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_129"
-setwd(dir = dir)
-path = dir
-files = list.files(path)
-
-env_129 = NULL
-for(i in 1:length(files)){
-  temp = read.xls(paste0(files[i]), sheet = 6, skip = 43)
-  temp = temp %>% mutate(year = 2019, month = as.numeric(str_sub(日付情報, 6, 7)), day = as.numeric(str_sub(日付情報, 9, 10)), site = 129)
-  env_129 = rbind(env_129, temp)
-}
+# #========== env_129 ==========#
+# dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/env_129"
+# setwd(dir = dir)
+# path = dir
+# files = list.files(path)
+# 
+# env_129 = NULL
+# for(i in 1:length(files)){
+#   temp = read.xls(paste0(files[i]), sheet = 6, skip = 43)
+#   temp = temp %>% mutate(year = 2019, month = as.numeric(str_sub(日付情報, 6, 7)), day = as.numeric(str_sub(日付情報, 9, 10)), site = 129)
+#   env_129 = rbind(env_129, temp)
+# }
 
 
 
@@ -194,6 +194,36 @@ colnames(jan) = c("temp", "salinity", "DO_mg","SorB", "year", "month", "day", "s
 jan$pH = NA
 
 envk1 = rbind(jan, envk1)
+
+
+
+# st129 ---------------------------------------------------------
+st2 = "env_129"
+path2 = paste0(dir, st2)
+setwd(path2)
+(files2 = list.files())
+t2 = NULL
+
+for(i in 1:length(files2)){
+  t = read.xls(paste0(files2[i]), sheet = 6, skip = 43) %>% dplyr::rename(dep = "深度..m.")
+  min = min(t[, 3])
+  max = max(t[, 3])
+  s = t %>% filter(dep == min) %>% mutate(SorB = "S")
+  b = t %>% filter(dep == max) %>% mutate(SorB = "B")
+  sb = rbind(s, b)
+  t2 = abind(t2, sb, along = 1)
+}
[…]

### 2021-03-12 R/makedata2019.R
made joint_edna2019.csv

@@ -260,7 +260,39 @@ e_chi = merge(e_chi, ph, by = "tag", all = T)
 
 
 
+# ---------------------------------------------------------------
+# kanagawa ---------------------------------------------------------
+# ---------------------------------------------------------------
+#st27
+st27 = mifish %>% filter(site == "27") %>% select(-tag) %>% mutate(tag = paste(year, month, SorB, sep = "_"))
+env27 = env_kana %>% filter(site == "27") %>% mutate(tag = paste(year, month, SorB, sep = "_")) %>% select(-year, -month, -day, -site, -SorB)
+st27 = merge(st27, env27, by = "tag")
 
+#st134
+st134 = mifish %>% filter(site == "134") %>% select(-tag) %>% mutate(tag = paste(year, month, SorB, sep = "_"))
+env134 = env_kana %>% filter(site == "134") %>% mutate(tag = paste(year, month, SorB, sep = "_")) %>% select(-year, -month, -day, -site, -SorB)
+st134 = merge(st134, env134, by = "tag")
+
+#st136
+st136 = mifish %>% filter(site == "136") %>% select(-tag) %>% mutate(tag = paste(year, month, SorB, sep = "_"))
+env136 = env_kana %>% filter(site == "136") %>% mutate(tag = paste(year, month, SorB, sep = "_")) %>% select(-year, -month, -day, -site, -SorB)
+st136 = merge(st136, env136, by = "tag")
+
+#st129
+st129 = mifish %>% filter(site == "129") %>% select(-tag) %>% mutate(tag = paste(year, month, SorB, sep = "_"))
+env129 = env_kana %>% filter(site == "129") %>% mutate(tag = paste(year, month, SorB, sep = "_")) %>% select(-year, -month, -day, -site, -SorB)
+st129 = merge(st129, env129, by = "tag")
+
+e_kana = rbind(st27, st134)
+e_kana = rbind(e_kana, st136)
+e_kana = rbind(e_kana, st129)
+unique(e_kana$site)
+
+
+# combine -------------------------------------------------------
+colnames(e_chi)
+colnames(e_kana)
+mifish = rbind(e_chi %>% dplyr::rename(temp = 水温, salinity = 塩分, DO_mg = DO.mg., pH = ｐＨ), e_kana)
 
 setwd(dir = dir_output)
-write.csv(df, "joint_edna2019.csv")
+write.csv(mifish, "joint_edna2019.csv", fileEncoding = "CP932")

### 2021-03-12 R/makedata2019.R
small changes

@@ -38,10 +38,11 @@ mifish = mifish %>% select(-tag) %>% mutate(tag = paste(year, month, day, site, 
 
 
 
+
+# ---------------------------------------------------------------
 # env. data ------------------------------------------------------
+# ---------------------------------------------------------------
 setwd(dir = dir_input)
-# env = read_csv("Data/Env_data_merged_unique.csv")
-# summary(env)
 
 #========== chiba ==========#
 #========== env1 ==========#
@@ -130,6 +131,9 @@ for(i in 1:length(files)){
 # env_136_1 = env_136_1 %>% mutate(year = 2019, month = 1, day = NA, site = 136)
 
 
+
+
+#========== kanagawa ==========#
 # st27, 134, 136 ------------------------------------------------
 dir = "/Users/Yuki/Dropbox/eDNA_INLA/篠原さん由来/Data/"
 st = c("env_27", "env_134", "env_136")
@@ -232,7 +236,7 @@ env_kana = rbind(envk1, envk2)
 # chiba ---------------------------------------------------------
 # ---------------------------------------------------------------
 #eDNA
-e_chi = mifish %>% filter(site != "27") %>% filter(site != "134") %>% filter(site != "136") %>% filter(site != "129")
+e_chi = mifish %>% filter(site != "27") %>% filter(site != "134") %>% filter(site != "136") %>% filter(site != "129") #4772
 unique(e_chi$site)
 
 unique(env1$pop)
@@ -242,7 +246,7 @@ env1 = env1 %>% mutate(site = if_else(site %in% c("ANESAKI", "ANE"), "AZ", site)
   mutate(site = if_else(site == "FUTTU", "FT", site)) %>%
   mutate(site = if_else(site %in% c("URA", "URAYASU"), "UY", site)) %>%
   mutate(SorB = rep(c("S", "B"), nrow(env1)/2)) %>% 
-  mutate(tag = paste(year, month, day, site, SorB, sep = "_"))
+  mutate(tag = paste(year, month, day, site, SorB, sep = "_")) #398
 
 unique(env1$site)
 

### 2021-03-13 R/makecpuedata2019.R
initial commit

@@ -1,0 +1,79 @@
+dir_input = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/追加データ2020年3月まで/"
+dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/"
+
+require(tidyverse)
+require(openxlsx)
+require(gdata)
+require(abind)
+
+
+# combine the added data ----------------------------------------------------------
+# (catch only data; not include zero data) ----------------------------------------------------------
+setwd(dir = dir_input)
+path = dir_input
+files = list.files(path)
+
+all = NULL
+for(i in 1:length(files)){
+  temp = read.xlsx(paste0(files[i]), colNames = T)
+  temp = temp %>% select(年月日, 緯度, 経度, 回数, CPUE, 全銘柄) %>%
+    mutate(check = as.Date(temp$年月日, origin = "1899-12-30")) %>% 
+    mutate(year = as.numeric(str_sub(check, 1, 4)), month = as.numeric(str_sub(check, 6, 7)), day = as.numeric(str_sub(check, 9, 10))) 
+  
+  # gear
+  if(str_detect(files[i], pattern = "ビーム")){
+    temp = temp %>% mutate(gear = "beam")
+  }else{
+    temp = temp %>% mutate(gear = "keta")
+  }
+  
+  #species name
+  if(str_detect(files[i], pattern = "イシガレイ")){
+    temp$sp = "isigarei"
+  }
+  if(str_detect(files[i], pattern = "ｲｼﾓﾁ")){
+    temp$sp = "isimoti-rui"
+  }
+  if(str_detect(files[i], pattern = "カマス")){
+    temp$sp = "kamasu-rui"
+  }
+  if(str_detect(files[i], pattern = "クルマエビ")){
+    temp$sp = "kurumaebi"
+  }
+  if(str_detect(files[i], pattern = "クロダイ")){
+    temp$sp = "kurodai"
+  }
+  if(str_detect(files[i], pattern = "コウイカ")){
+    temp$sp = "kouika"
+  }
+  if(str_detect(files[i], pattern = "コノシロ")){
+    temp$sp = "konosiro"
+  }
+  if(str_detect(files[i], pattern = "スズキ")){
+    temp$sp = "suzuki"
+  }
+  if(str_detect(files[i], pattern = "トラフグ")){
+    temp$sp = "torafugu"
+  }
[…]

### 2021-03-13 R/makecpuedata.R
remove two data

@@ -77,39 +77,3 @@ all = all %>% dplyr::rename(catch = 全銘柄, effort = 回数) %>%
 
 setwd(dir = dir_output)
 write.csv(all, "added_data.csv")
-
-
-
-
-
-
-
-
-# check spatial location -------------------------------
-require(maps)
-require(mapdata)
-library(ggrepel)
-
-p <- ggplot() + coord_fixed() +
-  xlab("Longitude") + ylab("Latitude")
-world_map <- map_data("world")
-jap <- subset(world_map, world_map$region == "Japan")
-jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-t2 <- p + geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")+ coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
-t2 + geom_point(data = all, aes(x = lon, y = lat), shape = 16, size = 1)
-summary(all)
-
-tent = all[all$lon > 139.7, ]
-summary(tent)
-t2 + geom_point(data = tent, aes(x = lon, y = lat), shape = 16, size = 1)
-
-ue = tent %>% filter(lat > 35.4)
-sita = tent %>% filter(lat <= 35.4)
-t2 + geom_point(data = sita, aes(x = lon, y = lat), shape = 16, size = 1)
-summary(sita)
-sita = sita[sita$lon != max(sita$lon), ]
-t2 + geom_point(data = sita, aes(x = lon, y = lat), shape = 16, size = 1)
-
-tent2 = rbind(ue, sita)
-setwd(dir = dir_output)
-write.csv(tent, "tent.csv")

### 2021-03-13 R/makecpuedata2019.R
try to add zero data

@@ -112,4 +112,28 @@ t2 + geom_point(data = sita, aes(x = lon, y = lat), shape = 16, size = 1)
 
 tent2 = rbind(ue, sita)
 setwd(dir = dir_output)
-write.csv(tent, "tent.csv")
+write.csv(tent2, "tent.csv")
+
+
+
+# add zero data -------------------------------
+tent2 = tent2 %>% mutate(tag = paste(year, month, day, lon, lat, sep = "_"))
+# effort = tent2 %>% filter(year == 2019) %>% group_by(tag) %>% summarize(t_effort = sum(effort)) 
+# tent3 = left_join(tent2 %>% filter(year == 2019), effort, by = "tag")
+
+splist = unique(tent2$sp)
+for(i in 1:length(splist)){
+  assign(paste(splist[i]),
+         tent2 %>% filter(sp == splist[i]))
+}
+
+test = left_join(konosiro %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), 
+                 suzuki %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), by = "tag", all = T)
+
+tent3 = tent2 %>% filter(year == 2019)
+taglist = data.frame(tag = tent3$tag)
+test = left_join(taglist, konosiro %>% filter(year == 2019), by = "tag", all = T)
+
+
+
+

### 2021-03-13 R/makecpuedata2019.R
added zero data

@@ -117,8 +117,8 @@ write.csv(tent2, "tent.csv")
 
 
 # add zero data -------------------------------
-tent2 = tent2 %>% mutate(tag = paste(year, month, day, lon, lat, sep = "_"))
-# effort = tent2 %>% filter(year == 2019) %>% group_by(tag) %>% summarize(t_effort = sum(effort)) 
+tent2 = tent2 %>% mutate(tag = paste(year, formatC(tent2$month, width=2, flag="0"), formatC(tent2$day, width=2, flag="0"), format(as.numeric(str_sub(tent2$lon, 1, 8)), nsmall = 4), format(as.numeric(str_sub(tent2$lat, 1, 8)), nsmall = 4), sep = "_"))
+effort = tent2 %>% filter(year == 2019) %>% group_by(tag) %>% summarize(m_effort = mean(effort)) 
 # tent3 = left_join(tent2 %>% filter(year == 2019), effort, by = "tag")
 
 splist = unique(tent2$sp)
@@ -127,13 +127,38 @@ for(i in 1:length(splist)){
          tent2 %>% filter(sp == splist[i]))
 }
 
-test = left_join(konosiro %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), 
-                 suzuki %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), by = "tag", all = T)
+# test = left_join(konosiro %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), 
+#                  suzuki %>% filter(year == 2019) %>% select(tag, effort, CPUE, catch), by = "tag", all = T)
 
 tent3 = tent2 %>% filter(year == 2019)
-taglist = data.frame(tag = tent3$tag)
-test = left_join(taglist, konosiro %>% filter(year == 2019), by = "tag", all = T)
+taglist = data.frame(tag = unique(tent3$tag)) 
+taglist = taglist %>% 
+  mutate(year = as.numeric(str_sub(tag, 1, 4)), month = as.numeric(str_sub(tag, 6, 7)), day = as.numeric(str_sub(tag, 9, 10)), 
+         lon = as.numeric(str_sub(tag, 12, 19)), lat = as.numeric(str_sub(tag, 21, 28)))
+taglist = left_join(taglist, effort, by = "tag")
 
[…]

### 2021-03-13 R/makecpuedata2019.R
revised the csv name

@@ -161,4 +161,4 @@ for(i in 1:length(splist)){
 }
 
 setwd(dir = dir_output)
-write.csv(cpue2019, "cpue2019.csv")
+write.csv(cpue2019, "joint_cpue2019.csv")

### 2021-03-13 R/makedata2019.R
revised lonlat in FT

@@ -30,6 +30,7 @@ summary(d2019_2)
 edna = rbind(d2019_1, d2019_2)
 
 lonlat = read.table("2018/sampling_points.txt", header = T)
+lonlat[1, 4] = "FT"
 lonlat = lonlat %>% dplyr::rename(site = pop)
 mifish = left_join(edna, lonlat, by = "site")
 #%>% mutate(tag = paste(month, day, site, layer, sep = "_"))

### 2021-03-13 R/makecpuedata2019.R
removed the location

@@ -103,6 +103,8 @@ tent = all[all$lon > 139.7, ]
 summary(tent)
 t2 + geom_point(data = tent, aes(x = lon, y = lat), shape = 16, size = 1)
 
+tent = all[all$lon < 140.2, ] #地図の外にもデータがあるっぽい
+
 ue = tent %>% filter(lat > 35.4)
 sita = tent %>% filter(lat <= 35.4)
 t2 + geom_point(data = sita, aes(x = lon, y = lat), shape = 16, size = 1)

### 2021-03-13 R/konosiro2019.R
initial commit

@@ -1,0 +1,399 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2018 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+# データは4~12月，神奈川は地点によって調査がなかった月がある
+mifish = read.csv("joint_edna2019.csv")
+
+# sp1 = read.xlsx("splist2019.xlsx", sheet = 1, colNames = T)
+# sp2 = read.xlsx("splist2019.xlsx", sheet = 2, colNames = T)
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2019.csv")
+
+
+# コノシロ ------------------------------------
+e_fish = mifish %>% filter(sp_group == "konosiro", SorB == "B")
+summary(e_fish)
+unique(e_fish$ID)
+edna = (e_fish$copy > 0) + 0
+
+c_fish = data %>% filter(sp == "konosiro")
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
[…]

### 2021-03-13 R/konosiro2019.R
model check

@@ -144,6 +144,7 @@ ep_stk = inla.stack(data = list(y = cbind(na[, 1], na[, 2])),
                     tag = "ep_dat")
 stk_edna = inla.stack(e_stk, ep_stk)
 
+
 #cpue
 c_stk = inla.stack(data = list(y = cbind(NA, catch)),
                    A = list(c_A, 1),
@@ -162,6 +163,7 @@ stk = inla.stack(stk_edna, stk_catch)
 # formula
 formula = y ~ 0 + cb.0 + eb.0 + offset(effort) + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
 # + f(DO, model = "rw1") 
+
 
 # formula = y ~ 0 + cb.0 + eb.0 + offset(effort) + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
 # formula = y ~ 0 + eb.0 + cb.0 + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.e, model = spde) + f(i.c, copy = "i.e", fixed = FALSE) + f(effort, model = "rw1")
@@ -183,7 +185,7 @@ res_kono = inla(formula,
 #                 control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
 #                 control.compute = list(waic = TRUE, dic = TRUE))
 
-res_kono$waic$waic; res_kono$dic$dic #640.3, 640.4
+res_kono$waic$waic; res_kono$dic$dic #514.1, NaN / i.e2なしだと514.5, NaN /i.e2とi.c2なしだと11439, 11415
 # res_kono2$waic$waic; res_kono2$dic$dic #640.4, 640.5 
 summary(res_kono)
 

### 2021-03-13 R/maanago2019.R
initial commit

@@ -1,0 +1,402 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2018 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+# データは1~12月，神奈川は環境データに不安がある
+mifish = read.csv("joint_edna2019.csv")
+
+# sp1 = read.xlsx("splist2019.xlsx", sheet = 1, colNames = T)
+# sp2 = read.xlsx("splist2019.xlsx", sheet = 2, colNames = T)
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2019.csv")
+
+
+# マアナゴ ------------------------------------
+e_fish = mifish %>% filter(sp_group == "maanago", SorB == "B")
+summary(e_fish)
+unique(e_fish$ID)
+edna = (e_fish$copy > 0) + 0
+
+c_fish = data %>% filter(sp == "maanago")
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
[…]

### 2021-03-13 R/suzuki2019.R
initial commit

@@ -1,0 +1,400 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2019 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+mifish = read.csv("joint_edna2019.csv")
+
+# sp1 = read.xlsx("splist2019.xlsx", sheet = 1, colNames = T)
+# sp2 = read.xlsx("splist2019.xlsx", sheet = 2, colNames = T)
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2019.csv")
+
+
+# スズキ ------------------------------------
+e_fish = mifish %>% filter(sp_group == "suzuki", SorB == "B")
+summary(e_fish)
+unique(e_fish$ID)
+edna = (e_fish$copy > 0) + 0
+
+c_fish = data %>% filter(sp == "suzuki")
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
+points(e_loc, col = "green", pch = 16, cex = 1)
[…]

### 2021-03-13 R/makogarei2019.R
initial commit

@@ -1,0 +1,400 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2019 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+mifish = read.csv("joint_edna2019.csv")
+
+# sp1 = read.xlsx("splist2019.xlsx", sheet = 1, colNames = T)
+# sp2 = read.xlsx("splist2019.xlsx", sheet = 2, colNames = T)
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2019.csv")
+
+
+# スズキ ------------------------------------
+e_fish = mifish %>% filter(sp_group == "makogarei", SorB == "B")
+summary(e_fish)
+unique(e_fish$ID)
+edna = (e_fish$copy > 0) + 0
+
+c_fish = data %>% filter(sp == "makogarei")
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
+points(e_loc, col = "green", pch = 16, cex = 1)
[…]

### 2021-03-13 R/isigarei2019.R
initial commit

@@ -1,0 +1,400 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2019 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+mifish = read.csv("joint_edna2019.csv")
+
+# sp1 = read.xlsx("splist2019.xlsx", sheet = 1, colNames = T)
+# sp2 = read.xlsx("splist2019.xlsx", sheet = 2, colNames = T)
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2019.csv")
+
+
+# スズキ ------------------------------------
+e_fish = mifish %>% filter(sp_group == "isigarei", SorB == "B")
+summary(e_fish)
+unique(e_fish$ID)
+edna = (e_fish$copy > 0) + 0
+
+c_fish = data %>% filter(sp == "isigarei")
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
+points(e_loc, col = "green", pch = 16, cex = 1)
+mesh2$n #651
+
+# projector matricies
[…]

### 2021-03-14 R/2018/makedata2018.R
added species group

@@ -10,7 +10,7 @@ edna = read.table("2018_Mifish/COUNT.mifish.unoise.2018.v2.txt", header = T)
 unique(edna$layer)
 edna = edna %>% gather(key = zotu, value = count, 6:ncol(edna))
 (unique(edna$zotu))
-analize = data.frame(zotu = c("Zotu62", "Zotu59", "Zotu120", "Zotu6", "Zotu1", "Zotu13"), sp = c("maanago", "makogarei", "isigarei", "suzuki", "konosiro", "kurodai"))
+analize = data.frame(zotu = c("Zotu62", "Zotu59", "Zotu120", "Zotu6", "Zotu1", "Zotu13", "Zotu14", "Zotu137", "Zotu23", "Zotu64", "Zotu48"), sp = c("maanago", "makogarei", "isigarei", "suzuki", "konosiro", "kurodai", "siroguti", "nibe", "akakamasu", "yamatokamasu", "kurosibikamasu"), sp_group = c("maanago", "makogarei", "isigarei", "suzuki", "konosiro", "kurodai", "isimoti-rui", "isimoti-rui", "kamasu-rui", "kamasu-rui", "kamasu-rui"))
 edna2 = edna %>% filter(zotu %in% analize$zotu)
 edna2 = merge(edna2, analize, by = "zotu")
 (unique(edna2$site))

### 2021-03-14 R/2018/makedata2018.R
checked the included sp in cupe data

@@ -92,6 +92,7 @@ setwd("/Users/Yuki/Dropbox/Network2020")
 data = read.csv("VASTdata.csv") %>% filter(Y == 2018)
 head(data, 2)
 summary(data)
+unique(data$FISH)
 # data = data %>% mutate(lon = Lon %/% 1 + (Lon %% 1)*60 + 0.05, lat = Lat %/% 1 + (Lat %% 1)*60 + 0.05)
 
 setwd("/Users/Yuki/Dropbox/eDNA_INLA")

### 2021-03-14 R/2019/makecpuedata.R
deleted

@@ -1,79 +1,0 @@
-dir_input = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/追加データ2020年3月まで/"
-dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/"
-
-require(tidyverse)
-require(openxlsx)
-require(gdata)
-require(abind)
-
-
-# combine the added data ----------------------------------------------------------
-# (catch only data; not include zero data) ----------------------------------------------------------
-setwd(dir = dir_input)
-path = dir_input
-files = list.files(path)
-
-all = NULL
-for(i in 1:length(files)){
-  temp = read.xlsx(paste0(files[i]), colNames = T)
-  temp = temp %>% select(年月日, 緯度, 経度, 回数, CPUE, 全銘柄) %>%
-    mutate(check = as.Date(temp$年月日, origin = "1899-12-30")) %>% 
-    mutate(year = as.numeric(str_sub(check, 1, 4)), month = as.numeric(str_sub(check, 6, 7)), day = as.numeric(str_sub(check, 9, 10))) 
-  
-  # gear
-  if(str_detect(files[i], pattern = "ビーム")){
-    temp = temp %>% mutate(gear = "beam")
-  }else{
-    temp = temp %>% mutate(gear = "keta")
-  }
-  
-  #species name
-  if(str_detect(files[i], pattern = "イシガレイ")){
-    temp$sp = "isigarei"
-  }
-  if(str_detect(files[i], pattern = "ｲｼﾓﾁ")){
-    temp$sp = "isimoti-rui"
-  }
-  if(str_detect(files[i], pattern = "カマス")){
-    temp$sp = "kamasu-rui"
-  }
-  if(str_detect(files[i], pattern = "クルマエビ")){
-    temp$sp = "kurumaebi"
-  }
-  if(str_detect(files[i], pattern = "クロダイ")){
-    temp$sp = "kurodai"
-  }
-  if(str_detect(files[i], pattern = "コウイカ")){
-    temp$sp = "kouika"
-  }
-  if(str_detect(files[i], pattern = "コノシロ")){
-    temp$sp = "konosiro"
-  }
-  if(str_detect(files[i], pattern = "スズキ")){
-    temp$sp = "suzuki"
-  }
-  if(str_detect(files[i], pattern = "トラフグ")){
-    temp$sp = "torafugu"
-  }
[…]

### 2021-03-14 R/2018/makedata2018tuika.R
initial commit

@@ -1,0 +1,145 @@
+dir_input = "/Users/Yuki/Dropbox/Network/千葉追加データ"
+dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/"
+
+require(tidyverse)
+require(openxlsx)
+require(gdata)
+require(abind)
+
+
+# combine the added data ----------------------------------------------------------
+# (catch only data; not include zero data) ----------------------------------------------------------
+setwd(dir = dir_input)
+path = dir_input
+files = list.files(path)
+
+all = NULL
+for(i in 1:length(files)){
+  temp = read.xlsx(paste0(files[i]), colNames = T)
+  temp = temp %>% select(年月日, 緯度, 経度, 回数, CPUE, 全銘柄) %>%
+    mutate(check = as.Date(temp$年月日, origin = "1899-12-30")) %>% 
+    mutate(year = as.numeric(str_sub(check, 1, 4)), month = as.numeric(str_sub(check, 6, 7)), day = as.numeric(str_sub(check, 9, 10))) 
+  
+  # gear
+  if(str_detect(files[i], pattern = "不明")){
+    temp = temp %>% mutate(gear = "Beam Fumei")
+  }
+  if(str_detect(files[i], pattern = "スズキ")){
+    temp = temp %>% mutate(gear = "Beam Suzuki")
+  }
+  if(str_detect(files[i], pattern = "桁曳網")){
+    temp = temp %>% mutate(gear = "Keta")
+  }
+  
+  #species name
+  if(str_detect(files[i], pattern = "シログチ")){
+    temp$sp = "isimoti-rui"
+  }
+  if(str_detect(files[i], pattern = "カマス")){
+    temp$sp = "kamasu-rui"
+  }
+  if(str_detect(files[i], pattern = "クロダイ")){
+    temp$sp = "kurodai"
+  }
+  if(str_detect(files[i], pattern = "トラフグ")){
+    temp$sp = "torafugu"
+  }
+
+  
+  all = rbind(all, temp)
+  
+}
+# check
+unique(all$sp)
+unique(all$gear)
+
+all = all %>% dplyr::rename(catch = 全銘柄, effort = 回数) %>% 
+  mutate(lat = 緯度 %/% 100 + 緯度 %% 100/60, lon = 経度 %/% 100 + 経度 %% 100/60) %>% 
[…]

### 2021-03-14 R/2018/makedata2018tuika.R
revised dir

@@ -1,5 +1,5 @@
 dir_input = "/Users/Yuki/Dropbox/Network/千葉追加データ"
-dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/cpue2019/"
+dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/"
 
 require(tidyverse)
 require(openxlsx)

### 2021-03-14 R/2018/kurodai.R
small changed

@@ -1,0 +1,383 @@
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+
+require(INLA)
+require(tidyverse)
+require(openxlsx)
+
+# 2018 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+# データは4~12月，神奈川は地点によって調査がなかった月がある
+mifish = read.csv("joint_edna2018.csv")
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2018_tuikasp.csv")
+
+
+# クロダイ ------------------------------------
+e_fish = mifish %>% filter(sp == "kurodai", layer == "B")
+summary(e_fish)
+edna = (e_fish$count > 0) + 0
+
+c_fish = data %>% filter(sp == "kurodai")
+# c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+summary(c_fish)
+catch = (c_fish$catch > 0) + 0
+# catch = (c_fish$CPUE > 0) + 0
+summary(catch)
+
+# e_fish = e_fish %>% mutate(Month = as.factor(month))
+# c_fish = c_fish %>% mutate(Month = as.factor(M), Gear = as.factor(GEAR))
+
+# INLA ----------------------------------------------------------
+#lonlat
+e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+loc = rbind(e_loc, c_loc)
+
+c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+
+bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
+mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+plot(mesh2)
+points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
[…]

### 2021-03-14 R/2018/kurodai.R
using cpue and scaled data

@@ -22,8 +22,9 @@ edna = (e_fish$count > 0) + 0
 c_fish = data %>% filter(sp == "kurodai")
 # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
 summary(c_fish)
-catch = (c_fish$catch > 0) + 0
-# catch = (c_fish$CPUE > 0) + 0
+c_fish$cpue = c_fish$catch/c_fish$m_effort
+# catch = (c_fish$catch > 0) + 0
+catch = (c_fish$cpue > 0) + 0
 summary(catch)
 
 # e_fish = e_fish %>% mutate(Month = as.factor(month))
@@ -124,7 +125,7 @@ na = as.matrix(cbind(rep(NA, nrow(coop)), rep(NA, nrow(coop))))
 ep_stk = inla.stack(data = list(y = cbind(na[, 1], na[, 2])),
                     A = list(Ap, 1),
                     effects = list(list(i.e = 1:mesh2$n, i.e2 = 1:mesh2$n), 
-                                   list(eb.0 = rep(1, nrow(coop)), temp = rep(1, nrow(coop)), salinity = rep(1, nrow(coop)), DO = rep(1, nrow(coop)), pH = rep(1, nrow(coop)))
+                                   list(eb.0 = rep(1, nrow(coop)), temp = rep(1, nrow(coop)), salinity = rep(1, nrow(coop)), pH = rep(1, nrow(coop)))
                     ),
                     tag = "ep_dat")
 
@@ -146,8 +147,8 @@ stk_catch = inla.stack(c_stk, cp_stk)
 stk = inla.stack(stk_edna, stk_catch)
 
 # formula
-#formula = y ~ 0 + cb.0 + eb.0 + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
-formula = y ~ 0 + cb.0 + eb.0 + offset(effort) + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
[…]

### 2021-03-14 R/2018/kurodai.R
compared the model

@@ -148,7 +148,7 @@ stk = inla.stack(stk_edna, stk_catch)
 
 # formula
 formula = y ~ 0 + cb.0 + eb.0 + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
-#formula = y ~ 0 + cb.0 + eb.0 + offset(effort) + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
+formula = y ~ 0 + cb.0 + eb.0 + offset(effort) + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(pH, model = "rw1") + f(i.c, model = spde) + f(i.e, copy = "i.c", fixed = FALSE) + f(i.c2, model = spde) + f(i.e2, model = spde)
 # formula = y ~ 0 + eb.0 + cb.0 + f(temp, model = "rw1") + f(salinity, model = "rw1") + f(DO, model = "rw1") + f(pH, model = "rw1") + f(i.e, model = spde) + f(i.c, copy = "i.e", fixed = FALSE) + f(effort, model = "rw1")
 
 
@@ -170,6 +170,7 @@ res_kuro = inla(formula,
 
 res_kuro$waic$waic; res_kuro$dic$dic #2776, 2766 catch+offcet(effort)
 res_kuro$waic$waic; res_kuro$dic$dic #1076, 1077 DO抜き+スケーリング+CPUE
+res_kuro$waic$waic; res_kuro$dic$dic # 7796, 7792 DO抜き+スケーリング+catch+offcet(effort)
 # res_kono2$waic$waic; res_kono2$dic$dic #640.4, 640.5 
 summary(res_kuro)
 setwd(dir = "/Users/Yuki/Dropbox/eDNA_INLA/est0314")
@@ -385,4 +386,4 @@ l = geom_line()
 f = facet_wrap(~ variable, scales = "free")
 labs = labs(x = "Environmental variable", y = "Effect of environment", title = "konosiro")
 g+l+f+labs+theme_bw()
-summary(e_fish$pH)
+

### 2021-03-14 R/2018/loop.R
initial commit

@@ -1,0 +1,322 @@
+df_env = NULL
+
+for(i in 1:length(splist)){
+  setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimori-rui")
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp.csv")
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  c_fish$cpue = c_fish$catch/c_fish$m_effort
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+  c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+  
+  bound2 = inla.nonconvex.hull(loc, convex = 0.05, concave = -0.15)
[…]

### 2021-03-14 R/2018/loop.R
added rm(list =ls())

@@ -319,4 +319,6 @@ for(i in 1:length(splist)){
   labs = labs(x = "Environmental variable", y = "Effect of environment", title = "konosiro")
   env = g+l+f+labs+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/env_", splist[i], ".pdf"), plot = env, units = "in", width = 11.69, height = 8.27) 
+  
+  rm(list =ls())
 }

### 2021-03-14 R/2018/loop.R
revised

@@ -1,4 +1,5 @@
 df_env = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 
 for(i in 1:length(splist)){
   setwd("/Users/Yuki/Dropbox/eDNA_INLA")
@@ -8,7 +9,6 @@ for(i in 1:length(splist)){
   require(openxlsx)
   
   # 2018 ----------------------------------------------------------
-  splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimori-rui")
   
   # eDNA & env ----------------------------------------------------------
   # データは4~12月，神奈川は地点によって調査がなかった月がある
@@ -18,21 +18,22 @@ for(i in 1:length(splist)){
   # データは1-12月
   if(i < 6){
     data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
   }else{
     data = read.csv("joint_cpue2018_tuikasp.csv")
+    data$cpue = data$catch/data$m_effort
   }
   
   
   
   # select species ------------------------------------------------
-  e_fish = mifish %>% filter(sp == paste0(splist[i]), layer == "B")
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
   summary(e_fish)
   edna = (e_fish$count > 0) + 0
   
   c_fish = data %>% filter(sp == paste0(splist[i]))
   # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
   summary(c_fish)
-  c_fish$cpue = c_fish$catch/c_fish$m_effort
   # catch = (c_fish$catch > 0) + 0
   catch = (c_fish$cpue > 0) + 0
   summary(catch)
@@ -141,13 +142,12 @@ for(i in 1:length(splist)){
   #cpue
   c_stk = inla.stack(data = list(y = cbind(NA, catch)),
                      A = list(c_A, 1),
-                     effects = list(list(i.c = 1:mesh2$n, i.c2 = 1:mesh2$n), list(cb.0 = rep(1, length(catch)), effort = c_fish$m_effort)),
+                     effects = list(list(i.c = 1:mesh2$n, i.c2 = 1:mesh2$n), list(cb.0 = rep(1, length(catch)))),
[…]

### 2021-03-14 R/2018/loop.R
write.csv for env

@@ -320,3 +320,5 @@ for(i in 1:length(splist)){
   env = g+l+f+labs+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/env_", splist[i], ".pdf"), plot = env, units = "in", width = 11.69, height = 8.27) 
 }
+
+write.csv(df_env, "df_env.csv")

### 2021-03-14 R/2018/loop_do.R
initial commit

@@ -1,0 +1,329 @@
+df_env = NULL
+df_waic = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+  c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+  
[…]

### 2021-03-14 R/2018/loop.R
added waic

@@ -1,4 +1,5 @@
 df_env = NULL
+df_waic = NULL
 splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 
 for(i in 1:length(splist)){
@@ -319,6 +320,10 @@ for(i in 1:length(splist)){
   labs = labs(x = "Environmental variable", y = "Effect of environment", title = "konosiro")
   env = g+l+f+labs+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/env_", splist[i], ".pdf"), plot = env, units = "in", width = 11.69, height = 8.27) 
+
+  waic = data.frame(waic = res_kono$waic$waic, sp = paste0(splist[i]))
+  df_waic = rbind(df_waic, waic)
 }
 
 write.csv(df_env, "df_env.csv")
+write.csv(df_waic, "df_waic.csv")

### 2021-03-14 R/2018/loop_do.R
changed

@@ -321,7 +321,7 @@ labs = labs(x = "Environmental variable", y = "Effect of environment", title = "
 env = g+l+f+labs+theme_bw()
 ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/env_", splist[i], ".pdf"), plot = env, units = "in", width = 11.69, height = 8.27) 
 
-waic = data.frame(waic = res_kono$waic$waic, sp = paste0(splist[i]))
+waic = data.frame(waic = res$waic$waic, sp = paste0(splist[i]))
 df_waic = rbind(df_waic, waic)
 }
 

### 2021-03-14 R/2018/loop_doph.R
initial commit

@@ -1,0 +1,327 @@
+df_env = NULL
+df_waic = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+  c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+  
[…]

### 2021-03-14 R/2018/loop_doph.R
fixed a bug

@@ -134,8 +134,7 @@ for(i in 1:length(splist)){
   ep_stk = inla.stack(data = list(y = cbind(na[, 1], na[, 2])),
                       A = list(Ap, 1),
                       effects = list(list(i.e = 1:mesh2$n, i.e2 = 1:mesh2$n), 
-                                     list(eb.0 = rep(1, nrow(coop)), temp = rep(1, nrow(coop)), salinity = rep(1, nrow(coop))))
-                      ),
+                                     list(eb.0 = rep(1, nrow(coop)), temp = rep(1, nrow(coop)), salinity = rep(1, nrow(coop)))),
                       tag = "ep_dat")
   
   stk_edna = inla.stack(e_stk, ep_stk)

### 2021-03-14 R/2018/outputs.R
added figures of estimated eDNA and catch map

@@ -7,10 +7,11 @@ files1 = list.files(path_nasi, pattern = ".Rdata")
 
 # splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 df_waic1 = NULL
-for(i in 1:length(files)){
-  load(files[i])
-  waic = data.frame(waic = res$waic$waic, dic = res$dic$dic, sp = paste0(res[[54]]), do = "-")
-  df_waic1 = rbind(df_waic1, waic)
+for(i in 1:length(files1)){
+  setwd(dir = path_nasi)
+  load(files1[i])
+  waic1 = data.frame(waic = res$waic$waic, dic = res$dic$dic, sp = paste0(res[[54]]), do = "-")
+  df_waic1 = rbind(df_waic1, waic1)
 }
 
 
@@ -21,9 +22,10 @@ files2 = list.files(path_ari, pattern = ".Rdata")
 # splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 df_waic2 = NULL
 for(i in 1:length(files2)){
+  setwd(dir = path_ari)
   load(files2[i])
-  waic = data.frame(waic = res$waic$waic, dic = res$dic$dic, sp = paste0(res[[54]]), do = "+")
-  df_waic2 = rbind(df_waic2, waic)
+  waic2 = data.frame(waic = res$waic$waic, dic = res$dic$dic, sp = paste0(res[[54]]), do = "+")
+  df_waic2 = rbind(df_waic2, waic2)
 }
 
 df_model = rbind(df_waic1, df_waic2)
@@ -50,7 +52,7 @@ f = facet_wrap(~ sp, scales = "free", ncol = 4)
 labs = labs(x = "Temperature (scaled)", y = "Effect of environment", color = "Species")
 fig_env_temp = g+l+f+labs+theme_bw()
 
-# sal.
+# sal.　クロダイとスズキではピークが低い
 g = ggplot(env %>% filter(variable == "Salinity"), aes(x = x, y = y, color = sp))
 l = geom_line()
 f = facet_wrap(~ sp, scales = "free", ncol = 4)
@@ -67,3 +69,39 @@ fig_env_ph = g+l+f+labs+theme_bw()
[…]

### 2021-03-14 R/2018/outputs.R
changed color

@@ -98,7 +98,7 @@ edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
 g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = prob))
 t = geom_tile()
 c = coord_fixed(ratio = 1)
-s = scale_fill_gradient(name = "Occurrence", low = "white", high = "orange")
+s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
 catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
 
 ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/edna_", splist[i], ".pdf"), plot = edna, units = "in", width = 11.69, height = 8.27) 

### 2021-03-14 R/2018/get_est.R
initial commit

@@ -1,0 +1,256 @@
+# path_nasi = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし"
+# files1 = list.files(path_nasi, pattern = ".Rdata")
+
+
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+
+for(i in 1:length(splist[i])){
+  setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
[…]

### 2021-03-14 R/2018/get_est.R
fixed a bug

@@ -1,4 +1,4 @@
-# path_nasi = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし"
+path_nasi = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし"
 # files1 = list.files(path_nasi, pattern = ".Rdata")
 
 
@@ -9,7 +9,7 @@ df1 = NULL
 df2 = NULL
 df3 = NULL
 
-for(i in 1:length(splist[i])){
+for(i in 1:length(splist)){
   setwd("/Users/Yuki/Dropbox/eDNA_INLA")
   
   require(INLA)
@@ -161,7 +161,8 @@ for(i in 1:length(splist[i])){
   
   stk = inla.stack(stk_edna, stk_catch)
   
-  file = list.files(path_nasi, pattern = paste0(splist[i]))
+  file = list.files(path_nasi, pattern = paste0(splist[i], ".Rdata"))
+  setwd(dir = path_nasi)
   load(file)
   
   best_kono = res
@@ -194,7 +195,7 @@ for(i in 1:length(splist[i])){
   dpm_e$variable = as.factor(dpm_e$variable)
   dpm_c$variable = as.factor(dpm_c$variable)
   dpm = rbind(dpm_e, dpm_c)
-  dpm$sp == paste0(splist[i])
+  dpm$sp = paste0(splist[i])
   df_dpm = rbind(df_dpm, dpm)
   
   

### 2021-03-15 R/2018/outputs.R
changed dir

@@ -1,4 +1,4 @@
-setwd("/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし")
+# setwd("/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし")
 
 
 # do なし ---------------------------------------------------------
@@ -34,9 +34,9 @@ df_model = rbind(df_waic1, df_waic2)
 
 # 作図 ------------------------------------------------------------
 # environmental factors
-env = read.csv(paste0(path_nasi, "/df_env.csv"))
-env = env %>% mutate(variable = ifelse(env$variable == "ph", "pH", ifelse(env$variable == "temp", "Temperature", "Salinity")))
-env$variable = factor(env$variable, levels = c("Temperature", "Salinity", "pH"))
+path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし"
+env = read.csv(paste0(path_nasi2, "/df_env.csv"))
+env = env %>% mutate(variable = ifelse(env$variable == "Temp", "Temperature", "Salinity"))
 
 # all
 g = ggplot(env, aes(x = x, y = y, color = sp))
@@ -59,22 +59,22 @@ f = facet_wrap(~ sp, scales = "free", ncol = 4)
 labs = labs(x = "Salinity (scaled)", y = "Effect of environment", color = "Species")
 fig_env_sal = g+l+f+labs+theme_bw()
 
-# pH
-g = ggplot(env %>% filter(variable == "pH"), aes(x = x, y = y, color = sp))
-l = geom_line()
-f = facet_wrap(~ sp, scales = "free", ncol = 4)
-labs = labs(x = "pH (scaled)", y = "Effect of environment", color = "Species")
-fig_env_ph = g+l+f+labs+theme_bw()
+# # pH
+# g = ggplot(env %>% filter(variable == "pH"), aes(x = x, y = y, color = sp))
+# l = geom_line()
+# f = facet_wrap(~ sp, scales = "free", ncol = 4)
+# labs = labs(x = "pH (scaled)", y = "Effect of environment", color = "Species")
+# fig_env_ph = g+l+f+labs+theme_bw()
 
-ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし/temp.pdf"), plot = fig_env_temp, units = "in", width = 11.69, height = 8.27) 
[…]

### 2021-03-15 R/2018/get_est.R
changed dir

@@ -1,4 +1,4 @@
-path_nasi = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/doなし"
+path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし"
 # files1 = list.files(path_nasi, pattern = ".Rdata")
 
 
@@ -250,7 +250,7 @@ for(i in 1:length(splist)){
 }
 
 
-setwd(dir = path_nasi)
+setwd(dir = path_nasi2)
 write.csv(df_dpm, "df_dpm.csv")
 write.csv(df1, "df_ic.csv")
 write.csv(df2, "df_ic2.csv")

### 2021-03-15 R/2018/get_est.R
revised

@@ -226,7 +226,6 @@ for(i in 1:length(splist)){
   df_ic2 = expand.grid(x = proj_e$x, y = proj_e$y)
   df_ic2$mean_s = as.vector(mean_s_ic2)
   df_ic2$sd_s = as.vector(sd_s_ic2)
-  df_ic2 = df_ic2
   df_ic2$sp = paste0(splist[i])
   df2 = rbind(df2, df_ic2)
   
@@ -243,7 +242,6 @@ for(i in 1:length(splist)){
   df_ie2 = expand.grid(x = proj_e$x, y = proj_e$y)
   df_ie2$mean_s = as.vector(mean_s_ie2)
   df_ie2$sd_s = as.vector(sd_s_ie2)
-  df_ie2 = df_ie2
   df_ie2$sp = paste0(splist[i])
   df3 = rbind(df3, df_ie2)
   

### 2021-03-15 R/2018/outputs.R
revised

@@ -84,24 +84,82 @@ m_dpm$prob = exp(m_dpm$value)/(1+exp(m_dpm$value))
 world_map <- map_data("world")
 jap <- subset(world_map, world_map$region == "Japan")
 jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gracy 50", fill="gray 50")
 c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
 
 #eDNA
-g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = prob))
-t = geom_tile()
-c = coord_fixed(ratio = 1)
-s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
-edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+for(i in 1:length(splist)){
+  g = ggplot(data = m_dpm %>% filter(sp == splist[i], variable == "pred_mean_eDNA"), aes(east, north, fill = prob))
+  t = geom_tile()
+  c = coord_fixed(ratio = 1)
+  s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
+  f = facet_wrap(~ sp, ncol = 4)
+  edna = g+t+c+s+f+pol+c_map+theme_bw()+labs(title = "Estimated eDNA")
+  
+  ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/edna_", splist[i], ".pdf"), plot = edna, units = "in", width = 11.69, height = 8.27) 
+}
+
 
 #pred_mean_catch
-g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = prob))
-t = geom_tile()
-c = coord_fixed(ratio = 1)
-s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
-catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
+#何か変
[…]

### 2021-03-15 R/2018/outputs.R
added a map for raw data

@@ -163,3 +163,41 @@ for(i in 1:length(splist)){
 }
 
 
+
+
+
+# map raw data --------------------------------------------------
+# with map
+world_map <- map_data("world")
+jap <- subset(world_map, world_map$region == "Japan")
+jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
+pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
+
+
+setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+# 2018 ----------------------------------------------------------
+# eDNA & env ----------------------------------------------------------
+# データは4~12月，神奈川は地点によって調査がなかった月がある
+mifish = read.csv("joint_edna2018.csv")
+
+# catch ---------------------------------------------------------
+# データは1-12月
+data = read.csv("joint_cpue2018.csv")
+data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+
+# select species ------------------------------------------------
+e_fish = mifish %>% filter(sp_group == "konosiro", layer == "B")
+summary(e_fish)
+
+c_fish = data %>% filter(sp == "konosiro")
+summary(c_fish)
+
+map = rbind(e_fish %>% select(lng, lat) %>% dplyr::rename(lon = lng) %>% mutate(data = "eDNA"),
+            c_fish %>% select(lon, lat) %>% mutate(data = "CPUE"))
+
+g = ggplot(data = map, aes(lon, lat, color = data))
+p = geom_point()
+raw_map = g+p+pol+c_map+theme_bw()+labs(title = "")
+ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/raw_map.pdf"), plot = raw_map, units = "in", width = 11.69, height = 8.27) 
+

### 2021-03-16 R/2018/loop_doph.R
added fill name

@@ -251,8 +251,8 @@ for(i in 1:length(splist)){
   t = geom_tile()
   v = scale_fill_viridis(na.value = "transparent")
   c = coord_fixed(ratio = 1)
-  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean")
-  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD")
+  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean", fill = "mean_theta")
+  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD", fill = "SD_theta")
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/dist_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
@@ -274,8 +274,8 @@ for(i in 1:length(splist)){
   t = geom_tile()
   v = scale_fill_viridis(na.value = "transparent")
   c = coord_fixed(ratio = 1)
-  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean")
-  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD")
+  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean", fill = "Mean_u2")
+  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD", fill = "SD_u2")
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/fish_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
@@ -297,8 +297,8 @@ for(i in 1:length(splist)){
   t = geom_tile()
   v = scale_fill_viridis(na.value = "transparent")
   c = coord_fixed(ratio = 1)
-  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean")
-  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD")
+  labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean", fill = "Mean_u1")
+  labs2 = labs(x = "Longitude", y = "Latitude", title = "SD", fill = "Mean_u1")
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
[…]

### 2021-03-16 R/2018/loop_doph.R
added df to save estimations

@@ -1,5 +1,9 @@
 df_env = NULL
 df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
 splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 
 for(i in 1:length(splist)){
@@ -210,6 +214,8 @@ for(i in 1:length(splist)){
   dpm = rbind(dpm_e, dpm_c)
   m_dpm = dpm %>% filter(str_detect(variable, "mean"))
   unique(m_dpm$variable)
+  dpm$sp = paste0(splist[i])
+  df_dpm = rbind(df_dpm, dpm)
   
   #eDNA
   g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = value))
@@ -256,6 +262,9 @@ for(i in 1:length(splist)){
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/dist_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
+  df_ic = df_ie
+  df_ic$sp = paste0(splist[i])
+  df1 = rbind(df1, df_ic)
   
   # latent fisheries pattern -------------------------------------------
   range_e = apply(mesh2$loc[, c(1, 2)], 2, range)
@@ -279,6 +288,8 @@ for(i in 1:length(splist)){
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/fish_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
+  df_ic2$sp = paste0(splist[i])
+  df2 = rbind(df2, df_ic2)
   
   # latent pom pattern -------------------------------------------
   range_e = apply(mesh2$loc[, c(1, 2)], 2, range)
@@ -302,6 +313,8 @@ for(i in 1:length(splist)){
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/pom_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
+  df_ie2$sp = paste0(splist[i])
[…]

### 2021-03-16 R/2018/loop_doph.R
changed date

@@ -173,7 +173,11 @@ for(i in 1:length(splist)){
   res[[53]] = "cpue+scaled(env)-do-ph"
   res[[54]] = paste0(splist[i])
   
-  setwd(dir = "/Users/Yuki/Dropbox/eDNA_INLA/est0314")
+  
+  
+  
+  
+  setwd(dir = "/Users/Yuki/Dropbox/eDNA_INLA/est0317")
   save(res, file = paste0(splist[i], ".Rdata"))
   
   best_kono = res

### 2021-03-16 R/2018/makedata2018tuika.R
bags in isimoti-rui

@@ -11,7 +11,7 @@ require(abind)
 # (catch only data; not include zero data) ----------------------------------------------------------
 setwd(dir = dir_input)
 path = dir_input
-files = list.files(path)
+files = list.files(path, pattern = ".xlsx")
 
 all = NULL
 for(i in 1:length(files)){
@@ -83,7 +83,8 @@ t2 + geom_point(data = tent, aes(x = lon, y = lat), shape = 16, size = 1)
 write.csv(tent, "tent.csv")
 
 # add zero data -------------------------------
-tent2 = tent %>% mutate(tag = paste(year, formatC(tent2$month, width=2, flag="0"), formatC(tent2$day, width=2, flag="0"), format(as.numeric(str_sub(tent2$lon, 1, 8)), nsmall = 4), format(as.numeric(str_sub(tent2$lat, 1, 8)), nsmall = 4), sep = "_"))
+# tent2 = tent %>% mutate(tag = paste(year, formatC(tent2$month, width=2, flag="0"), formatC(tent2$day, width=2, flag="0"), format(as.numeric(str_sub(tent2$lon, 1, 8)), nsmall = 4), format(as.numeric(str_sub(tent2$lat, 1, 8)), nsmall = 4), sep = "_"))
+tent2 = tent %>% mutate(tag = paste(year, formatC(tent$month, width=2, flag="0"), formatC(tent$day, width=2, flag="0"), format(as.numeric(str_sub(tent$lon, 1, 8)), nsmall = 4), format(as.numeric(str_sub(tent$lat, 1, 8)), nsmall = 4), sep = "_"))
 effort = tent2 %>% filter(year == 2018) %>% group_by(tag) %>% summarize(m_effort = mean(effort)) 
 # tent3 = left_join(tent2 %>% filter(year == 2019), effort, by = "tag")
 
@@ -110,6 +111,7 @@ summary(old)
 unique(old$FISH)
 old = old %>% mutate(tag = paste(Y, formatC(old$M, width=2, flag="0"), formatC(old$D, width=2, flag="0"), format(as.numeric(str_sub(old$Lon, 1, 8)), nsmall = 4), format(as.numeric(str_sub(old$Lat, 1, 8)), nsmall = 4), sep = "_"))
 effort = old %>% group_by(tag) %>% summarize(m_effort = mean(NUM)) 
+unique(old$M)
 
[…]

### 2021-03-17 R/2018/makedata2018tuika.R
revised isimoti-rui data

@@ -147,3 +147,134 @@ for(i in 1:length(splist)){
 
 setwd(dir = dir_output)
 write.csv(cpue2018, "joint_cpue2018_tuikasp.csv")
+
+
+
+
+# イシモチ類のやり直し ----------------------------------------------------
+dir_input = "/Users/Yuki/Dropbox/TokyoBay_CPUE/nominalCPUE/"
+dir_output = "/Users/Yuki/Dropbox/eDNA_INLA/"
+
+require(tidyverse)
+require(openxlsx)
+require(gdata)
+require(abind)
+
+
+# combine the added data ----------------------------------------------------------
+# (catch only data; not include zero data) ----------------------------------------------------------
+setwd(dir = dir_input)
+path = dir_input
+files = list.files(path, pattern = "ｲｼﾓﾁ類")
+
+all = NULL
+for(i in 1:length(files)){
+  temp = read.xlsx(paste0(files[i]), colNames = T)
+  temp = temp %>% select(年月日, 緯度, 経度, 回数, CPUE, 全銘柄) %>%
+    mutate(check = as.Date(temp$年月日, origin = "1899-12-30")) %>% 
+    mutate(year = as.numeric(str_sub(check, 1, 4)), month = as.numeric(str_sub(check, 6, 7)), day = as.numeric(str_sub(check, 9, 10))) 
+  
+  # gear
+  if(str_detect(files[i], pattern = "不明")){
+    temp = temp %>% mutate(gear = "Beam Fumei")
+  }
+  if(str_detect(files[i], pattern = "スズキ")){
+    temp = temp %>% mutate(gear = "Beam Suzuki")
+  }
+  if(str_detect(files[i], pattern = "桁曳網")){
+    temp = temp %>% mutate(gear = "Keta")
+  }
+  
+  temp$sp = "isimoti-rui"
+  
+  # #species name
+  # if(str_detect(files[i], pattern = "シログチ")){
+  #   temp$sp = "isimoti-rui"
+  # }
+  # if(str_detect(files[i], pattern = "カマス")){
+  #   temp$sp = "kamasu-rui"
+  # }
+  # if(str_detect(files[i], pattern = "クロダイ")){
+  #   temp$sp = "kurodai"
+  # }
+  # if(str_detect(files[i], pattern = "トラフグ")){
+  #   temp$sp = "torafugu"
+  # }
+  
+  
[…]

### 2021-03-17 R/2018/loop_doph.R
revised

@@ -25,7 +25,7 @@ for(i in 1:length(splist)){
     data = read.csv("joint_cpue2018.csv")
     data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
   }else{
-    data = read.csv("joint_cpue2018_tuikasp.csv")
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
     data$cpue = data$catch/data$m_effort
   }
   

### 2021-03-17 R/2018/loop_doph.R
revised

@@ -341,3 +341,7 @@ for(i in 1:length(splist)){
 
 write.csv(df_env, "df_env.csv")
 write.csv(df_waic, "df_waic.csv")
+write.csv(df_dpm, "df_dist.csv")
+write.csv(df1, "df_ic.csv")
+write.csv(df2, "df_ic2.csv")
+write.csv(df3, "df_ie.csv")

### 2021-03-17 R/2018/loop_doph.R
changed

@@ -341,7 +341,7 @@ for(i in 1:length(splist)){
 
 write.csv(df_env, "df_env.csv")
 write.csv(df_waic, "df_waic.csv")
-write.csv(df_dpm, "df_dist.csv")
+write.csv(df_dpm, "df_dpm.csv")
 write.csv(df1, "df_ic.csv")
 write.csv(df2, "df_ic2.csv")
 write.csv(df3, "df_ie.csv")

### 2021-03-30 R/2018/outputs.R
revised the dir

@@ -34,7 +34,7 @@ df_model = rbind(df_waic1, df_waic2)
 
 # 作図 ------------------------------------------------------------
 # environmental factors
-path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし"
+path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0317"
 env = read.csv(paste0(path_nasi2, "/df_env.csv"))
 env = env %>% mutate(variable = ifelse(env$variable == "Temp", "Temperature", "Salinity"))
 
@@ -74,7 +74,7 @@ ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし/sal.pdf")
 
 
 # estimated eDNA & catch map ----------------------------------------------------------------
-path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし"
+path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0317"
 dpm = read.csv("df_dpm.csv")
 m_dpm = dpm %>% filter(str_detect(variable, "mean"))
 unique(m_dpm$variable)
@@ -84,7 +84,7 @@ m_dpm$prob = exp(m_dpm$value)/(1+exp(m_dpm$value))
 world_map <- map_data("world")
 jap <- subset(world_map, world_map$region == "Japan")
 jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gracy 50", fill="gray 50")
+pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
 c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
 
 #eDNA
@@ -97,7 +97,7 @@ for(i in 1:length(splist)){
   f = facet_wrap(~ sp, ncol = 4)
   edna = g+t+c+s+f+pol+c_map+theme_bw()+labs(title = "Estimated eDNA")
   
-  ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/edna_", splist[i], ".pdf"), plot = edna, units = "in", width = 11.69, height = 8.27) 
[…]

### 2021-03-30 R/2018/loop_doph.R
revised the dir

@@ -7,7 +7,8 @@ df3 = NULL
 splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
 
 for(i in 1:length(splist)){
-  setwd("/Users/Yuki/Dropbox/eDNA_INLA")
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
   
   require(INLA)
   require(tidyverse)
@@ -177,7 +178,9 @@ for(i in 1:length(splist)){
   
   
   
-  setwd(dir = "/Users/Yuki/Dropbox/eDNA_INLA/est0317")
+  dir_save = paste0(dirname, "/", Sys.Date())
+  dir.create(dir_save)
+  setwd(dir = dir_save)
   save(res, file = paste0(splist[i], ".Rdata"))
   
   best_kono = res
@@ -235,8 +238,8 @@ for(i in 1:length(splist)){
   s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
   catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
   
-  ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/edna_", splist[i], ".pdf"), plot = edna, units = "in", width = 11.69, height = 8.27) 
-  ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/catch_", splist[i], ".pdf"), plot = catch, units = "in", width = 11.69, height = 8.27) 
+  ggsave(file = paste0(dir_save, "/edna_", splist[i], ".pdf"), plot = edna, units = "in", width = 11.69, height = 8.27) 
+  ggsave(file = paste0(dir_save, "/catch_", splist[i], ".pdf"), plot = catch, units = "in", width = 11.69, height = 8.27) 
   
   
   # projecting the spatial field ----------------------------------
@@ -264,7 +267,7 @@ for(i in 1:length(splist)){
   labs1 = labs(x = "Longitude", y = "Latitude", title = "Mean", fill = "mean_theta")
   labs2 = labs(x = "Longitude", y = "Latitude", title = "SD", fill = "SD_theta")
   m = g1+t+v+c+pol+c_map+labs1+theme_bw()
[…]

### 2021-03-30 R/2018/outputs.R
revised the color in spatial error

@@ -130,12 +130,11 @@ require(gridExtra)
 for(i in 1:length(splist)){
   g1 = ggplot(df_ic %>% filter(sp == splist[i]), aes(x = x, y = y, fill = mean_s_ie))
   t = geom_tile()
-  v = scale_fill_viridis(na.value = "transparent")
   c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
+  s = scale_fill_gradient(name = "", low = "white", high = "red")
   labs1 = labs(x = "Longitude", y = "Latitude", title = "", fill = "")
   
-  m = g1+t+c+v+pol+c_map+labs1+theme_bw()
+  m = g1+t+c+s+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/dist_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
 }
@@ -143,7 +142,7 @@ for(i in 1:length(splist)){
 
 # error of fisheries -----------------------------------------------
 path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし"
-df_ic2 = read.csv("df_ic2.csv")
+df_ic2 = read.csv(paste0(path_nasi2, "/df_ic2.csv"))
 
 require(viridis)
 require(cowplot)
@@ -152,12 +151,11 @@ require(gridExtra)
 for(i in 1:length(splist)){
   g1 = ggplot(df_ic2 %>% filter(sp == splist[i]), aes(x = x, y = y, fill = mean_s_ie))
   t = geom_tile()
-  v = scale_fill_viridis(na.value = "transparent")
   c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
+  s = scale_fill_gradient(name = "", low = "white", high = "red")
   labs1 = labs(x = "Longitude", y = "Latitude", title = "", fill = "")
   
-  m = g1+t+c+v+pol+c_map+labs1+theme_bw()
+  m = g1+t+c+s+pol+c_map+labs1+theme_bw()
   ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/fish_", splist[i], ".pdf"), plot = m, units = "in", width = 11.69, height = 8.27) 
   
 }

### 2021-03-30 R/2018/outputs.R
revised in estimated eDNA

@@ -75,7 +75,7 @@ ggsave(file = paste0("/Users/Yuki/Dropbox/eDNA_INLA/est0314/dophなし/sal.pdf")
 
 # estimated eDNA & catch map ----------------------------------------------------------------
 path_nasi2 = "/Users/Yuki/Dropbox/eDNA_INLA/est0317"
-dpm = read.csv("df_dpm.csv")
+dpm = read.csv(paste0(path_nasi2, "/df_dpm.csv"))
 m_dpm = dpm %>% filter(str_detect(variable, "mean"))
 unique(m_dpm$variable)
 m_dpm$prob = exp(m_dpm$value)/(1+exp(m_dpm$value))
@@ -92,7 +92,7 @@ splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", 
 for(i in 1:length(splist)){
   g = ggplot(data = m_dpm %>% filter(sp == splist[i], variable == "pred_mean_eDNA"), aes(east, north, fill = prob))
   t = geom_tile()
-  c = coord_fixed(ratio = 1)
+  c = coord_fixed(ratio = 1) #必要？？
   s = scale_fill_gradient(name = "Occurrence", low = "white", high = "red")
   f = facet_wrap(~ sp, ncol = 4)
   edna = g+t+c+s+f+pol+c_map+theme_bw()+labs(title = "Estimated eDNA")

### 2021-03-30 R/2018/makedata2018.R
removed Kuroshibikamasu from eDNA data

@@ -13,6 +13,10 @@ edna = edna %>% gather(key = zotu, value = count, 6:ncol(edna))
 analize = data.frame(zotu = c("Zotu62", "Zotu59", "Zotu120", "Zotu6", "Zotu1", "Zotu13", "Zotu14", "Zotu137", "Zotu23", "Zotu64", "Zotu48"), sp = c("maanago", "makogarei", "isigarei", "suzuki", "konosiro", "kurodai", "siroguti", "nibe", "akakamasu", "yamatokamasu", "kurosibikamasu"), sp_group = c("maanago", "makogarei", "isigarei", "suzuki", "konosiro", "kurodai", "isimoti-rui", "isimoti-rui", "kamasu-rui", "kamasu-rui", "kamasu-rui"))
 edna2 = edna %>% filter(zotu %in% analize$zotu)
 edna2 = merge(edna2, analize, by = "zotu")
+
+#クロシビカマスの除去
+edna2 = edna2 %>% filter(sp != "kurosibikamasu")
+(unique(edna2$sp))
 (unique(edna2$site))
 
 lonlat = read.table("2018/sampling_points.txt", header = T)

### 2021-03-30 R/2018/loop_temp.R
initial commit

@@ -1,0 +1,349 @@
+df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-30 R/2018/loop_tempsal.R
small changes

@@ -171,14 +171,14 @@ for(i in 1:length(splist)){
              control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
              control.compute = list(waic = TRUE, dic = TRUE))
   
-  res[[53]] = "cpue+scaled(env)-do-ph"
+  res[[53]] = "cpue+scaled(temp, sal)"
   res[[54]] = paste0(splist[i])
   
   
   
   
   
-  dir_save = paste0(dirname, "/", Sys.Date())
+  dir_save = paste0(dirname, "/", Sys.Date(), "tempsal")
   dir.create(dir_save)
   setwd(dir = dir_save)
   save(res, file = paste0(splist[i], ".Rdata"))

### 2021-03-30 R/2018/loop_sal.R
initial commit

@@ -1,0 +1,350 @@
+df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-30 R/2018/loop_noenv.R
initial commit

@@ -1,0 +1,349 @@
+df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-30 R/2018/loop_sal.R
revised

@@ -171,7 +171,7 @@ for(i in 1:length(splist)){
              control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
              control.compute = list(waic = TRUE, dic = TRUE))
   
-  res[[53]] = "cpue+scaled(temp, sal)"
+  res[[53]] = "scaled(sal)"
   res[[54]] = paste0(splist[i])
   
   

### 2021-03-30 R/2018/loop_tempsal.R
revised

@@ -171,7 +171,7 @@ for(i in 1:length(splist)){
              control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
              control.compute = list(waic = TRUE, dic = TRUE))
   
-  res[[53]] = "cpue+scaled(temp, sal)"
+  res[[53]] = "scaled(temp, sal)"
   res[[54]] = paste0(splist[i])
   
   

### 2021-03-30 R/2018/loop_temp.R
revised

@@ -170,7 +170,7 @@ for(i in 1:length(splist)){
              control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
              control.compute = list(waic = TRUE, dic = TRUE))
   
-  res[[53]] = "cpue+scaled(temp)"
+  res[[53]] = "scaled(temp)"
   res[[54]] = paste0(splist[i])
   
   

### 2021-03-30 results/draft.tex
revised

@@
 Almost of all gear was beam trawl although dredge net also used.
-The species which also detected by eDNA was \textit{Conger myriaster} (マアナゴ), \textit{Kareius bicoloratus} (イシガレイ), \textit{Lateolabrax japonicus} (スズキ), and \textit{Konosirus punctatus} (コノシロ).
+The species which also detected by eDNA was \textit{Conger myriaster} (マアナゴ), \textit{Kareius bicoloratus} (イシガレイ), \textit{Pseudopleuronectes yokohamae} (マコガレイ), \textit{Lateolabrax japonicus} (スズキ), \textit{Konosirus punctatus} (コノシロ), \textit{Acanthopagrus schlegelii}, species group of \textit{Pennahia} which includes \textit{Pennahia argentata} and \textit{Nibea mitsukurii} (イシモチ類), and species group of \textit{Sphyraena} which includes \textit{Sphyraena pinguis}, \textit{Sphyraena japonica}, and \textit{Promethichthys prometheus}.
 Thus, we estimated the spatial distribution of these four species using the eDNA-IDM.
-\textcolor{red}{マコガレイ，カマス類，クロダイ，イシモチ類も解析できる？？}
+\textcolor{red}{カマス類とイシモチ類の種群の書き方を工夫する．あと，表でまとめる？}
 
@@
 \[
-\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \beta_{i} + \theta(s_{i}) + u_{c}(s_{i})
+\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \theta(s_{i}) + u_{c}(s_{i})
 \]
+%\[
+%\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \beta_{i} + \theta(s_{i}) + u_{c}(s_{i})
+%\]
 where $\alpha$ is the intercept, and $x_{k}(s_{i})$ is the covariates at sites $i$ for occurrence probabilities of eDNA at sites $i$.
@@
 \ \ \ \ \ \ \ \ \ \
+
+\section{Results}
 

### 2021-03-30 R/2018/loop_temp.R
run

@@ -210,12 +210,12 @@ for(i in 1:length(splist)){
   dpm_e$variable = as.factor(dpm_e$variable)
   dpm_c$variable = as.factor(dpm_c$variable)
   
-  # with map
-  world_map <- map_data("world")
-  jap <- subset(world_map, world_map$region == "Japan")
-  jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-  pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
-  c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
+  # # with map
+  # world_map <- map_data("world")
+  # jap <- subset(world_map, world_map$region == "Japan")
+  # jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
+  # pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+  # c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
   
   dpm = rbind(dpm_e, dpm_c)
   m_dpm = dpm %>% filter(str_detect(variable, "mean"))
@@ -223,22 +223,22 @@ for(i in 1:length(splist)){
   dpm$sp = paste0(splist[i])
   df_dpm = rbind(df_dpm, dpm)
   
-  #eDNA
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
-  #pred_mean_catch
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
[…]

### 2021-03-30 R/2018/loop_sal.R
run

@@ -211,12 +211,12 @@ for(i in 1:length(splist)){
   dpm_e$variable = as.factor(dpm_e$variable)
   dpm_c$variable = as.factor(dpm_c$variable)
   
-  # with map
-  world_map <- map_data("world")
-  jap <- subset(world_map, world_map$region == "Japan")
-  jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-  pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
-  c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
+  # # with map
+  # world_map <- map_data("world")
+  # jap <- subset(world_map, world_map$region == "Japan")
+  # jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
+  # pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+  # c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
   
   dpm = rbind(dpm_e, dpm_c)
   m_dpm = dpm %>% filter(str_detect(variable, "mean"))
@@ -224,22 +224,22 @@ for(i in 1:length(splist)){
   dpm$sp = paste0(splist[i])
   df_dpm = rbind(df_dpm, dpm)
   
-  #eDNA
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
-  #pred_mean_catch
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
[…]

### 2021-03-30 R/2018/loop_tempsal.R
run

@@ -211,12 +211,12 @@ for(i in 1:length(splist)){
   dpm_e$variable = as.factor(dpm_e$variable)
   dpm_c$variable = as.factor(dpm_c$variable)
   
-  # with map
-  world_map <- map_data("world")
-  jap <- subset(world_map, world_map$region == "Japan")
-  jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-  pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
-  c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
+  # # with map
+  # world_map <- map_data("world")
+  # jap <- subset(world_map, world_map$region == "Japan")
+  # jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
+  # pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+  # c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
   
   dpm = rbind(dpm_e, dpm_c)
   m_dpm = dpm %>% filter(str_detect(variable, "mean"))
@@ -224,22 +224,22 @@ for(i in 1:length(splist)){
   dpm$sp = paste0(splist[i])
   df_dpm = rbind(df_dpm, dpm)
   
-  #eDNA
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
-  #pred_mean_catch
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
[…]

### 2021-03-30 R/2018/loop_noenv.R
revised

@@ -210,12 +210,12 @@ for(i in 1:length(splist)){
   dpm_e$variable = as.factor(dpm_e$variable)
   dpm_c$variable = as.factor(dpm_c$variable)
   
-  # with map
-  world_map <- map_data("world")
-  jap <- subset(world_map, world_map$region == "Japan")
-  jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
-  pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
-  c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
+  # # with map
+  # world_map <- map_data("world")
+  # jap <- subset(world_map, world_map$region == "Japan")
+  # jap_cog <- jap[jap$lat > 35 & jap$lat < 38 & jap$long > 139 & jap$long < 141, ]
+  # pol = geom_polygon(data = jap_cog, aes(x=long, y=lat, group=group), colour="gray 50", fill="gray 50")
+  # c_map = coord_map(xlim = c(139.5, 140.3), ylim = c(35, 35.75))
   
   dpm = rbind(dpm_e, dpm_c)
   m_dpm = dpm %>% filter(str_detect(variable, "mean"))
@@ -223,22 +223,22 @@ for(i in 1:length(splist)){
   dpm$sp = paste0(splist[i])
   df_dpm = rbind(df_dpm, dpm)
   
-  #eDNA
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_eDNA"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  edna = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
-  #pred_mean_catch
-  g = ggplot(data = m_dpm %>% filter(variable == "pred_mean_catch"), aes(east, north, fill = value))
-  t = geom_tile()
-  c = coord_fixed(ratio = 1)
-  s = scale_fill_gradient(name = "encounter prob. (logit)", low = "blue", high = "orange")
-  catch = g+t+c+s+pol+c_map+theme_bw()+labs(title = paste0(splist[i]))
-  
[…]

### 2021-03-31 R/2018/loop_sal.R
revised

@@ -341,6 +341,7 @@ for(i in 1:length(splist)){
   df_waic = rbind(df_waic, waic)
 }
 
+setwd(dir = dir_save)
 write.csv(df_env, "df_env.csv")
 write.csv(df_waic, "df_waic.csv")
 write.csv(df_dpm, "df_dpm.csv")

### 2021-03-31 R/2018/loop_noenv_eDNAonly.R
revised

@@ -20,45 +20,45 @@ for(i in 1:length(splist)){
   # データは4~12月，神奈川は地点によって調査がなかった月がある
   mifish = read.csv("joint_edna2018.csv")
   
-  # catch ---------------------------------------------------------
-  # データは1-12月
-  if(i < 6){
-    data = read.csv("joint_cpue2018.csv")
-    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
-  }else{
-    data = read.csv("joint_cpue2018_tuikasp2.csv")
-    data$cpue = data$catch/data$m_effort
-  }
-  
-  
+  # # catch ---------------------------------------------------------
+  # # データは1-12月
+  # if(i < 6){
+  #   data = read.csv("joint_cpue2018.csv")
+  #   data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  # }else{
+  #   data = read.csv("joint_cpue2018_tuikasp2.csv")
+  #   data$cpue = data$catch/data$m_effort
+  # }
+  # 
+  # 
   
   # select species ------------------------------------------------
   e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
   summary(e_fish)
   edna = (e_fish$count > 0) + 0
   
-  c_fish = data %>% filter(sp == paste0(splist[i]))
-  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
-  summary(c_fish)
-  # catch = (c_fish$catch > 0) + 0
-  catch = (c_fish$cpue > 0) + 0
-  summary(catch)
+  # c_fish = data %>% filter(sp == paste0(splist[i]))
+  # # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  # summary(c_fish)
+  # # catch = (c_fish$catch > 0) + 0
+  # catch = (c_fish$cpue > 0) + 0
+  # summary(catch)
   
   
   # INLA ----------------------------------------------------------
   #lonlat
   e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
-  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
-  loc = rbind(e_loc, c_loc)
+  # c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
[…]

### 2021-03-31 R/2018/loop_noenv_CPUEonly.R
revised

@@ -1,0 +1,231 @@
+#df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  summary(c_fish)
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
+  c_loca = as.matrix(cbind(c_fish %>% filter(catch == 0) %>% select(lon), c_fish %>% filter(catch == 0) %>% select(lat)))
+  
+  bound2 = inla.nonconvex.hull(c_loc, convex = 0.05, concave = -0.15)
+  mesh2 = inla.mesh.2d(boundary = bound2, max.edge = c(0.04, 0.04), cutoff = 0.08/5)
+  plot(mesh2)
+  points(c_locp, col = "red", pch = 15, cex = 2) #pdfにする時はcex = 1，その他は.5にする
+  points(c_loca, col = "orange", pch = 16, cex = 1) #pdfにする時はcex = 1，その他は.5にする
+  mesh2$n #618
+  
+  # projector matricies
+  c_A = inla.spde.make.A(mesh2, loc = c_loc)
+  dim(c_A) # 2321, 618
[…]

### 2021-03-31 R/2018/loop_noenv_noic2.R
revised

@@ -1,0 +1,350 @@
+#df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-31 R/2018/loop_noenv_noie2.R

@@ -1,0 +1,350 @@
+#df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-31 R/2018/loop_noenv_noie2noic2.R
initial commit

@@ -1,0 +1,349 @@
+#df_env = NULL
+df_waic = NULL
+df_dpm = NULL
+df1 = NULL
+df2 = NULL
+df3 = NULL
+splist = c("konosiro", "makogarei", "maanago", "isigarei", "suzuki", "kurodai", "kamasu-rui", "isimoti-rui")
+
+for(i in 1:length(splist)){
+  dirname = "/Users/Yuki/Dropbox/eDNA_INLA"
+  setwd(dir = dirname)
+  
+  require(INLA)
+  require(tidyverse)
+  require(openxlsx)
+  
+  # 2018 ----------------------------------------------------------
+  
+  # eDNA & env ----------------------------------------------------------
+  # データは4~12月，神奈川は地点によって調査がなかった月がある
+  mifish = read.csv("joint_edna2018.csv")
+  
+  # catch ---------------------------------------------------------
+  # データは1-12月
+  if(i < 6){
+    data = read.csv("joint_cpue2018.csv")
+    data = data %>% dplyr::rename(sp = FISH, cpue = CPUE, lon = Lon, lat = Lat)
+  }else{
+    data = read.csv("joint_cpue2018_tuikasp2.csv")
+    data$cpue = data$catch/data$m_effort
+  }
+  
+  
+  
+  # select species ------------------------------------------------
+  e_fish = mifish %>% filter(sp_group == paste0(splist[i]), layer == "B")
+  summary(e_fish)
+  edna = (e_fish$count > 0) + 0
+  
+  c_fish = data %>% filter(sp == paste0(splist[i]))
+  # c_mako = data %>% filter(FISH == "makogarei", Y == 2018, M > 2) #eDNAと月を揃えた方が良い？
+  summary(c_fish)
+  # catch = (c_fish$catch > 0) + 0
+  catch = (c_fish$cpue > 0) + 0
+  summary(catch)
+  
+  
+  # INLA ----------------------------------------------------------
+  #lonlat
+  e_loc = as.matrix(cbind(e_fish$lng, e_fish$lat))
+  c_loc = as.matrix(cbind(c_fish$lon, c_fish$lat))
+  loc = rbind(e_loc, c_loc)
+  
+  c_locp = as.matrix(cbind(c_fish %>% filter(catch > 0) %>% select(lon), c_fish %>% filter(catch > 0) %>% select(lat)))
[…]

### 2021-03-31 R/2018/loop_noenv_noie2noic2.R
revised

@@ -169,7 +169,7 @@ for(i in 1:length(splist)){
              control.results = list(return.marginals.random = FALSE, return.marginals.predictor = FALSE), 
              control.compute = list(waic = TRUE, dic = TRUE))
   
-  res[[53]] = "no_env"
+  res[[53]] = "no_env/noie2noic2"
   res[[54]] = paste0(splist[i])
   
   
